---
title: "Final_Study_2_Analysis"
output: html_document
date: "2025-02-19"
---

##--------Load packages---------
```{r setup, include=FALSE}
if (!(require("tidyverse"))) install.packages("tidyverse"); require("tidyverse")
if (!(require("psych"))) install.packages("psych"); require("psych")
if (!require("irr")) {install.packages("irr"); require("irr")} 
if (!require("reshape2")) {install.packages("reshape2"); require("reshape2")} 
if (!require("ggrepel")) {install.packages("ggrepel"); require("ggrepel")} 
if (!require("pwr")) {install.packages("pwr"); require("pwr")}
library(knitr)
library(readr)
library(gridExtra)
library(grid)
library(png)
library(ggrepel)
```

#---------Load in data--------
```{r}

data_23 <- read.csv("../data/rating-task/v23/data_exp_169297-v23_task-6digNEWEST.csv")
data_24 <- read.csv("../data/rating-task/v24/data_exp_169297-v24_task-6dig.csv")
data_25 <- read.csv("../data/rating-task/v25/data_exp_169297-v25_task-6dig.csv")
data_26 <- read.csv("../data/rating-task/v26/data_exp_169297-v26_task-6dig.csv")
data_27 <- read.csv("../data/rating-task/v27/data_exp_169297-v27_task-6dig.csv")

```

```{r}
granularity_data_23 <- data_23 %>%
  filter(Response.Type == "response") %>% 
  select("Participant.Public.ID","Response","Object.Name", "Spreadsheet..Image", "Spreadsheet..Audio") %>%
  mutate(Response = as.numeric(Response))

granularity_data_24 <- data_24 %>%
  filter(Response.Type == "response") %>% 
  select("Participant.Public.ID","Response","Object.Name", "Spreadsheet..Image", "Spreadsheet..Audio") %>%
  mutate(Response = as.numeric(Response))

granularity_data_25 <- data_25 %>%
  filter(Response.Type == "response") %>% 
  select("Participant.Public.ID","Response","Object.Name", "Spreadsheet..Image", "Spreadsheet..Audio") %>%
  mutate(Response = as.numeric(Response))

granularity_data_26 <- data_26 %>%
  filter(Response.Type == "response") %>% 
  select("Participant.Public.ID","Response","Object.Name", "Spreadsheet..Image", "Spreadsheet..Audio") %>%
  mutate(Response = as.numeric(Response))

granularity_data_27 <- data_27 %>%
  filter(Response.Type == "response") %>% 
  select("Participant.Public.ID","Response","Object.Name", "Spreadsheet..Image", "Spreadsheet..Audio") %>%
  mutate(Response = as.numeric(Response)) %>%
  mutate(Participant.Public.ID = ifelse(grepl("^5", Participant.Public.ID), 
                               paste0("TEAM_YA_0", substr(Participant.Public.ID, 2, nchar(Participant.Public.ID))), 
                               Participant.Public.ID))
```

### EXCLUDE PARTICIPANTS FROM STUDY 1
```{r}
study1_participants <- final_scores$SURVEY_CODE

granularity_data_23 <- granularity_data_23 %>%
  filter(!(Participant.Public.ID %in% study1_participants)) %>%
  filter(nchar(as.character(Participant.Public.ID)) != 5)

granularity_data_24 <-granularity_data_24 %>%
  filter(Participant.Public.ID == "TEAM_YA_046" | Participant.Public.ID == "TEAM_YA_056" | Participant.Public.ID == "TEAM_YA_048" | Participant.Public.ID == "TEAM_YA_054")

granularity_data_25 <-granularity_data_25 %>%
  filter(Participant.Public.ID == "TEAM_YA_065")

granularity_data_26 <-granularity_data_26 %>%
  filter(Participant.Public.ID == "TEAM_YA_069" | Participant.Public.ID == "TEAM_YA_064" | Participant.Public.ID == "TEAM_YA_062" | Participant.Public.ID == "TEAM_YA_061" | Participant.Public.ID == "TEAM_YA_081")

granularity_data_27 <-granularity_data_27 %>%
  filter(Participant.Public.ID != "TEAM_YA_077")

granularity_data <- bind_rows(granularity_data_23,
                              granularity_data_24,
                              granularity_data_25,
                              granularity_data_26,
                              granularity_data_27) %>%
  filter(!grepl("^TEAM_DEV_\\d+", Participant.Public.ID))

# num_unique_ids <- granularity_data %>%
#   summarise(unique_count = n_distinct(Participant.Public.ID)) %>%
#   pull(unique_count)
# 
# print(num_unique_ids)

```

```{r}
## Separating by picture vs music, removing practice stims
granularity_pic <- granularity_data %>%
  filter(Spreadsheet..Image != "") %>%
  filter(Spreadsheet..Image != "Coffee 1.jpg") %>%
  select(-c("Spreadsheet..Audio"))

granularity_music <- granularity_data %>%
  filter(Spreadsheet..Audio != "") %>%
  filter(Spreadsheet..Audio != "8_pieceA_dreamy_calm_joyous_1.mp3") %>%
  select(-c("Spreadsheet..Image"))
```

```{r}
granularity_check <- granularity_data %>%
  filter(Spreadsheet..Audio == "6_5.mp3") %>%
  group_by(Participant.Public.ID) %>%
  summarize(count = n())
```

##-----Subsetting by valence and stimulus type--------
```{r}
# List of emotions
emotions <- list(
  neg = c("Gloomy", "Sad", "Scared", "Anxious", "Upset"),
  pos = c("Happy", "Satisfied", "Excited", "Joyful", "Relaxed")
)

# Function to filter and rename
filter_and_rename <- function(data, emotion, media_type, keep_id = FALSE) {
  columns_to_select <- if (keep_id) {
    c("Participant.Public.ID", "Response")
  } else {
    c("Response")
  }
  
  data %>%
    filter(Object.Name == paste(emotion, "Slider")) %>%
    select(-c(paste0("Spreadsheet..", media_type), "Object.Name")) %>%
    select(all_of(columns_to_select)) %>%
    rename(!!tolower(emotion) := "Response")
}

# General function to apply filtering to both media types and emotion types
apply_filter <- function(data, emotions, media_type) {
  lapply(seq_along(emotions), function(i) {
    filter_and_rename(data, emotions[i], media_type, keep_id = (i == 1))
  }) %>% bind_cols() %>% na.omit()
}

# Apply the process for each combination of data and emotion types
music_negative <- apply_filter(granularity_music, emotions$neg, "Audio")
music_positive <- apply_filter(granularity_music, emotions$pos, "Audio")
pic_negative <- apply_filter(granularity_pic, emotions$neg, "Image")
pic_positive <- apply_filter(granularity_pic, emotions$pos, "Image")
```

##--Plotting means of emotion word ratings--
```{r}
# Modified plot_emotion_means to return summaries as well
plot_emotion_means <- function(data, title, file_name, type) {
  summary <- data %>%
    select(-Participant.Public.ID) %>%
    pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
    group_by(variable) %>%
    summarize(
      mean_value = mean(value, na.rm = TRUE),
      se_value = sd(value, na.rm = TRUE) / sqrt(n())
    )
  
  # Add the "type" column for "Music" or "Picture"
  summary$type <- type
  
  plot <- ggplot(summary, aes(x = variable, y = mean_value)) +
    geom_point() +
    geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), width = 0.2) +
    labs(title = title, x = "Emotion", y = "Mean Response") +
    theme_bw()
  
  ggsave(file_name, plot, width = 9)
  
  # Return the summary for further use
  return(summary)
}

# Get summaries and plots for negative and positive emotions
music_negative_summary <- plot_emotion_means(music_negative, "Music Negative Emotion Means", "../results/rating-task/study2/Music_Negative_Means_2_25_25.png", "Music")
music_positive_summary <- plot_emotion_means(music_positive, "Music Positive Emotion Means", "../results/rating-task/study2/Music_Positive_Means_2_25_25.png", "Music")
pic_negative_summary <- plot_emotion_means(pic_negative, "Picture Negative Emotion Means", "../results/rating-task/study2/Picture_Negative_Means_2_25_25.png", "Picture")
pic_positive_summary <- plot_emotion_means(pic_positive, "Picture Positive Emotion Means", "../results/rating-task/study2/Picture_Positive_Means_2_25_25.png", "Picture")

# Combine the summaries for negative and positive emotions
neg_summary <- bind_rows(music_negative_summary, pic_negative_summary)
pos_summary <- bind_rows(music_positive_summary, pic_positive_summary)


# Plot for negative emotions (combined music and picture)
neg_plot <- ggplot(neg_summary, aes(x = variable, y = mean_value, color = type)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), width = 0.2) +
  labs(title = "Negative Emotion Means", x = "Emotion", y = "Mean Response") +
  theme_bw()

# Plot for positive emotions (combined music and picture)
pos_plot <- ggplot(pos_summary, aes(x = variable, y = mean_value, color = type)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), width = 0.2) +
  labs(title = "Positive Emotion Means", x = "Emotion", y = "Mean Response") +
  theme_bw()

# Save the combined plots
ggsave('../results/rating-task/study2/Negative_Emotion_Means_2_25_25.png', neg_plot, width = 9)
ggsave('../results/rating-task/study2/Positive_Emotion_Means_2_25_25.png', pos_plot, width = 9)
```
##-Percent of nonzero responses--
```{r}
# Function to calculate the percentage of non-zero responses for each column
calculate_non_zero_percentage <- function(df) {
  df %>%
    select(-Participant.Public.ID) %>%
    summarise(across(everything(), ~ round(sum(!is.na(.) & . != 0) / sum(!is.na(.)) * 100)))
}

# List of dataframes and their captions
tables <- list(
  list(data = music_negative, caption = "% of Non-Zero Responses for Negative Emotion Words (Music)"),
  list(data = pic_negative, caption = "% of Non-Zero Responses for Negative Emotion Words (Pictures)"),
  list(data = music_positive, caption = "% of Non-Zero Responses for Positive Emotion Words (Music)"),
  list(data = pic_positive, caption = "% of Non-Zero Responses for Positive Emotion Words (Pictures)")
)

# Create table grobs and arrange them with their captions
table_grobs <- lapply(tables, function(tbl) {
  percentages <- calculate_non_zero_percentage(tbl$data)
  table_grob <- tableGrob(percentages, theme = ttheme_minimal())
  caption_grob <- textGrob(tbl$caption, gp = gpar(fontsize = 10))
  arrangeGrob(caption_grob, table_grob, ncol = 1)
})

# Arrange all tables vertically
arranged_tables <- do.call(arrangeGrob, c(table_grobs, ncol = 1))

# Save the arranged tables as a PNG file
png("../results/rating-task/study2/Emotion Response Percentages_2_25_25.png", width = 400, height = 400)
grid.draw(arranged_tables)
dev.off()
```

##--Separating pics and music by valence (pos/neg)--
```{r}
# Create a function to filter data by positive or negative images/music
filter_by_type <- function(data, type_list, column_name) {
  data %>%
    filter(!!sym(column_name) %in% type_list)
}

# Positive and Negative picture and music lists
pos_pic <- c("Beach 1.jpg", "Fireworks 6.jpg", "Lake 12.jpg", "Rainbow 2.jpg", "Clean 1.jpg", "Heart 3.jpg", "Rocks 1.jpg", "Snow 1.jpg")
neg_pic <- c("Dirt 1.jpg", "Ferret 1.jpg", "Fire 10.jpg", "Flood 1.jpg", "Destruction 2.jpg", "Garbage dump 1.jpg", "Prison 2.jpg", "Toilet 4.jpg")

pos_music <- c("2_1.mp3", "4_1.mp3", "4_2.mp3", "6_5.mp3", "8_2.mp3", "10_1.mp3", "10_2.mp3", "12_2.mp3")
neg_music <- c("3_1.mp3", "5_14.mp3", "6_10.mp3", "7_10.mp3", "7_13.mp3", "11_2.mp3", "11_10.mp3", "11_11.mp3")

# Apply the filter function
pos_pic_data <- filter_by_type(granularity_pic, pos_pic, "Spreadsheet..Image")
neg_pic_data <- filter_by_type(granularity_pic, neg_pic, "Spreadsheet..Image")

pos_music_data <- filter_by_type(granularity_music, pos_music, "Spreadsheet..Audio")
neg_music_data <- filter_by_type(granularity_music, neg_music, "Spreadsheet..Audio")
```

### STIMULUS HEATMAPPING
```{r}
# 8 clips
averages_pos_music <- pos_music_data %>%
  group_by(Spreadsheet..Audio, Object.Name) %>%
  summarise(
    Average.Response = mean(Response, na.rm = TRUE),
    se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    )

# 8 clips
averages_neg_music <- neg_music_data %>%
  group_by(Spreadsheet..Audio, Object.Name) %>%
  summarise(
    Average.Response = mean(Response, na.rm = TRUE),
    se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    )

# 8 pics
averages_pos_pic <- pos_pic_data %>%
  group_by(Spreadsheet..Image, Object.Name) %>%
  summarise(
    Average.Response = mean(Response, na.rm = TRUE),
    se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    )

# 8 pics
averages_neg_pic <- neg_pic_data %>%
  group_by(Spreadsheet..Image, Object.Name) %>%
  summarise(
    Average.Response = mean(Response, na.rm = TRUE),
    se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    )

all_averages <- bind_rows(
  averages_pos_music %>% mutate(Type = "Positive Valence Music"),
  averages_neg_music %>% mutate(Type = "Negative Valence Music"),
  averages_pos_pic %>% mutate(Type = "Positive Valence Pictures"),
  averages_neg_pic %>% mutate(Type = "Negative Valence Pictures"),
)

all_averages$Object.Name <- gsub("Slider", "", all_averages$Object.Name)

# Trim any extra whitespace that might be left after removing "Slider"
all_averages$Object.Name <- trimws(all_averages$Object.Name)

emotion_order <- c("Gloomy", "Anxious", "Sad", "Scared", "Upset", "Excited", "Happy", "Joyful", "Relaxed", "Satisfied")
all_averages$Object.Name <- factor(all_averages$Object.Name, levels = emotion_order)

grouped_averages <- split(all_averages, all_averages$Type)

```

## 10-9-24
```{r}
library(ggcorrplot)
df_wide <- pivot_wider(all_averages[, c("Spreadsheet..Audio", "Object.Name", "Average.Response", "Spreadsheet..Image")], 
                       names_from = Object.Name, 
                       values_from = Average.Response)

df_wide <- df_wide[, c("Spreadsheet..Audio", "Spreadsheet..Image", emotion_order)]

# Split into audio and image datasets
audio_df <- df_wide[!is.na(df_wide$Spreadsheet..Audio), ]
image_df <- df_wide[!is.na(df_wide$Spreadsheet..Image), ]

# Drop the unnecessary columns for correlation
audio_corr <- cor(audio_df[ , -c(1, 2)])  # Removing 'Spreadsheet.Audio' and 'Spreadsheet.Image'
image_corr <- cor(image_df[ , -c(1, 2)])  # Removing 'Spreadsheet.Audio' and 'Spreadsheet.Image'

# Plot heatmap for audio correlation
music_corr_plot <- ggcorrplot(audio_corr, 
           method = "square", 
           type = "lower", 
           lab = TRUE, 
           lab_size = 3, 
           colors = c("blue", "white", "red"), 
           title = "Correlations of Emotion Responses to Music",
           tl.cex = 10,
           ggtheme = theme_classic())

# Plot heatmap for image correlation
pic_corr_plot <- ggcorrplot(image_corr, 
           method = "square", 
           type = "lower", 
           lab = TRUE, 
           lab_size = 3, 
           colors = c("blue", "white", "red"), 
           title = "Correlations of Emotion Responses to Pictures",
           tl.cex = 10,
           ggtheme = theme_classic())

ggsave('../results/rating-task/study2/Picture Emotion Correlations 2_25_25.png', pic_corr_plot, width = 9)
ggsave('../results/rating-task/study2/Music Emotion Correlations 2_25_25.png', music_corr_plot, width = 9)

```

```{r}
for(group_name in names(grouped_averages)) {
  # Get the specific dataframe for the current group
  df_group <- grouped_averages[[group_name]]
  
  # Identify the non-NA column (either Spreadsheet..Audio or Spreadsheet..Image)
  df_group <- df_group %>%
    mutate(Stimulus = ifelse(!is.na(Spreadsheet..Audio), Spreadsheet..Audio, Spreadsheet..Image))
  
  # Create the confusion matrix plot
  p <- ggplot(df_group, aes(x = Object.Name, y = Stimulus, fill = Average.Response)) +
    geom_tile() +
    ggtitle(paste("Average Responses by Emotion and Stimulus for", group_name)) +
    xlab("Emotion") +
    ylab("Stimulus") +
    scale_fill_gradient(low = "blue", high = "red") +  # Adjust color scheme as needed
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, color = "black"), axis.text.y = element_text(color = "black"), plot.background = element_rect(fill = "white", color = NA),  # Set plot background to white
        panel.background = element_rect(fill = "white", color = NA))  # Rotate x-axis labels for readability
  
  # Print and save the plots
  print(p)
  ggsave(paste("../results/rating-task/study2/", group_name, ".png"), p, width = 9)
}

```

##-All graphed together
```{r}
# Function to summarize data by Object.Name
summarize_data <- function(data, type_label) {
  data %>%
    group_by(Object.Name) %>%
    summarise(
      Average.Response = mean(Response, na.rm = TRUE),
      se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    ) %>%
    mutate(Type = type_label)
}

# Summarize positive and negative music and picture data
averages_pos_music <- summarize_data(pos_music_data, "Positive Valence Music")
averages_neg_music <- summarize_data(neg_music_data, "Negative Valence Music")
averages_pos_pic   <- summarize_data(pos_pic_data, "Positive Valence Pictures")
averages_neg_pic   <- summarize_data(neg_pic_data, "Negative Valence Pictures")

# Combine all summarized data
all_averages <- bind_rows(
  averages_pos_music,
  averages_neg_music,
  averages_pos_pic,
  averages_neg_pic
)

# Clean up Object.Name
all_averages$Object.Name <- gsub("Slider", "", all_averages$Object.Name)
all_averages$Object.Name <- trimws(all_averages$Object.Name)

# Factorize Object.Name based on predefined emotion order
emotion_order <- c("Gloomy", "Anxious", "Sad", "Scared", "Upset", "Excited", "Happy", "Joyful", "Relaxed", "Satisfied")
all_averages$Object.Name <- factor(all_averages$Object.Name, levels = emotion_order)

# Plot all emotions together
full_plot <- ggplot(all_averages, aes(x = Object.Name, y = Average.Response, color = Type)) +
  geom_point() +
  geom_errorbar(aes(ymin = Average.Response - se_value, ymax = Average.Response + se_value), 
                width = 0.2) +
  labs(title = "All Emotions - Mean Response by Stimulus Valence/Type", x = "Emotion", y = "Mean Response") +
  theme_bw() +
  ylim(0, 51)

# Save the plot
ggsave('../results/rating-task/study2/All_Emotion_Means_2_25_25.png', full_plot, width = 9)

all_averages$Type1 <- ifelse(grepl("Music", all_averages$Type),"Music", "Image" )

all_averages$Valence <- ifelse(grepl("Positive", all_averages$Type),"Positive", "Negative" )

summary_plot <- 
  ggplot(all_averages, aes(x = Valence, y = Average.Response, color=Type1)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0.025,linewidth=1,position=position_dodge(width=0.1)) +
  stat_summary(fun.data = 'mean_se', geom = 'pointrange', size=0.5,position=position_dodge(width=0.1)) + theme_bw() +
    theme(
    axis.text.x = element_text(family="Arial", size=24),
    axis.text.y = element_text(family="Arial",size=24),
    axis.title.x = element_text(family="Arial",size=30),
    axis.title.y = element_text(family="Arial",size=30),
    legend.position = "none")+
    scale_color_manual(values=c("#0072B2", "#D55E00" )) +
  scale_fill_manual(values=c("#0072B2","#D55E00"))+
  xlab("Emotion Valence") +
    ylab("Average Emotion Rating")

ggsave('../results/rating-task/Emotion_Category_Means_pervalencestimStudy2.png', summary_plot, width = 9, dpi=1000)
```

```{r}
all_averages$Category <- ifelse(all_averages$Object.Name %in% emotions$neg, "Negative Emotions", "Positive Emotions")

summary_df <- all_averages %>%
  group_by(Type, Category) %>%
  summarise(
    Average.Response = mean(Average.Response),
    Combined.SE = sqrt(sum(se_value^2) / n())
  )

summary_plot <- ggplot(summary_df, aes(x = Category, y = Average.Response, color = Type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = Average.Response - Combined.SE, ymax = Average.Response + Combined.SE), 
                width = 0.2) +
  labs(title = "Emotion Categories - Mean Response by Stimulus Valence/Type", x = "Emotion", y = "Mean") +
  theme_bw() +
  ylim(0, 51)

# Save the plots
ggsave('../results/rating-task/study2/Emotion_Category_Means_2_25_25.png', summary_plot, width = 9)

```

```{r}
# Function to summarize data by group
summarize_data <- function(data, group_var) {
  data %>%
    group_by(!!sym(group_var)) %>%
    summarise(
      Average.Response = mean(Response, na.rm = TRUE),
      se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    )
}

# Summarizing positive and negative music and picture data
averages_pos_music <- summarize_data(pos_music_data, "Spreadsheet..Audio")
averages_neg_music <- summarize_data(neg_music_data, "Spreadsheet..Audio")
averages_pos_pic   <- summarize_data(pos_pic_data, "Spreadsheet..Image")
averages_neg_pic   <- summarize_data(neg_pic_data, "Spreadsheet..Image")

# Combine all summaries and add labels
all_averages <- bind_rows(
  averages_pos_music %>% mutate(Type = "pos_music"),
  averages_neg_music %>% mutate(Type = "neg_music"),
  averages_pos_pic   %>% mutate(Type = "pos_pic"),
  averages_neg_pic   %>% mutate(Type = "neg_pic")
)

# Simplify Type labeling
all_averages <- all_averages %>%
  mutate(Type = case_when(
    Type %in% c("pos_music", "neg_music") ~ "Music",
    Type %in% c("pos_pic", "neg_pic") ~ "Picture"
  ))

# Plot all stimuli
all_stims_plotted <- ggplot(all_averages, aes(x = Type, y = Average.Response)) +
  geom_point() +
  geom_errorbar(aes(ymin = Average.Response - se_value, ymax = Average.Response + se_value), 
                alpha = 0.4, width = 0.2) +
  labs(title = "All Stimuli - Average Responses", x = "Stimulus Type", y = "Mean Response") +
  theme_bw()

# Save the plot
ggsave('../results/rating-task/study2/All_Stims_Means_2_25_25.png', all_stims_plotted, width = 14)

# Summarize collapsed stimulus types
collapsed_stims <- all_averages %>%
  group_by(Type) %>%
  summarise(
    Mean_Value = mean(Average.Response),
    Combined_SE = sqrt(sum(se_value^2) / n())  # Combining standard errors
  )

all_averages$Type[all_averages$Type == "Negative Valence Music" | all_averages$Type == "Positive Valence Music"] = "Music"
all_averages$Type[all_averages$Type == "Negative Valence Pictures" | all_averages$Type == "Positive Valence Pictures"] = "Picture"

collapsed_plot <- ggplot(collapsed_stims, aes(x = Type, y = Mean_Value, color = Mean_Value, label = round(Mean_Value, 2))) +
  geom_point() +
  geom_text(hjust=0, vjust=0) +
  geom_errorbar(aes(ymin = Mean_Value - Combined_SE, ymax = Mean_Value + Combined_SE, color = Mean_Value), alpha = 0.4, width = 0.2) +
  labs(title = "Stimulus Response Averages", x = "Stimulus Type", y = "Mean Response") +
  theme_bw()

ggsave('../results/rating-task/study2/Average_Stims_Means_2_25_25.png', collapsed_plot, width = 10)
```

##----Scoring ICC------
```{r}
# Function 1: ICC with Fisher transformation (without recoding)
compute_icc_fisher <- function(data_list) {
  sapply(data_list, function(data) {
    icc_result <- data %>%
      select(-Participant.Public.ID) %>%
      icc(model = "twoway", type = "consistency", unit = "average")
    
    -1 * fisherz(icc_result$value)  # Fisher transform and reverse score
  })
}

# Function 2: ICC with Fisher transformation and recoding of negative correlations
compute_icc_fisher_recode <- function(data_list) {
  sapply(data_list, function(data) {
    icc_result <- data %>%
      select(-Participant.Public.ID) %>%
      icc(model = "twoway", type = "consistency", unit = "average")
    
    # Recode correlations less than 0 as 0
    icc_value <- ifelse(icc_result$value < 0, 0, icc_result$value)
    
    # Fisher transformation and reverse scoring
    -1 * fisherz(icc_value)
  })
}

# Create lists of data frames split by Participant.Public.ID
music_negative_list <- split(music_negative, music_negative$Participant.Public.ID)
music_positive_list <- split(music_positive, music_positive$Participant.Public.ID)
pic_negative_list <- split(pic_negative, pic_negative$Participant.Public.ID)
pic_positive_list <- split(pic_positive, pic_positive$Participant.Public.ID)

### Result DataFrame 1: Using ICC with Fisher transformation
results_study2 <- data.frame(ID = names(music_negative_list))
results_study2$negmusicICC <- compute_icc_fisher(music_negative_list)
results_study2$posmusicICC <- compute_icc_fisher(music_positive_list)
results_study2$negpicICC <- compute_icc_fisher(pic_negative_list)
results_study2$pospicICC <- compute_icc_fisher(pic_positive_list)
results_study2$allmusicICC <- rowMeans(results_study2[, c("negmusicICC", "posmusicICC")], na.rm = TRUE)
results_study2$allpicICC <- rowMeans(results_study2[, c("negpicICC", "pospicICC")], na.rm = TRUE)

### Result DataFrame 2: Using ICC with Fisher transformation and recoding
results_study2_recode <- data.frame(ID = names(music_negative_list))
results_study2_recode$negmusicICC <- compute_icc_fisher_recode(music_negative_list)
results_study2_recode$posmusicICC <- compute_icc_fisher_recode(music_positive_list)
results_study2_recode$negpicICC <- compute_icc_fisher_recode(pic_negative_list)
results_study2_recode$pospicICC <- compute_icc_fisher_recode(pic_positive_list)
results_study2_recode$allmusicICC <- rowMeans(results_study2_recode[, c("negmusicICC", "posmusicICC")], na.rm = TRUE)
results_study2_recode$allpicICC <- rowMeans(results_study2_recode[, c("negpicICC", "pospicICC")], na.rm = TRUE)

```

## 10-9-24
```{r}
# Drop the ID column
music_neg_corr <- cor(music_negative[ , -c(1)])
pic_neg_corr <- cor(pic_negative[ , -c(1)])
music_positive <- music_positive[,c("Participant.Public.ID","happy","satisfied","relaxed", "joyful", "excited")]
music_pos_corr <- cor(music_positive[ , -c(1)]) 
pic_positive <- pic_positive[,c("Participant.Public.ID","happy","satisfied","relaxed", "joyful", "excited")]
pic_pos_corr <- cor(pic_positive[ , -c(1)])

# Plot heatmap for audio correlation
music_neg_corr_plot <- ggcorrplot(music_neg_corr, 
           method = "square", 
           type = "lower", 
           lab = TRUE, 
           show.diag = TRUE,
           lab_size = 10, 
           colors = c("blue", "white", "red"), 
           #title = "Correlations between Negative Emotion Ratings to Music",
           tl.cex = 20,
           ggtheme = theme_classic())

music_pos_corr_plot <- ggcorrplot(music_pos_corr, 
           method = "square", 
           type = "lower", 
           lab = TRUE, 
           show.diag = TRUE,
           lab_size = 10, 
           colors = c("blue", "white", "red"), 
           #title = "Correlations between Positive Emotion Ratings to Music",
           tl.cex = 20,
           ggtheme = theme_classic())

# Plot heatmap for image correlation
pic_neg_corr_plot <- ggcorrplot(pic_neg_corr, 
           method = "square", 
           type = "lower", 
           lab = TRUE, 
           show.diag = TRUE,
           lab_size = 10, 
           colors = c("blue", "white", "red"), 
           #title = "Correlations between Negative Emotion Ratings to Pictures",
           tl.cex = 20,
           ggtheme = theme_classic())

pic_pos_corr_plot <- ggcorrplot(pic_pos_corr, 
           method = "square", 
           type = "lower", 
           lab = TRUE, 
           show.diag = TRUE,
           lab_size = 10, 
           colors = c("blue", "white", "red"), 
           #title = "Correlations of Positive Emotion Responses to Pictures",
           tl.cex = 20,
           ggtheme = theme_classic())

ggsave('../results/rating-task/study2/Picture Negative Emotion Correlations_bothstudies.png', pic_neg_corr_plot, width = 9, dpi=1000)
ggsave('../results/rating-task/study2/Music Negative Emotion Correlations_bothstudies.png', music_neg_corr_plot, width = 9, dpi=1000)
ggsave('../results/rating-task/study2/Picture Positive Emotion Correlations_bothstudies.png', pic_pos_corr_plot, width = 9, dpi=1000)
ggsave('../results/rating-task/study2/Music Positive Emotion Correlations_bothstudies.png', music_pos_corr_plot, width = 9, dpi=1000)

```

# REMOVING OUTLIERS
```{r}
# results <- results %>%
#   filter(negpicICC < 1 & 
#          negmusicICC < 1 & 
#          pospicICC < 1 & 
#          posmusicICC < 1 & 
#          allpicICC < 1 & 
#          allmusicICC < 1)
```

##Plotting granularity scores for overall spread and correlations 
```{r}

# Function to create histogram plots
create_histogram <- function(data, key_vars, title, output_file) {
  df_long <- data %>%
    gather(key = "Variable", value = "Value", all_of(key_vars))
  
  hist_plot <- ggplot(df_long, aes(x = Value, fill = Variable)) +
    geom_histogram(position = "identity", alpha = 0.5) +
    labs(title = title, x = "Granularity Score", y = "Count") +
    theme_classic()
  
  ggsave(output_file, hist_plot, width = 14)
}

# Function to create correlation scatter plots with linear model fit
create_scatter_plot <- function(data, x_var, y_var, x_label, y_label, title, output_file) {
  scatter_plot <- ggplot(data, aes(x = !!ensym(x_var), y = !!ensym(y_var))) +
    geom_point() +
    stat_smooth(method = 'lm', formula = y ~ x) +
    xlab(x_label) +
    ylab(y_label) +
    ggtitle(title) +
    theme_classic() +
    theme(axis.title.x = element_text(size = 30),
          axis.title.y = element_text(size = 30),
          axis.text.x = element_text(size = 24),
          axis.text.y = element_text(size = 24))
          #plot.title = element_text(size = 16, face = 'bold', hjust = 0.5))
  
  ggsave(output_file, scatter_plot, width = 10)
}

# # Plotting histograms
# create_histogram(results_study2, c("negmusicICC", "negpicICC"), 
#                  "Negative Emotions - Granularity Scores (Fisher r to z)", 
#                  "../results/rating-task/study2/Negative_ICCs_2_25_25.png")
# 
# create_histogram(results_study2, c("posmusicICC", "pospicICC"), 
#                  "Positive Emotions - Granularity Scores (Fisher r to z)", 
#                  "../results/rating-task/study2/Positive_ICCs_2_25_25.png")
# 
# create_histogram(results_study2, c("allmusicICC", "allpicICC"), 
#                  "All Emotions - Granularity Scores (Fisher r to z)", 
#                  "../results/rating-task/study2/Combined_ICCs_2_25_25.png")

# Plotting histograms - recoded
#create_histogram(results_study2_recode, c("negmusicICC", "negpicICC"), 
                 #"Negative Emotional Granularity Scores", 
                 #"../results/rating-task/final/study2/Negative_ICCs_Final_2_28.png",
                 #labels = c("Music", "Picture"))

#create_histogram(results_study2_recode, c("posmusicICC", "pospicICC"), 
                 #"Positive Emotional Granularity Scores", 
                 #"../results/rating-task/final/study2/Positive_ICCs_Final_2_28.png",
                 #labels = c("Music", "Picture"))

#create_histogram(results_study2_recode, c("allmusicICC", "allpicICC"), 
                 #"Combined Emotional Granularity Scores", 
                 #"../results/rating-task/final/study2/Combined_ICCs_Final_2_28.png",
                 #labels = c("Music", "Picture"))

# # Plotting correlation scatter plots
# create_scatter_plot(results_study2, "negpicICC", "negmusicICC", 
#                     "Negative Emotion Granularity (Pictures)", 
#                     "Negative Emotion Granularity (Music)", 
#                     "Correlation of Negative Emotion Granularity Scores (Fisher r to z)", 
#                     "../results/rating-task/study2/Neg_Graph_2_25_25.png")
# 
# create_scatter_plot(results_study2, "pospicICC", "posmusicICC", 
#                     "Positive Emotion Granularity (Pictures)", 
#                     "Positive Emotion Granularity (Music)", 
#                     "Correlation of Positive Emotion Granularity Scores (Fisher r to z)", 
#                     "../results/rating-task/study2/Pos_Graph_2_25_25.png")
# 
# create_scatter_plot(results_study2, "allpicICC", "allmusicICC", 
#                     "Combined Emotion Granularity (Pictures)", 
#                     "Combined Emotion Granularity (Music)", 
#                     "Correlation of Combined Emotion Granularity Scores (Fisher r to z)", 
#                     "../results/rating-task/study2/Combined_Graph_2_25_25.png")

# Plotting correlation scatter plots - Recoded
create_scatter_plot(results_study2_recode, "negpicICC", "negmusicICC", 
                    "Negative Emotional\nGranularity (Pictures)", 
                    "Negative Emotional\nGranularity (Music)", 
                    "", 
                    "../results/rating-task/final/study2/Neg_Graph_Final_3_10.png")

create_scatter_plot(results_study2_recode, "pospicICC", "posmusicICC", 
                    "Positive Emotional\nGranularity (Pictures)", 
                    "Positive Emotional\nGranularity (Music)", 
                    "", 
                    "../results/rating-task/final/study2/Pos_Graph_Final_3_10.png")

create_scatter_plot(results_study2_recode, "allpicICC", "allmusicICC", 
                    "Combined Emotional Granularity (Pictures)", 
                    "Combined Emotional Granularity (Music)", 
                    "Correlation of Combined Emotional Granularity Scores", 
                    "../results/rating-task/final/study2/Combined_Graph_Final_2_28.png")
```

```{r}
# Function to perform correlations and paired t-tests
run_tests <- function(data, label) {
  cat(paste0("Results for ", label, ":\n"))
  cat("Correlations:\n")
  cor.test(data$posmusicICC, data$pospicICC) %>% print()
  cor.test(data$negmusicICC, data$negpicICC) %>% print()
  cor.test(data$allmusicICC, data$allpicICC) %>% print()
  
  cat("\nPaired T-tests:\n")
  t.test(data$posmusicICC, data$pospicICC, paired = TRUE) %>% print()
  t.test(data$negmusicICC, data$negpicICC, paired = TRUE) %>% print()
  t.test(data$allmusicICC, data$allpicICC, paired = TRUE) %>% print()
}

# # Function to create and save mean comparison plot
# create_mean_comparison_plot <- function(data, title, output_file) {
#   mean_comparison <- data %>%
#     pivot_longer(negmusicICC:allpicICC) %>%
#     ggplot(aes(x = name, y = value)) +
#     stat_summary(fun.data = 'mean_cl_normal', geom = 'errorbar', width = 0.2) +
#     stat_summary(fun.data = 'mean_cl_normal', geom = 'pointrange', width = 0.2) +
#     theme_bw() +
#     xlab('Stimulus and Valence') +
#     ylab('Average Emotion Granularity') +
#     ggtitle(title) +
#     theme(axis.title.x = element_text(size = 14, face = 'bold'),
#           axis.title.y = element_text(size = 14, face = 'bold'),
#           axis.text.x = element_text(size = 12),
#           axis.text.y = element_text(size = 12)) +
#     scale_x_discrete(labels = c('Negative Music', 'Negative Picture', 'Positive Music', 'Positive Picture'))
#   
#   ggsave(output_file, mean_comparison, width = 9)
# }

# # Run tests and create plots for non-recoded data
# run_tests(results_study2, "Non-Recoded Data")
# create_mean_comparison_plot(results_study2, 
#                             'Average Granularity Scores by Stimulus Type/Valence (Fisher r to z)', 
#                             '../results/rating-task/study2/Mean_Comparisons_2_25_25.png')

# Run tests and create plots for recoded data
run_tests(results_study2_recode, "Recoded Data")
create_mean_comparison_plot(results_study2_recode, 
                            'Average Granularity Scores by Stimulus Type and Valence', 
                            '../results/rating-task/final/study2/Mean_Comparisons_Final_2_28.png')

results_study2_recode1 <- results_study2_recode %>%
    pivot_longer(negmusicICC:pospicICC)

results_study2_recode1$stim <- str_replace(results_study2_recode1$name, "ICC", "")
results_study2_recode1$valence <- str_replace(results_study2_recode1$stim, "music", "")
results_study2_recode1$valence <- str_replace(results_study2_recode1$valence, "pic", "")
results_study2_recode1$stim <- str_replace(results_study2_recode1$stim, "neg", "")
results_study2_recode1$stim <- str_replace(results_study2_recode1$stim, "pos", "")
results_study2_recode1 <- 
  results_study2_recode1 %>%
  mutate(stim = recode(stim, "music" = "Music", "pic" = "Pictures")) %>%
  mutate(valence = recode(valence, "neg" = "Negative", "pos" = "Positive"))

poster_means<-
  ggplot(data=results_study2_recode1, aes(x=valence, y=value, color=stim))+
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0.015, size=0.75) +
  stat_summary(fun.data = 'mean_se', geom = 'pointrange', width = 0.015, size=0.5) +
  scale_color_manual(values=c("#0072B2", "#D55E00" )) +
  scale_fill_manual(values=c("#0072B2","#D55E00")) +
  xlab("Emotional Granularity Valence") +
  ylab("Emotional Granularity Score") +
  theme_bw() +
  theme(axis.title.x = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          axis.text.x = element_text(size = 18),
          axis.text.y = element_text(size = 18),
        legend.position = "none") 
  

ggsave('../results/rating-task/final/Mean_Comparisons_Final_3_10_study2.png', poster_means, width=10, dpi=1000)
```


##Power analysis
```{r}

# Function to calculate effect size (Cohen's d)
effect_size <- function(x, y) {
  mean_diff <- mean(x - y, na.rm = TRUE)
  sd_diff <- sd(x - y, na.rm = TRUE)
  return(mean_diff / sd_diff)
}

# Function to perform power analysis for paired t-tests
power_analysis_t_test <- function(x, y, alpha = 0.05, power = 0.80) {
  d <- effect_size(x, y)
  sample_size <- pwr.t.test(d = d, power = power, sig.level = alpha, type = "paired")$n
  return(list(effect_size = d, sample_size = ceiling(sample_size)))
}

# Function to perform power analysis for correlations with clear output
power_analysis_correlation <- function(x, y, alpha = 0.05, power = 0.80) {
  cor_test <- cor.test(x, y, method = "pearson")
  r <- cor_test$estimate
  power_analysis <- pwr.r.test(r = r, sig.level = alpha, power = power)
  sample_size <- ceiling(power_analysis$n)
  
  # Displaying the result in a clear output
  cat("Correlation Analysis:\n")
  cat("Correlation coefficient (r):", round(r, 2), "\n")
  cat("Required sample size for 80% power:", sample_size, "\n")
  cat("Power analysis details:\n")
  print(power_analysis)
  return(list(correlation = r, sample_size = sample_size, power_analysis = power_analysis))
}

# Power analysis for positive granularity scores
pos_t_test <- power_analysis_t_test(results_study2$posmusicICC, results_study2$pospicICC)
paste("Effect size for positive granularity: ", round(pos_t_test$effect_size, 2), 
      "--> N =", pos_t_test$sample_size, "for 80% power.")

# Power analysis for negative granularity scores
neg_t_test <- power_analysis_t_test(results_study2$negmusicICC, results_study2$negpicICC)
paste("Effect size for negative granularity: ", round(neg_t_test$effect_size, 2), 
      "--> N =", neg_t_test$sample_size, "for 80% power.")

# Power analysis for combined granularity scores
all_t_test <- power_analysis_t_test(results_study2$allmusicICC, results_study2$allpicICC)
paste("Effect size for combined granularity: ", round(all_t_test$effect_size, 2), 
      "--> N =", all_t_test$sample_size, "for 80% power.")

# Power analysis for correlations with clear output
cat("\nNegative Granularity Correlation Analysis:\n")
neg_corr_analysis <- power_analysis_correlation(results_study2$negmusicICC, results_study2$negpicICC)

cat("\nPositive Granularity Correlation Analysis:\n")
pos_corr_analysis <- power_analysis_correlation(results_study2$posmusicICC, results_study2$pospicICC)

cat("\nCombined Granularity Correlation Analysis:\n")
all_corr_analysis <- power_analysis_correlation(results_study2$allmusicICC, results_study2$allpicICC)
```

```{r}
#### FOR RECODED SCORES
# Power analysis for positive granularity scores
print('FOR RECODED SCORES')
pos_t_test_recode <- power_analysis_t_test(results_study2_recode$posmusicICC, results_study2_recode$pospicICC)
paste("Effect size for positive granularity: ", round(pos_t_test_recode$effect_size, 2), 
      "--> N =", pos_t_test_recode$sample_size, "for 80% power.")

# Power analysis for negative granularity scores
neg_t_test_recode <- power_analysis_t_test(results_study2_recode$negmusicICC, results_study2_recode$negpicICC)
paste("Effect size for negative granularity: ", round(neg_t_test_recode$effect_size, 2), 
      "--> N =", neg_t_test_recode$sample_size, "for 80% power.")

# Power analysis for combined granularity scores
all_t_test_recode <- power_analysis_t_test(results_study2_recode$allmusicICC, results_study2_recode$allpicICC)
paste("Effect size for combined granularity: ", round(all_t_test_recode$effect_size, 2), 
      "--> N =", all_t_test_recode$sample_size, "for 80% power.")

# Power analysis for correlations with clear output
cat("\nNegative Granularity Correlation Analysis:\n")
neg_corr_analysis_recode <- power_analysis_correlation(results_study2_recode$negmusicICC, results_study2_recode$negpicICC)

cat("\nPositive Granularity Correlation Analysis:\n")
pos_corr_analysis_recode <- power_analysis_correlation(results_study2_recode$posmusicICC, results_study2_recode$pospicICC)

cat("\nCombined Granularity Correlation Analysis:\n")
all_corr_analysis_recode <- power_analysis_correlation(results_study2_recode$allmusicICC, results_study2_recode$allpicICC)
```

##descriptive statistics
```{r}
summary_stats <- function(df) {
  stats <- data.frame(
    Variable = colnames(df),
    Mean = sapply(df, function(x) round(mean(x, na.rm = TRUE), 2)),
    SD = sapply(df, function(x) round(sd(x, na.rm = TRUE), 2)),
    Min = sapply(df, function(x) min(x, na.rm = TRUE)),
    Max = sapply(df, function(x) max(x, na.rm = TRUE))
  )
  return(stats)
}

# Apply function to results_recode dataframe
summary_results_study2 <- summary_stats(results_study2_recode)

# Print results
print(summary_results_study2)

```