---
title: "Final_Study_2_Scoring"
output: html_document
date: "2025-02-26"
---

#replace "df" in script w/ dataframe name of survey.csv
```{r}
library(tidyverse)
library(corrplot)
source("reverseCode.R")

surveys_study2 <- read.csv("../data/redcap/TEAMYAInPersonSurvey_DATA_2025-02-25_1539.csv") %>%
  filter(participant_id %in% results_study2$ID)

missing_goldmsi <- c("TEAM_YA_003","TEAM_YA_013","TEAM_YA_022","TEAM_YA_023","TEAM_YA_030","TEAM_YA_031")

followup_surveys <- read.csv("../data/qualtrics/granularity followup surveys_February 26, 2025_11.46.csv") %>%
  select(c("gmsi39", "id")) %>%
  mutate(id = ifelse(grepl("^5", id), 
                               paste0("TEAM_YA_0", substr(id, 2, nchar(id))), 
                               id)) %>%
  filter(id %in% missing_goldmsi)

# Update goldmsi_39_v2 in surveys_study2 using matching id values from followup_surveys
surveys_study2 <- surveys_study2 %>%
  left_join(followup_surveys, by = c("participant_id" = "id")) %>%
  mutate(goldmsi_39_v2 = ifelse(!is.na(gmsi39), gmsi39, goldmsi_39_v2)) %>%
  select(-gmsi39) %>% # Remove the gmsi39 column after merging
  mutate(goldmsi_39_v2 = as.integer(goldmsi_39_v2))  # Ensure it's stored as integers
  
final_scores_study2 <- surveys_study2 %>%
  select("participant_id") %>%
  rename(SURVEY_CODE = participant_id)
  
```

#STAI - NOT IN STUDY 2
```{r}
# STAI <- df %>%
#   select("SURVEY_CODE", "STAI1_1":"STAI20_1")
# 
# STAI[,-1] <- lapply(STAI[,-1], as.integer)
# 
# cols_reverse <- c("STAI1_1","STAI3_1","STAI6_1","STAI7_1","STAI10_1","STAI13_1","STAI14_1","STAI16_1","STAI19_1")
# STAI[cols_reverse] <- lapply(STAI[cols_reverse], reverseCode, min=1, max=4)
# 
# STAI$STAI_total <- apply(STAI[,-1],1,sum)
# 
# final_scores_study2 <- merge(final_scores_study2, STAI[, c(1, ncol(STAI))], by.x = "SURVEY_CODE", by.y = "SURVEY_CODE", all.x = TRUE)
# hist(final_scores_study2$STAI_total)
```

#CD-RISC - NOT IN STUDY 2
```{r}
# CD.RISC <- df %>%
#   select("SURVEY_CODE", "CD.RISC1_1":"CD.RISC10_1")
# 
# CD.RISC[ ,-1] <- lapply(CD.RISC[,-1], as.integer)
# 
# CD.RISC$CD.RISC_total <- apply(CD.RISC[,-1],1,sum)
# 
# final_scores_study2 <- merge(final_scores_study2, CD.RISC[, c(1, ncol(CD.RISC))], by.x = "SURVEY_CODE", by.y = "SURVEY_CODE", all.x = TRUE)
# 
# hist(final_scores_study2$CD.RISC_total)
```

#GoldMSI Scoring
```{r}
# Gold <- df %>%
#   select("SURVEY_CODE", "Q1.1_1":"Q1.38")

Gold_study_2 <- surveys_study2 %>%
  # excluding write-in question
  select("participant_id", "goldmsi_1_v2":"goldmsi_37_v2", "goldmsi_39_v2") %>%
  rename(
    SURVEY_CODE = participant_id,
    Q1.1_1 = goldmsi_1_v2,
    Q1.2_1 = goldmsi_2_v2,
    Q1.3_1 = goldmsi_3_v2,
    Q1.4_1 = goldmsi_4_v2,
    Q1.5_1 = goldmsi_5_v2,
    Q1.6_1 = goldmsi_6_v2,
    Q1.7_1 = goldmsi_7_v2,
    Q1.8_1 = goldmsi_8_v2,
    Q1.9_1 = goldmsi_9_v2,
    Q1.10_1 = goldmsi_10_v2,
    Q1.11_1 = goldmsi_11_v2,
    Q1.12_1 = goldmsi_12_v2,
    Q1.13_1 = goldmsi_13_v2,
    Q1.14_1 = goldmsi_14_v2,
    Q1.15_1 = goldmsi_15_v2,
    Q1.16_1 = goldmsi_16_v2,
    Q1.17_1 = goldmsi_17_v2,
    Q1.18_1 = goldmsi_18_v2,
    Q1.19_1 = goldmsi_19_v2,
    Q1.20_1 = goldmsi_20_v2,
    Q1.21_1 = goldmsi_21_v2,
    Q1.22_1 = goldmsi_22_v2,
    Q1.23_1 = goldmsi_23_v2,
    Q1.24_1 = goldmsi_24_v2,
    Q1.25_1 = goldmsi_25_v2,
    Q1.26_1 = goldmsi_26_v2,
    Q1.27_1 = goldmsi_27_v2,
    Q1.28_1 = goldmsi_28_v2,
    Q1.29_1 = goldmsi_29_v2,
    Q1.30_1 = goldmsi_30_v2,
    Q1.31_1 = goldmsi_31_v2,
    Q1.32 = goldmsi_39_v2, # this one was left out from redcap initially, need to swap order here
    Q1.33 = goldmsi_32_v2,
    Q1.34 = goldmsi_33_v2,
    Q1.35 = goldmsi_34_v2,
    Q1.36 = goldmsi_35_v2,
    Q1.37 = goldmsi_36_v2,
    Q1.38 = goldmsi_37_v2,
  )

# #delete atttention checking question
# Gold$Qcheck <- NULL
# 
# Gold[, -1] <- lapply(Gold[, -1], as.integer)

# Gold_study_2 <- bind_rows(Gold, Gold_redcap)

# GoldMSI columns to reverse code and sub-score (for these questions, the correct answer (ie the more positive answer) is a higher number. Negative questions are reverse coded.) 

cols_reverse <- c("Q1.21_1" ,
"Q1.11_1" ,
"Q1.13_1" ,
"Q1.23_1" ,
"Q1.14_1" ,
"Q1.27_1" ,
"Q1.17_1" ,
"Q1.25_1" ,
"Q1.9_1")

cols_activeengagement <- c("Q1.1_1" ,
"Q1.3_1" ,
"Q1.8_1" ,
"Q1.15_1" ,
"Q1.21_1" ,
"Q1.24_1" ,
"Q1.28_1" ,
"Q1.34" ,
"Q1.38")

cols_perceptualabilities <- c("Q1.5_1" ,
"Q1.6_1" ,
"Q1.11_1" ,
"Q1.12_1" ,
"Q1.13_1" ,
"Q1.18_1" ,
"Q1.22_1" ,
"Q1.23_1" ,
"Q1.26_1")

cols_musicaltraining <- c("Q1.14_1" , "Q1.27_1",
"Q1.32" ,
"Q1.33" , ## think about how this is scored? doesn't seem like a lot of people answered
"Q1.35" ,
"Q1.36" ,
"Q1.37")


cols_singingabilities <- c("Q1.4_1" ,
"Q1.7_1" ,
"Q1.10_1" ,
"Q1.17_1" ,
"Q1.25_1" ,
"Q1.29_1" ,
"Q1.30_1")

cols_emotion <- c("Q1.2_1" ,
"Q1.9_1" ,
"Q1.16_1" ,
"Q1.19_1" ,
"Q1.20_1" ,
"Q1.31_1")

cols_musicalsophistication <- c("Q1.1_1" ,
           "Q1.3_1" ,
"Q1.4_1" ,
"Q1.7_1" ,
"Q1.10_1" ,
"Q1.12_1" ,
"Q1.14_1" ,
"Q1.15_1" ,
"Q1.17_1" ,
"Q1.19_1" ,
"Q1.23_1" ,
"Q1.24_1" ,
"Q1.25_1" ,
"Q1.27_1" ,
"Q1.29_1" ,
"Q1.32" ,
"Q1.33")

# Reverse code

Gold_study_2[cols_reverse] <- lapply(Gold_study_2[cols_reverse], reverseCode, min=1, max=7)

# Add sub-scores and total to main df

Gold_study_2$Gold_total <- apply(Gold_study_2[, -1],1, sum)/38 # total GoldMSI score
Gold_study_2$Gold_activeengagement <- apply(Gold_study_2[cols_activeengagement], 1,sum)/9
Gold_study_2$Gold_perceptualabilities <- apply(Gold_study_2[cols_perceptualabilities],1, sum)/9
Gold_study_2$Gold_musicaltraining <-apply(Gold_study_2[cols_musicaltraining],1, sum)/7
Gold_study_2$Gold_singingabilities <- apply(Gold_study_2[cols_singingabilities],1, sum)/7
Gold_study_2$Gold_emotion <- apply(Gold_study_2[cols_emotion],1, sum)/6
Gold_study_2$Gold_musicalsophistication <- apply(Gold_study_2[cols_musicalsophistication],1, sum)/18

final_scores_study2 <- merge(final_scores_study2, Gold_study_2[, c(1, 40:46)], by.x = "SURVEY_CODE", by.y = "SURVEY_CODE", all.x = TRUE)

hist(final_scores_study2$Gold_total)
```

#eBMRQ
```{r}
# bmrq <- df %>%
#   select("SURVEY_CODE", "Q2_1":"Q21_1", "Q23_1":"Q26_1")
# 
# bmrq[,-1] <- lapply(bmrq[,-1], as.integer)

#need to add aims_3 as Q23, aims_13 as Q24, aims_15 as Q25, aims_29 as Q26
bmrq_study_2 <- surveys_study2 %>%
  select("participant_id", "ebmrq_1":"ebmrq_20", "aims_3", "aims_13", "aims_15", "aims_29") %>%
  rename(
    SURVEY_CODE = participant_id,
    Q2_1 = ebmrq_1,
    Q3_1 = ebmrq_2,
    Q4_1 = ebmrq_3,
    Q5_1 = ebmrq_4,
    Q6_1 = ebmrq_5,
    Q7_1 = ebmrq_6,
    Q8_1 = ebmrq_7,
    Q9_1 = ebmrq_8,
    Q10_1 = ebmrq_9,
    Q11_1 = ebmrq_10,
    Q12_1 = ebmrq_11,
    Q13_1 = ebmrq_12,
    Q14_1 = ebmrq_13,
    Q15_1 = ebmrq_14,
    Q16_1 = ebmrq_15,
    Q17_1 = ebmrq_16,
    Q18_1 = ebmrq_17,
    Q19_1 = ebmrq_18,
    Q20_1 = ebmrq_19,
    Q21_1 = ebmrq_20,
    Q23_1 = aims_3,
    Q24_1 = aims_13,
    Q25_1 = aims_15,
    Q26_1 = aims_29
  )

# bmrq[, -1] <- lapply(bmrq[, -1], as.integer)
# 
# bmrq_study_2 <- bind_rows(bmrq, bmrq_redcap)

# BMRQ columns to reverse code and sub-score
cols_reverse <- c("Q3_1",
                  "Q6_1")

cols_emotion <- c("Q4_1",
  "Q9_1",
  "Q13_1",
  "Q19_1")

cols_sensorimotor <-c("Q6_1",
  "Q11_1",
  "Q16_1",
  "Q21_1")
                      
cols_moodreg <- c("Q5_1",
  "Q10_1",
  "Q15_1",
  "Q20_1")

cols_musicseek <- c("Q3_1",
  "Q8_1",
  "Q12_1",
  "Q18_1")

cols_socialreward <-c("Q2_1",
  "Q7_1",
  "Q14_1",
  "Q17_1")

cols_absorption <- c("Q23_1", "Q24_1", "Q25_1", "Q26_1")

# Reverse code
bmrq_study_2[cols_reverse] <- lapply(bmrq_study_2[cols_reverse], reverseCode)

# Add sub-scores and total to main df
bmrq_study_2$eBMRQ_total <- apply(bmrq_study_2[,-1],1, sum) 
bmrq_study_2$BMRQ_emotion <- apply(bmrq_study_2[cols_emotion], 1,sum)
bmrq_study_2$BMRQ_sensorimotor <- apply(bmrq_study_2[cols_sensorimotor],1, sum)
bmrq_study_2$BMRQ_moodreg <-apply(bmrq_study_2[cols_moodreg],1, sum)
bmrq_study_2$BMRQ_musicseek <- apply(bmrq_study_2[cols_musicseek],1, sum)
bmrq_study_2$BMRQ_socialreward <- apply(bmrq_study_2[cols_socialreward],1, sum)
bmrq_study_2$BMRQ_absorption<- apply(bmrq_study_2[cols_absorption],1, sum)

final_scores_study2 <- merge(final_scores_study2, bmrq_study_2[, c(1, 26:32)], by.x = "SURVEY_CODE", by.y = "SURVEY_CODE", all.x = TRUE)

hist(final_scores_study2$eBMRQ_total)
```

#BDI --> items asking about changes in appetite (BDI_17) and sleep (BDI_15) need to be scored differently (see Attachment_AU in named attachments folder - there are two answers for both 1, 2, and 3 scores; also the responses should range from 0 to 3 )
```{r}
# BDI <- df %>%
#   select("SURVEY_CODE", "BDI_1":"BDI_20")
# 
# BDI[, -1] <- lapply(BDI[, -1], as.integer)

BDI_study_2 <- surveys_study2 %>%
  select("participant_id", "bdi_1":"bdi_20") %>%
  rename(
    SURVEY_CODE = participant_id,
    BDI_1 = bdi_1,
    BDI_2 = bdi_2,
    BDI_3 = bdi_3,
    BDI_4 = bdi_4,
    BDI_5 = bdi_5,
    BDI_6 = bdi_6,
    BDI_7 = bdi_7,
    BDI_8 = bdi_8,
    BDI_9 = bdi_9,
    BDI_10 = bdi_10,
    BDI_11 = bdi_11,
    BDI_12 = bdi_12,
    BDI_13 = bdi_13,
    BDI_14 = bdi_14,
    BDI_15 = bdi_15,
    BDI_16 = bdi_16,
    BDI_17 = bdi_17,
    BDI_18 = bdi_18,
    BDI_19 = bdi_19,
    BDI_20 = bdi_20
  )

# BDI_study_2 <- bind_rows(BDI, BDI_redcap)

BDI_study_2$BDI_15[BDI_study_2$BDI_15 == 3] <- 2
BDI_study_2$BDI_15[BDI_study_2$BDI_15 == 4 | BDI_study_2$BDI_15 == 5] <- 3
BDI_study_2$BDI_15[BDI_study_2$BDI_15 == 6 | BDI_study_2$BDI_15 == 7] <- 4

BDI_study_2$BDI_17[BDI_study_2$BDI_17 == 3] <- 2
BDI_study_2$BDI_17[BDI_study_2$BDI_17 == 4 | BDI_study_2$BDI_17 == 5] <- 3
BDI_study_2$BDI_17[BDI_study_2$BDI_17 == 6 | BDI_study_2$BDI_17 == 7] <- 4

BDI_study_2[BDI_study_2 == 1] <- 0
BDI_study_2[BDI_study_2 == 2] <- 1
BDI_study_2[BDI_study_2 == 3] <- 2
BDI_study_2[BDI_study_2 == 4] <- 3

BDI_study_2$BDI_total <- apply(BDI_study_2[,-1], 1, sum)

final_scores_study2 <- merge(final_scores_study2, BDI_study_2[, c(1, 22)], by.x = "SURVEY_CODE", by.y = "SURVEY_CODE", all.x = TRUE)

hist(final_scores_study2$BDI_total)
```

#M@H
```{r}
# MH <- df %>%
#   select("SURVEY_CODE", "M.H_child1_1":"M.H_child20_1")
# 
# MH <- MH[complete.cases(MH),]
# MH[,-1] <- lapply(MH[,-1], as.integer)

MH_study_2 <- surveys_study2 %>%
  select("participant_id", "mhr_1":"mhr_20") %>%
  rename(
    SURVEY_CODE = participant_id,
    M.H_child1_1 = mhr_1,
    M.H_child2_1 = mhr_2,
    M.H_child3_1 = mhr_3,
    M.H_child4_1 = mhr_4,
    M.H_child5_1 = mhr_5,
    M.H_child6_1 = mhr_6,
    M.H_child7_1 = mhr_7,
    M.H_child8_1 = mhr_8,
    M.H_child9_1 = mhr_9,
    M.H_child10_1 = mhr_10,
    M.H_child11_1 = mhr_11,
    M.H_child12_1 = mhr_12,
    M.H_child13_1 = mhr_13,
    M.H_child14_1 = mhr_14,
    M.H_child15_1 = mhr_15,
    M.H_child16_1 = mhr_16,
    M.H_child17_1 = mhr_17,
    M.H_child18_1 = mhr_18,
    M.H_child19_1 = mhr_19,
    M.H_child20_1 = mhr_20
  )

# MH_study_2 <- bind_rows(MH, MH_redcap)

cols_reverse <- c("M.H_child6_1","M.H_child7_1","M.H_child11_1","M.H_child12_1","M.H_child18_1","M.H_child19_1","M.H_child20_1")
MH_study_2[cols_reverse] <- lapply(MH_study_2[cols_reverse], reverseCode, min=1, max=7)

MH_study_2$MH_total <- apply(MH_study_2[,-1],1, sum) # total M@H scores

final_scores_study2 <- merge(final_scores_study2, MH_study_2[, c(1, 22)], by.x = "SURVEY_CODE", by.y = "SURVEY_CODE", all.x = TRUE)

hist(final_scores_study2$MH_total)


# # started putting these together but I'm not sure what goes where
# cols_caregiverbeliefs <- c("M.H_child1_1", "M.H_child2_1", "M.H_child3_1", "M.H_child4_1")
# 
# cols_caregiversinging <- c("M.H_child9_1")
# 
# cols_childhoodattitude <- c("M.H_child8_1")
# 
# cols_socialcontexts <- c("")
# 
# cols_musicmaking <- c("M.H_child5_1", "M.H_child6_1", "M.H_child7_1")
# 
# df$MH_caregiverbeliefs <- apply(MH[cols_caregiverbeliefs], 1,sum)
# df$MH_caregiversinging <- apply(MH[cols_caregiversinging],1, sum)
# df$MH_childhoodattitude <-apply(MH[cols_childhoodattitude],1, sum)
# df$MH_socialcontexts <- apply(MH[cols_socialcontexts],1, sum)
# df$MH_musicmaking <- apply(MH[cols_musicmaking],1, sum)
```

#RDEES
```{r}
# rdees <- df %>%
#   select("SURVEY_CODE", "RDEES_1_1":"RDEES_14_1")
# 
# rdees[,-1] <- lapply(rdees[,-1], as.integer)

rdees_study_2 <- surveys_study2 %>%
  select("participant_id", "rdees_1":"rdees_14") %>%
  rename(
    SURVEY_CODE = participant_id,
    RDEES_1_1 = rdees_1,
    RDEES_2_1 = rdees_2,
    RDEES_3_1 = rdees_3,
    RDEES_4_1 = rdees_4,
    RDEES_5_1 = rdees_5,
    RDEES_6_1 = rdees_6,
    RDEES_7_1 = rdees_7,
    RDEES_8_1 = rdees_8,
    RDEES_9_1 = rdees_9,
    RDEES_10_1 = rdees_10,
    RDEES_11_1 = rdees_11,
    RDEES_12_1 = rdees_12,
    RDEES_13_1 = rdees_13,
    RDEES_14_1 = rdees_14
  )

# rdees_study_2 <- bind_rows(rdees, rdees_redcap)

cols_reverse <- c("RDEES_1_1","RDEES_5_1","RDEES_9_1", "RDEES_11_1")

rdees_study_2[cols_reverse] <- lapply(rdees_study_2[cols_reverse], reverseCode, min=1, max=5)

cols_range <- c("RDEES_1_1","RDEES_3_1","RDEES_5_1","RDEES_7_1", "RDEES_9_1", "RDEES_11_1", "RDEES_13_1")
cols_differentation <- c("RDEES_2_1","RDEES_4_1","RDEES_6_1","RDEES_8_1", "RDEES_10_1", "RDEES_12_1", "RDEES_14_1")

rdees_study_2$rdees_range <- apply(rdees_study_2[cols_range], 1,sum)
rdees_study_2$rdees_differentiation <- apply(rdees_study_2[cols_differentation],1, sum)
rdees_study_2$rdees_total <- rdees_study_2$rdees_differentiation + rdees_study_2$rdees_range

final_scores_study2 <- merge(final_scores_study2, rdees_study_2[, c(1, 16:18)], by.x = "SURVEY_CODE", by.y = "SURVEY_CODE", all.x = TRUE)

hist(final_scores_study2$rdees_total)
```

## REMOVE THE SECOND OPTION IF THERE ARE DUPLICATES
```{r}
# # Check for duplicates in the SURVEY_CODE column and keep only the first occurrence
# df_unique <- df[!duplicated(df$SURVEY_CODE), ]
# 
# # If you want to see the duplicate entries that were removed
# duplicates <- df[duplicated(df$SURVEY_CODE), ]
# 
# # Display the result
# print(df_unique)
# print(duplicates)
```


```{r}
# # Find SURVEY_CODE in scores that do not match any ID in results
# non_matching_in_scores <- final_scores_study2[!final_scores_study2$SURVEY_CODE %in% results$ID, ]
# 
# # Find ID in results that do not match any SURVEY_CODE in scores
# non_matching_in_results <- results[!results$ID %in% final_scores_study2$SURVEY_CODE, ]
# 
# # Display the non-matching entries
# print("SURVEY_CODEs in scores that do not match any ID in results:")
# print(non_matching_in_scores)
# 
# print("IDs in results that do not match any SURVEY_CODE in scores:")
# print(non_matching_in_results)

```

## MERGE WITH ICC SCORING
```{r}
merged_df_study2 <- merge(final_scores_study2, results_study2, by.x = "SURVEY_CODE", by.y = "ID", all = FALSE)
merged_df_study2_recoded <- merge(final_scores_study2, results_study2_recode, by.x = "SURVEY_CODE", by.y = "ID", all = FALSE)
```

#correlations
```{r}
# Select only the numeric columns for the correlation matrix
numeric_columns <- merged_df_study2[, sapply(merged_df_study2, is.numeric)]
numeric_columns_recoded <- merged_df_study2_recoded[, sapply(merged_df_study2_recoded, is.numeric)]

# Calculate the correlation matrix
correlation_matrix <- cor(numeric_columns, use = "complete.obs")
correlation_matrix_recoded <- cor(numeric_columns_recoded, use = "complete.obs")

# Function to compute significance levels
cor.mtest <- function(mat, conf.level = 0.95) {
  mat <- as.matrix(mat)
  n <- ncol(mat)
  p.mat <- matrix(NA, n, n)
  diag(p.mat) <- 0
  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      tmp <- cor.test(mat[, i], mat[, j], conf.level = conf.level)
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
    }
  }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}

# Compute p-values
p_values <- cor.mtest(numeric_columns)
p_values_recoded <- cor.mtest(numeric_columns_recoded)

# Specify the folder where you want to save the file
output_folder <- "../results/qualtrics/study2/"

# Combine the folder path with the file name
output_file <- file.path(output_folder, "Significant Correlations Plot Study 2 (without Recoding ICC) 2-26-25.png")

# Open a PNG device with the specified file path
png(output_file, width = 800, height = 800)

# Generate the corrplot
corrplot(correlation_matrix, method = "circle", type = "upper", 
         p.mat = p_values, sig.level = 0.05, insig = "blank",
         tl.col = "black", tl.srt = 45, addCoef.col = NULL,
         col = colorRampPalette(c("blue", "white", "red"))(200))

title(main = "Significant Correlations Study 2 (without Recoding Granularity Scores)", col.main = "black", font.main = 4)

# Close the PNG device
dev.off()

# Specify the folder where you want to save the file
output_folder <- "../results/qualtrics/study2/"

# Combine the folder path with the file name
output_file <- file.path(output_folder, "Significant Correlations Plot Study 2 (with Recoding ICC) 2-26-25.png")

# Open a PNG device with the specified file path
png(output_file, width = 800, height = 800)

# Generate the corrplot
corrplot(correlation_matrix_recoded, method = "circle", type = "upper", 
         p.mat = p_values, sig.level = 0.05, insig = "blank",
         tl.col = "black", tl.srt = 45, addCoef.col = NULL,
         col = colorRampPalette(c("blue", "white", "red"))(200))

title(main = "Significant Correlations Study 2 (WITH Recoding Granularity Scores)", col.main = "black", font.main = 4)

# Close the PNG device
dev.off()
```
## USED TO GET PAIRWISE CORRELATION SAMPLE SIZES, DIDN'T USE FOR CORRELATION GRAPH
```{r}
# Select only numeric columns for correlation matrix
numeric_columns <- merged_df_study2[, sapply(merged_df_study2, is.numeric)]
numeric_columns_recoded <- merged_df_study2_recoded[, sapply(merged_df_study2_recoded, is.numeric)]

# Calculate the correlation matrix
correlation_matrix <- cor(numeric_columns, use = "pairwise.complete.obs")
correlation_matrix_recoded <- cor(numeric_columns_recoded, use = "pairwise.complete.obs")

# Function to compute significance levels and sample sizes
cor.mtest <- function(mat, conf.level = 0.95) {
  mat <- as.matrix(mat)
  n <- ncol(mat)
  p.mat <- matrix(NA, n, n)
  n.mat <- matrix(NA, n, n)  # Matrix to store sample sizes
  diag(p.mat) <- 0
  diag(n.mat) <- NA  # Diagonal sample size is irrelevant
  
  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      complete_cases <- complete.cases(mat[, i], mat[, j])  # Count non-NA pairs
      tmp <- cor.test(mat[complete_cases, i], mat[complete_cases, j], conf.level = conf.level)
      
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
      n.mat[i, j] <- n.mat[j, i] <- sum(complete_cases)  # Store sample size
    }
  }
  
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  colnames(n.mat) <- rownames(n.mat) <- colnames(mat)
  
  list(p_values = p.mat, sample_sizes = n.mat)
}

# Compute p-values and sample sizes
cor_results <- cor.mtest(numeric_columns)
p_values <- cor_results$p_values
sample_sizes <- cor_results$sample_sizes

cor_results_recoded <- cor.mtest(numeric_columns_recoded)
p_values_recoded <- cor_results_recoded$p_values
sample_sizes_recoded <- cor_results_recoded$sample_sizes

# Specify the folder where you want to save the file
output_folder <- "../results/qualtrics/study2/"

# Save first correlation plot (without recoding)
output_file <- file.path(output_folder, "Significant_Correlations_Plot_Study2_Without_Recoding.png")
png(output_file, width = 800, height = 800)

corrplot(correlation_matrix, method = "circle", type = "upper", 
         p.mat = p_values, sig.level = 0.05, insig = "blank",
         tl.col = "black", tl.srt = 45, addCoef.col = "black",
         col = colorRampPalette(c("blue", "white", "red"))(200),
         number.cex = 0.8)  # Adjust size of correlation coefficients

title(main = "Significant Correlations Study 2 (Without Recoding Granularity Scores)", col.main = "black", font.main = 4)

# Close the PNG device
dev.off()

# Save second correlation plot (with recoding)
output_file <- file.path(output_folder, "Significant_Correlations_Plot_Study2_With_Recoding.png")
png(output_file, width = 800, height = 800)

corrplot(correlation_matrix_recoded, method = "circle", type = "upper", 
         p.mat = p_values_recoded, sig.level = 0.05, insig = "blank",
         tl.col = "black", tl.srt = 45, addCoef.col = "black",
         col = colorRampPalette(c("blue", "white", "red"))(200),
         number.cex = 0.8)  # Adjust size of correlation coefficients

title(main = "Significant Correlations Study 2 (With Recoding Granularity Scores)", col.main = "black", font.main = 4)

# Close the PNG device
dev.off()

# Save sample size matrix as CSV for reference
write.csv(sample_sizes, file.path(output_folder, "Correlation_Sample_Sizes_Study2.csv"), row.names = TRUE)
write.csv(sample_sizes_recoded, file.path(output_folder, "Correlation_Sample_Sizes_Study2_Recoded.csv"), row.names = TRUE)


```

## aMEDT
```{r}
## CLEANED DATA BEFOREHAND, REMOVED DEVELOPMENTAL SAMPLE AND FIXED NAMING OF IDS TO MATCH GRANULARITY TASK
## also added the ones that were saved on Nick's laptop
## removed data from people that did not do the granularity task
aMEDT_inperson <- read.csv("../data/EDT/aMEDT In-Person Cleaned.csv") %>%
  select(c("session.p_id", "EDT.ability")) %>%
  rename(SURVEY_CODE = session.p_id)

## ADDING 3 WHO COMPLETED aMEDT AS FOLLOW-UP
aMEDT_followup <- read.csv("../data/EDT/aMEDT Follow-Up.csv") %>%
  select(c("session.p_id", "EDT.ability"))

aMEDT_followup <- aMEDT_followup %>%
  mutate(session.p_id = ifelse(grepl("^5", session.p_id), 
                               paste0("TEAM_YA_0", substr(session.p_id, 2, nchar(session.p_id))), 
                               session.p_id)) %>%
  rename(SURVEY_CODE = session.p_id)

aMEDT_all <- bind_rows(online_aMEDT, aMEDT_inperson, aMEDT_followup)

merged_study_2_with_aMEDT <- merge(aMEDT_all, merged_df_study2, by.x = "SURVEY_CODE", by.y = "SURVEY_CODE", all = FALSE)

merged_study_2_recoded_with_aMEDT <- merge(aMEDT_all, merged_df_study2_recoded, by.x = "SURVEY_CODE", by.y = "SURVEY_CODE", all = FALSE)

```

# Function to compute significance levels
```{r}
cor.mtest <- function(mat, conf.level = 0.95) {
  mat <- as.matrix(mat)
  n <- ncol(mat)
  p.mat <- matrix(NA, n, n)
  diag(p.mat) <- 0
  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      tmp <- cor.test(mat[, i], mat[, j], conf.level = conf.level)
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
    }
  }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
```

## EDT correlation with granularity scores
```{r}
# Function to create correlation scatter plots with linear model fit
create_scatter_plot <- function(data, x_var, y_var, x_label, y_label, title, output_file) {
  # Calculate correlation coefficient and p-value
  correlation <- cor.test(data[[x_var]], data[[y_var]], method = "pearson")
  corr_coeff <- round(correlation$estimate, 2)
  p_value <- sub("^0.", ".", round(correlation$p.value, 3))
  
  # Create scatter plot
  scatter_plot <- ggplot(data, aes(x = !!ensym(x_var), y = !!ensym(y_var))) +
    geom_point() +
    stat_smooth(method = 'lm', formula = y ~ x, color = "blue") +
    xlab(x_label) +
    ylab(y_label) +
    ggtitle(title) +
    theme_classic() +
    theme(axis.title.x = element_text(size = 14, face = 'bold'),
          axis.title.y = element_text(size = 14, face = 'bold'),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12),
          plot.title = element_text(size = 16, face = 'bold', hjust = 0.5)) +
    # Add correlation coefficient and p-value as annotation
    annotate("text", x = Inf, y = Inf, label = paste("r =", corr_coeff, "\np =", p_value), 
             hjust = 1.1, vjust = 1.5, size = 5, color = "red", fontface = "bold")
  
  # Save plot to file
  ggsave(output_file, scatter_plot, width = 11)
}

create_scatter_plot(merged_study_2_with_aMEDT, "EDT.ability", "negmusicICC", 
                    "aMEDT Score", 
                    "Negative Emotion Granularity (Music)", 
                    "Study 2 - Negative Emotion Granularity Scores (Music) and aMEDT Score", 
                    "../results/EDT/study2/Neg_Graph_2_26_25.png")

create_scatter_plot(merged_study_2_with_aMEDT, "EDT.ability", "posmusicICC", 
                    "aMEDT Score", 
                    "Positive Emotion Granularity (Music)", 
                    "Study 2 - Positive Emotion Granularity Scores (Music) and aMEDT Score", 
                    "../results/EDT/study2/Pos_Graph_2_26_25.png")

create_scatter_plot(merged_study_2_with_aMEDT, "EDT.ability", "allmusicICC", 
                    "aMEDT Score", 
                    "Combined Emotion Granularity (Music)", 
                    "Study 2 - Combined Emotion Granularity Scores (Music) and aMEDT Score", 
                    "../results/EDT/study2/Combined_Graph_2_26_25.png")

# Plotting correlation scatter plots - Recoded
create_scatter_plot(merged_study_2_recoded_with_aMEDT, "EDT.ability", "negmusicICC", 
                    "aMEDT Score", 
                    "Negative Emotion Granularity (Music)", 
                    "Study 2 - Negative Emotion Granularity Scores (Music) (Scores > 1 Recoded) and aMEDT Score", 
                    "../results/EDT/study2/Neg_Graph_Recoded_2_26_25.png")

create_scatter_plot(merged_study_2_recoded_with_aMEDT, "EDT.ability", "posmusicICC", 
                    "aMEDT Score", 
                    "Positive Emotion Granularity (Music)", 
                    "Study 2 - Positive Emotion Granularity Scores (Music) (Scores > 1 Recoded) and aMEDT Score", 
                    "../results/EDT/study2/Pos_Graph_Recoded_2_26_25.png")

create_scatter_plot(merged_study_2_recoded_with_aMEDT, "EDT.ability", "allmusicICC", 
                    "aMEDT Score", 
                    "Combined Emotion Granularity (Music)", 
                    "Study 2 - Combined Emotion Granularity Scores (Music) (Scores > 1 Recoded) and aMEDT Score", 
                    "../results/EDT/study2/Combined_Graph_Recoded_2_26_25.png")
```

```{r}
study2_dems <- surveys_study2 %>%
  select("participant_id","sex":"education")

study2_sex <- table(factor(study2_dems$sex, levels = c(1, 2), 
                              labels = c("Male", "Female")))

print(study2_sex)

# for Redcap Define gender column names
gender_columns <- c("gender___1", "gender___2", "gender___3", "gender___4", "gender___5", 
                    "gender___6", "gender___7", "gender___8", "gender___9", "gender___10")

# Summarize counts for each gender category (counting occurrences of 1)
study2_gender <- colSums(study2_dems[gender_columns] == 1, na.rm = TRUE)

# Assign descriptive names
names(study2_gender) <- c("Cisgender Man", "Cisgender Woman", "Transgender Man", 
                          "Transgender Woman", "Gender non-conforming", "Non-binary", 
                          "Genderfluid", "Genderqueer", "Other gender identity", "Prefer not to answer")

print(study2_gender)
```

## ethnicity/race
```{r}

# Define race/ethnicity column names
race_columns <- c("race_and_ethnicity___1", "race_and_ethnicity___2", "race_and_ethnicity___3", 
                  "race_and_ethnicity___4", "race_and_ethnicity___5", "race_and_ethnicity___6", 
                  "race_and_ethnicity___7")

num_selected <- rowSums(study2_dems[race_columns] == 1, na.rm = TRUE)
single_race <- num_selected == 1

# Summarize counts for each race/ethnicity category (counting occurrences of 1)
study2_races <- colSums(study2_dems[single_race, race_columns] == 1, na.rm = TRUE)

# Count number of respondents selecting more than one category
multi_race_count <- sum(rowSums(study2_dems[race_columns] == 1, na.rm = TRUE) > 1)
study2_races <- c(study2_races, "Two or more races" = multi_race_count)

# Assign descriptive names
names(study2_races) <- c("American Indian or Alaska Native", "Asian", "Black or African American", 
                        "Hispanic or Latino", "Native Hawaiian or Other Pacific Islander", 
                        "White", "Prefer not to answer", "Two or more races")

# Print results
print(study2_races)
```

## age
```{r}
# Calculate statistics
mean_age <- mean(as.numeric(study2_dems$age))
sd_age <- sd(as.numeric(study2_dems$age))
range_age <- range(as.numeric(study2_dems$age))

# Print results
cat("Mean Age:", mean_age, "\n")
cat("Standard Deviation:", sd_age, "\n")
cat("Age Range:", range_age[1], "to", range_age[2], "\n")


```

## combo time! BDI
```{r}
combined_BDI <- bind_rows(merged_df_recoded, merged_df_study2_recoded)

create_scatter_plot(combined_BDI, "BDI_total", "negpicICC", 
                    "Beck Depression Inventory II Score", 
                    "Negative Emotion Granularity (Picture)", 
                    "Correlation of BDI and Negative Granularity (Picture) - Combined Studies", 
                    "../results/rating-task/BDI and Negative Picture Combined Studies 2/27/25.png")

create_scatter_plot(combined_BDI, "BDI_total", "negmusicICC", 
                    "Beck Depression Inventory II Score", 
                    "Negative Emotion Granularity (Picture)", 
                    "Correlation of BDI and Negative Granularity (Music) - Combined Studies", 
                    "../results/rating-task/BDI and Negative Music Combined Studies 2/27/25.png")


```