---
title: "Gorilla_v11_Analysis"
output: html_document
date: "2024-08-13"
---

##--------Load packages---------
```{r setup, include=FALSE}
if (!(require("tidyverse"))) install.packages("tidyverse"); require("tidyverse")
if (!(require("psych"))) install.packages("psych"); require("psych")
if (!require("irr")) {install.packages("irr"); require("irr")} 
if (!require("reshape2")) {install.packages("reshape2"); require("reshape2")} 
if (!require("ggrepel")) {install.packages("ggrepel"); require("ggrepel")} 
if (!require("pwr")) {install.packages("pwr"); require("pwr")}
```

#---------Load in data--------
```{r}
v11 <- read.csv("../data/rating-task/data_exp_169297-v11_task-6dig.csv")

```

```{r}

granularity_data <- v11 %>%
  filter(Response.Type == "response") %>% 
  select("Participant.Public.ID","Response","Object.Name", "Spreadsheet..Image", "Spreadsheet..Audio") %>%
  mutate(Response = as.numeric(Response))

```

```{r}
granularity_data <- granularity_data %>%
  # MAX NEG PIC
  filter(Spreadsheet..Image != "Garbage dump 2.jpg") %>%
  
  # MIN NEG PIC
  filter(Spreadsheet..Image != "Cockroach 3.jpg") %>%
  
  # MAX POS PIC
  filter(Spreadsheet..Image != "Cat 5.jpg") %>%
  
  # MIN POS PIC
  filter(Spreadsheet..Image != "Cups 3.jpg") %>%
  
  # MIN NEG MUSIC
  filter(Spreadsheet..Audio != "11_pieceA_calm_anxious_sad_6.mp3") %>%
  
  # SECOND MIN NEG MUSIC
  filter(Spreadsheet..Audio != "5_pieceB_calm_sad_anxious_9.mp3") %>%
  
  # MIN POS MUSIC
  filter(Spreadsheet..Audio != "12_pieceA_joyous_sad_anxious_3.mp3") %>%
  
  # SECOND MIN POS MUSIC
  filter(Spreadsheet..Audio != "5_pieceB_calm_sad_anxious_7.mp3")
  
```

```{r}
# granularity_data <- granularity_data %>%
#   # MAX NEG PIC
#   filter(Spreadsheet..Image != "Garbage dump 2.jpg") %>%
#   
#   # SECOND MAX NEG PIC
#   filter(Spreadsheet..Image != "Destruction 2.jpg") %>%
#   
#   # MAX POS PIC
#   filter(Spreadsheet..Image != "Cat 5.jpg") %>%
#   
#   # SECOND MAX POS PIC
#   filter(Spreadsheet..Image != "Lake 12.jpg") %>%
#   
#   # MIN NEG MUSIC
#   filter(Spreadsheet..Audio != "11_pieceA_calm_anxious_sad_6.mp3") %>%
#   
#   # SECOND MIN NEG MUSIC
#   filter(Spreadsheet..Audio != "5_pieceB_calm_sad_anxious_9.mp3") %>%
#   
#   # MIN POS MUSIC
#   filter(Spreadsheet..Audio != "12_pieceA_joyous_sad_anxious_3.mp3") %>%
#   
#   # SECOND MIN POS MUSIC
#   filter(Spreadsheet..Audio != "5_pieceB_calm_sad_anxious_7.mp3")
#   
```

```{r}
# granularity_data <- granularity_data %>%
#   # MIN NEG PIC
#   filter(Spreadsheet..Image != "Cockroach 3.jpg") %>%
#   
#   # SECOND MIN NEG PIC
#   filter(Spreadsheet..Image != "Dirt 1.jpg") %>%
#   
#   # MIN POS PIC
#   filter(Spreadsheet..Image != "Cups 3.jpg") %>%
#   
#   # SECOND MIN POS PIC
#   filter(Spreadsheet..Image != "Heart 3.jpg") %>%
#   
#   # MIN NEG MUSIC
#   filter(Spreadsheet..Audio != "11_pieceA_calm_anxious_sad_6.mp3") %>%
#   
#   # SECOND MIN NEG MUSIC
#   filter(Spreadsheet..Audio != "5_pieceB_calm_sad_anxious_9.mp3") %>%
#   
#   # MIN POS MUSIC
#   filter(Spreadsheet..Audio != "12_pieceA_joyous_sad_anxious_3.mp3") %>%
#   
#   # SECOND MIN POS MUSIC
#   filter(Spreadsheet..Audio != "5_pieceB_calm_sad_anxious_7.mp3")
#   
```

```{r}
## Separating by picture vs music, removing practice stims
granularity_pic <- granularity_data %>%
  filter(Spreadsheet..Image != "") %>%
  filter(Spreadsheet..Image != "Coffee 1.jpg") %>%
  select(-c("Spreadsheet..Audio"))

granularity_music <- granularity_data %>%
  filter(Spreadsheet..Audio != "") %>%
  filter(Spreadsheet..Audio != "8_pieceA_dreamy_calm_joyous_1.mp3") %>%
  select(-c("Spreadsheet..Image"))
```

##-----Subsetting by valence and stimulus type--------
```{r}
# List of emotions
neg_emotions <- c("Angry", "Sad", "Scared", "Anxious", "Upset")
pos_emotions <- c("Happy", "Satisfied", "Excited", "Joyful", "Relaxed")

# Function to filter and rename
filter_and_rename <- function(data, emotion, media_type, keep_id = FALSE) {
  columns_to_select <- if (keep_id) {
    c("Participant.Public.ID", "Response")
  } else {
    c("Response")
  }
  
  data %>%
    filter(Object.Name == paste(emotion, "Slider")) %>%
    select(-c(paste0("Spreadsheet..", media_type), "Object.Name")) %>%
    select(all_of(columns_to_select)) %>%
    rename(!!tolower(emotion) := "Response")
}

# Apply function to each emotion for music and images
filtered_music_neg <- lapply(seq_along(neg_emotions), function(i) {
  filter_and_rename(granularity_music, neg_emotions[i], "Audio", keep_id = (i == 1))
})

filtered_music_pos <- lapply(seq_along(pos_emotions), function(i) {
  filter_and_rename(granularity_music, pos_emotions[i], "Audio", keep_id = (i == 1))
})

filtered_pic_neg <- lapply(seq_along(neg_emotions), function(i) {
  filter_and_rename(granularity_pic, neg_emotions[i], "Image", keep_id = (i == 1))
})

filtered_pic_pos <- lapply(seq_along(pos_emotions), function(i) {
  filter_and_rename(granularity_pic, pos_emotions[i], "Image", keep_id = (i == 1))
})

music_negative <- bind_cols(filtered_music_neg) %>%
  na.omit()

music_positive <- bind_cols(filtered_music_pos)

pic_negative <- bind_cols(filtered_pic_neg)

pic_positive <- bind_cols(filtered_pic_pos)
```

##--Plotting means of emotion word ratings--
```{r}
# music neg
music_negative_summary <- music_negative %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

music_negative_means <- ggplot(music_negative_summary, aes(x = variable, y = mean_value)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), width = 0.2) +
  labs(title = "Music Negative Emotion Means", x = "Emotion", y = "Mean Response") +
  theme_bw()

ggsave('../results/presentation/Music_Negative_Means_8_13_24.png', music_negative_means, width = 9)

# music pos
music_positive_summary <- music_positive %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

music_positive_means <- ggplot(music_positive_summary, aes(x = variable, y = mean_value)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), width = 0.2) +
  labs(title = "Music Positive Emotion Means", x = "Emotion", y = "Mean Response") +
  theme_bw()

ggsave('../results/presentation/Music_Positive_Means_8_13_24.png', music_positive_means, width = 9)

# pic pos
pic_positive_summary <- pic_positive %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

pic_positive_means <- ggplot(pic_positive_summary, aes(x = variable, y = mean_value)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), width = 0.2) +
  labs(title = "Picture Positive Emotion Means", x = "Emotion", y = "Mean Response") +
  theme_bw()

ggsave('../results/presentation/Picture_Positive_Means_8_13_24.png', pic_positive_means, width = 9)

# pic neg
pic_negative_summary <- pic_negative %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

pic_negative_means <- ggplot(pic_negative_summary, aes(x = variable, y = mean_value)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), width = 0.2) +
  labs(title = "Picture Negative Emotion Means", x = "Emotion", y = "Mean Response") +
  theme_bw()

ggsave('../results/presentation/Picture_Negative_Means_8_13_24.png', pic_negative_means, width = 9)
```

##--Graphs printed together to have scale reference--
```{r}
music_negative_summary$type <- "Music"
music_positive_summary$type <- "Music"
pic_negative_summary$type <- "Picture"
pic_positive_summary$type <- "Picture"
neg_summary <- bind_rows(music_negative_summary, pic_negative_summary)
pos_summary <- bind_rows(music_positive_summary, pic_positive_summary)

# Plot for negative emotions
neg_plot <- ggplot(neg_summary, aes(x = variable, y = mean_value, color = type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                width = 0.2) +
  labs(title = "Negative Emotion Means", x = "Emotion", y = "Mean Response") +
  theme_bw()

# Plot for positive emotions
pos_plot <- ggplot(pos_summary, aes(x = variable, y = mean_value, color = type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                width = 0.2) +
  labs(title = "Positive Emotion Means", x = "Emotion", y = "Mean Response") +
  theme_bw()

# Save the plots
ggsave('../results/presentation/Negative_Emotion_Means_8_13_24.png', neg_plot, width = 9)
ggsave('../results/presentation/Positive_Emotion_Means_8_13_24.png', pos_plot, width = 9)


```

##-Percent of nonzero responses--
```{r}
library(knitr)
library(readr)
library(gridExtra)
library(grid)
library(png)

# Function to calculate the percentage of non-zero responses for each column
calculate_non_zero_percentage <- function(df) {
  df %>%
    select(-Participant.Public.ID) %>%
    summarise(across(everything(), ~ round(sum(!is.na(.) & . != 0) / sum(!is.na(.)) * 100)))
}

# Calculate percentages and create tables
tables <- list(
  list(data = music_negative, caption = "% of Non-Zero Responses for Negative Emotion Words (Music)"),
  list(data = pic_negative, caption = "% of Non-Zero Responses for Negative Emotion Words (Pictures)"),
    list(data = music_positive, caption = "% of Non-Zero Responses for Positive Emotion Words (Music)"),
  list(data = pic_positive, caption = "% of Non-Zero Responses for Positive Emotion Words (Pictures)")
)

# Create grobs for each table and caption
table_grobs <- lapply(tables, function(tbl) {
  percentages <- calculate_non_zero_percentage(tbl$data)
  table_grob <- tableGrob(percentages, theme = ttheme_minimal())
  caption_grob <- textGrob(tbl$caption, gp = gpar(fontsize = 10))
  arrangeGrob(caption_grob, table_grob, ncol = 1)
})

# Arrange all tables vertically
arranged_tables <- do.call(arrangeGrob, c(table_grobs, ncol = 1))

# Save the arranged tables as a PNG file
png("../results/presentation/emotion_response_percentages_8_13_24.png", width = 400, height = 400)
grid.draw(arranged_tables)
dev.off()
```

##--Separating pics and music by valence (pos/neg)--
```{r}
pos_pic <- c("Beach 1.jpg", "Cat 5.jpg", "Fireworks 6.jpg", "Lake 12.jpg", "Rainbow 2.jpg", "Clean 1.jpg", "Cups 3.jpg", "Heart 3.jpg", "Rocks 1.jpg", "Snow 1.jpg")
pos_pic_data <- granularity_pic %>%
  filter(Spreadsheet..Image %in% pos_pic)

neg_pic <- c("Cockroach 3.jpg", "Dirt 1.jpg", "Ferret 1.jpg", "Fire 10.jpg", "Flood 1.jpg", "Garbage dump 2.jpg", "Destruction 2.jpg", "Garbage dump 1.jpg", "Prison 2.jpg", "Toilet 4.jpg")
neg_pic_data <- granularity_pic %>%
  filter(Spreadsheet..Image %in% neg_pic)

pos_music <- c("3_pieceB_joyous_anxious_sad_5.mp3", "6_pieceB_anxious_calm_joyous_8.mp3", "7_pieceB_joyous_anxious_sad_5.mp3", "7_pieceB_joyous_anxious_sad_6.mp3", "5_pieceB_calm_sad_anxious_7.mp3", "6_pieceB_anxious_calm_joyous_5.mp3", "6_pieceB_anxious_calm_joyous_7.mp3", "12_pieceA_joyous_sad_anxious_2.mp3", "12_pieceA_joyous_sad_anxious_3.mp3", "12_pieceA_joyous_sad_anxious_9.mp3")
pos_music_data <- granularity_music %>%
  filter(Spreadsheet..Audio %in% pos_music)

neg_music <- c("3_pieceB_joyous_anxious_sad_1.mp3", "11_pieceA_calm_anxious_sad_4.mp3", "11_pieceA_calm_anxious_sad_5.mp3", "11_pieceA_calm_anxious_sad_6.mp3", "11_pieceA_calm_anxious_sad_8.mp3", "5_pieceB_calm_sad_anxious_1.mp3", "5_pieceB_calm_sad_anxious_2.mp3", "5_pieceB_calm_sad_anxious_3.mp3", "5_pieceB_calm_sad_anxious_9.mp3", "11_pieceA_calm_anxious_sad_2.mp3")
neg_music_data <- granularity_music %>%
  filter(Spreadsheet..Audio %in% neg_music)
```

##-All graphed together - 8/12/24
```{r}
# 10 clips
averages_pos_music <- pos_music_data %>%
  group_by(Object.Name) %>%
  summarise(
    Average.Response = mean(Response, na.rm = TRUE),
    se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    )

# 10 clips
averages_neg_music <- neg_music_data %>%
  group_by(Object.Name) %>%
  summarise(
    Average.Response = mean(Response, na.rm = TRUE),
    se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    )

# 10 pics
averages_pos_pic <- pos_pic_data %>%
  group_by(Object.Name) %>%
  summarise(
    Average.Response = mean(Response, na.rm = TRUE),
    se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    )

# 10 pics
averages_neg_pic <- neg_pic_data %>%
  group_by(Object.Name) %>%
  summarise(
    Average.Response = mean(Response, na.rm = TRUE),
    se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    )

all_averages <- bind_rows(
  averages_pos_music %>% mutate(Type = "Positive Valence Music"),
  averages_neg_music %>% mutate(Type = "Negative Valence Music"),
  averages_pos_pic %>% mutate(Type = "Positive Valence Pictures"),
  averages_neg_pic %>% mutate(Type = "Negative Valence Pictures"),
)

all_averages$Object.Name <- gsub("Slider", "", all_averages$Object.Name)

# Trim any extra whitespace that might be left after removing "Slider"
all_averages$Object.Name <- trimws(all_averages$Object.Name)

emotion_order <- c("Angry", "Anxious", "Sad", "Scared", "Upset", "Excited", "Happy", "Joyful", "Relaxed", "Satisfied")
all_averages$Object.Name <- factor(all_averages$Object.Name, levels = emotion_order)

full_plot <- ggplot(all_averages, aes(x = Object.Name, y = Average.Response, color = Type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = Average.Response - se_value, ymax = Average.Response + se_value), 
                width = 0.2) +
  labs(title = "All Emotions - Mean Response by Stimulus Valence/Type", x = "Emotion", y = "Mean Response") +
  theme_bw() +
  ylim(0, 51)

# Save the plots
ggsave('../results/presentation/All_Emotion_Means_8_13_24.png', full_plot, width = 9)

```

```{r}
all_averages$Category <- ifelse(all_averages$Object.Name %in% c("Angry", "Anxious", "Sad", "Scared", "Upset"),
                      "Negative Emotions",
                      "Positive Emotions")

# REMOVE ANGRY TO CHECK
all_averages <- all_averages %>%
  filter(Object.Name != "Angry")

summary_df <- all_averages %>%
  group_by(Type, Category) %>%
  summarise(
    Average.Response = mean(Average.Response),
    Combined.SE = sqrt(sum(se_value^2) / n())
  )

summary_plot <- ggplot(summary_df, aes(x = Category, y = Average.Response, color = Type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = Average.Response - Combined.SE, ymax = Average.Response + Combined.SE), 
                width = 0.2) +
  labs(title = "Emotion Categories - Mean Response by Stimulus Valence/Type (with Anger Removed)", x = "Emotion", y = "Mean") +
  theme_bw() +
  ylim(0, 51)

# Save the plots
ggsave('../results/rating-task/Emotion_Category_Means_No_Anger_8_27_24.png', summary_plot, width = 9)

```

```{r}
# 10 clips
averages_pos_music <- pos_music_data %>%
  group_by(Spreadsheet..Audio) %>%
  summarise(
    Average.Response = mean(Response, na.rm = TRUE),
    se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    )

# 10 clips
averages_neg_music <- neg_music_data %>%
  group_by(Spreadsheet..Audio) %>%
  summarise(
    Average.Response = mean(Response, na.rm = TRUE),
    se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    )

# 10 pics
averages_pos_pic <- pos_pic_data %>%
  group_by(Spreadsheet..Image) %>%
  summarise(
    Average.Response = mean(Response, na.rm = TRUE),
    se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    )

# 10 pics
averages_neg_pic <- neg_pic_data %>%
  group_by(Spreadsheet..Image) %>%
  summarise(
    Average.Response = mean(Response, na.rm = TRUE),
    se_value = sd(Response, na.rm = TRUE) / sqrt(n())
    )

all_averages <- bind_rows(
  averages_pos_music %>% mutate(Type = "pos_music"),
  averages_neg_music %>% mutate(Type = "neg_music"),
  averages_pos_pic %>% mutate(Type = "pos_pic"),
  averages_neg_pic %>% mutate(Type = "neg_pic"),
)

# min_values_pos_music <- all_averages %>%
#   filter(Type == "pos_music") %>%
#   slice_min(Average.Response, n = 2)
# 
# min_values_neg_music <- all_averages %>%
#   filter(Type == "neg_music") %>%
#   slice_min(Average.Response, n = 2)
# 
# min_values_neg_pic <- all_averages %>%
#   filter(Type == "neg_pic") %>%
#   slice_min(Average.Response, n = 2)
# 
# min_values_pos_pic <- all_averages %>%
#   filter(Type == "pos_pic") %>%
#   slice_min(Average.Response, n = 2)
# 
# max_values_pos_pic <- all_averages %>%
#   filter(Type == "pos_pic") %>%
#   slice_max(Average.Response, n = 2)
# 
# max_values_neg_pic <- all_averages %>%
#   filter(Type == "neg_pic") %>%
#   slice_max(Average.Response, n = 2)

# ## REMOVING SOME STIMULI
# 
# all_averages <- anti_join(all_averages, max_values_pos_pic, by = c("Spreadsheet..Audio", "Average.Response", "se_value", "Type", "Spreadsheet..Image"))
# all_averages <- anti_join(all_averages, min_values_pos_pic, by = c("Spreadsheet..Audio", "Average.Response", "se_value", "Type", "Spreadsheet..Image"))
# all_averages <- anti_join(all_averages, max_values_neg_pic, by = c("Spreadsheet..Audio", "Average.Response", "se_value", "Type", "Spreadsheet..Image"))
# all_averages <- anti_join(all_averages, min_values_neg_pic, by = c("Spreadsheet..Audio", "Average.Response", "se_value", "Type", "Spreadsheet..Image"))
# 
# all_averages <- anti_join(all_averages, min_values_neg_music, by = c("Spreadsheet..Audio", "Average.Response", "se_value", "Type", "Spreadsheet..Image"))
# all_averages <- anti_join(all_averages, min_values_pos_music, by = c("Spreadsheet..Audio", "Average.Response", "se_value", "Type", "Spreadsheet..Image"))

library(ggrepel)

all_averages$Type[all_averages$Type == "neg_music" | all_averages$Type == "pos_music"] = "Music"
all_averages$Type[all_averages$Type == "neg_pic" | all_averages$Type == "pos_pic"] = "Picture"

all_stims_plotted <- ggplot(all_averages, aes(x = Type, y = Average.Response)) +
  geom_point() +
  geom_errorbar(aes(ymin = Average.Response - se_value, ymax = Average.Response + se_value), alpha = 0.4, width = 0.2) +
  labs(title = "All Stimuli - Average Responses", x = "Stimulus Type", y = "Mean Response") +
  theme_bw()

ggsave('../results/presentation/All_Stims_Means_8_13_24.png', all_stims_plotted, width = 14)

collapsed_stims <- all_averages %>%
  group_by(Type) %>%
  summarise(
    Mean_Value = mean(Average.Response),
    Combined_SE = sqrt(sum(se_value^2) / n())  # Combining standard errors
  )

```

##t-test for comparing differences of means with existing summmary stats
## to compare removing cockroach vs destruction
```{r}
# Summary statistics
mean1 <- collapsed_stims[1,2]  # Mean of group 1
mean2 <- collapsed_stims[2,2]  # Mean of group 2
se1 <- collapsed_stims[1,3]    # Standard error of group 1
se2 <- collapsed_stims[2,3]   # Standard error of group 2
n1 <- 16      # Sample size of group 1
n2 <- 16      # Sample size of group 2

# Calculate the t-statistic
t_stat <- (mean1 - mean2) / sqrt(se1^2 + se2^2)

# Calculate the degrees of freedom using Welch's approximation
df <- ((se1^2 + se2^2)^2) / (((se1^2)^2 / (n1 - 1)) + ((se2^2)^2 / (n2 - 1)))

# Calculate the p-value (two-tailed test)
p_value <- 2 * pt(-abs(t_stat[1,1]), df[1,1])

# Output the t-statistic, degrees of freedom, and p-value
cat("t-statistic:", t_stat[1,1], "\n")
cat("Degrees of freedom:", df[1,1], "\n")
cat("p-value:", p_value, "\n")


```

```{r}

# for 8-27-24
all_averages$Type[all_averages$Type == "Negative Valence Music" | all_averages$Type == "Positive Valence Music"] = "Music"
all_averages$Type[all_averages$Type == "Negative Valence Pictures" | all_averages$Type == "Positive Valence Pictures"] = "Picture"

collapsed_stims <- all_averages %>%
  group_by(Type) %>%
  summarise(
    Mean_Value = mean(Average.Response),
    Combined_SE = sqrt(sum(se_value^2) / n())  # Combining standard errors
  )

collapsed_plot <- ggplot(collapsed_stims, aes(x = Type, y = Mean_Value, color = Mean_Value, label = Mean_Value)) +
  geom_point() +
  geom_text(hjust=0, vjust=0) +
  geom_errorbar(aes(ymin = Mean_Value - Combined_SE, ymax = Mean_Value + Combined_SE, color = Mean_Value), alpha = 0.4, width = 0.2) +
  labs(title = "Stimulus Response Averages (with Anger Removed)", x = "Stimulus Type", y = "Mean Response") +
  theme_bw()

ggsave('../results/rating-task/Average_Stims_Means_8_27_24_Error_Bars.png', collapsed_plot, width = 10)

```

##----Scoring ICC------
```{r}
# Function to compute ICC and store results
compute_icc <- function(data_list, result_column) {
  sapply(seq_along(data_list), function(i) {
    icc_result <- data_list[[i]] %>%
      select(-Participant.Public.ID) %>%
      icc(model = "twoway", type = "consistency", unit = "average")
    1 - icc_result$value
  })
}

# Create a list of data frames split by Participant.Public.ID
music_negative_list <- split(music_negative, music_negative$Participant.Public.ID)
music_positive_list <- split(music_positive, music_positive$Participant.Public.ID)
pic_negative_list <- split(pic_negative, pic_negative$Participant.Public.ID)
pic_positive_list <- split(pic_positive, pic_positive$Participant.Public.ID)

# To test without "angry" data
# music_negative <- music_negative %>%
#   select(-c("angry"))

# Initialize results DataFrame
results <- expand.grid(ID = names(music_negative_list))

# Compute ICC values for each subset and add to results
results$negmusicICC <- compute_icc(music_negative_list, "negmusicICC")
results$posmusicICC <- compute_icc(music_positive_list, "posmusicICC")
results$negpicICC <- compute_icc(pic_negative_list, "negpicICC")
results$pospicICC <- compute_icc(pic_positive_list, "pospicICC")

## 8-28-24 ADDING COMBINED SCORES
results$allmusicICC <- rowMeans(results[, c("negmusicICC", "posmusicICC")])
results$allpicICC <- rowMeans(results[, c("negpicICC", "pospicICC")])

# Display the result
results
```

#scoring granularity responses # FISHER Z TRANSFORM VERSION
```{r}
# WITHOUT RECODING
compute_icc <- function(data_list, result_column) {
  sapply(seq_along(data_list), function(i) {
    icc_result <- data_list[[i]] %>%
      select(-Participant.Public.ID) %>%
      icc(model = "twoway", type = "consistency", unit = "average")
    
    1 - fisherz(icc_result$value)
  })
}

<<<<<<< Updated upstream
# FOR RECODED VERSION
compute_icc <- function(data_list, result_column) {
  sapply(seq_along(data_list), function(i) {
    icc_result <- data_list[[i]] %>%
      select(-Participant.Public.ID) %>%
      icc(model = "twoway", type = "consistency", unit = "average")
    
    # recode correlations less than 0 as 0
    icc_value <- ifelse(icc_result$value < 0, 0, icc_result$value)
    
    # Fisher transformation and reverse scoring
    1 - fisherz(icc_value)
  })
}
=======

results$negmusicICC <- ifelse(results$negmusicICC>1, 1, results$negmusicICC)
results$posmusicICC <- ifelse(results$posmusicICC>1, 1, results$posmusicICC)
results$negpicICC <- ifelse(results$negpicICC>1, 1, results$negpicICC)
results$pospicICC <- ifelse(results$pospicICC>1, 1, results$pospicICC)
>>>>>>> Stashed changes
```

# after removing outliers
```{r}
results <- results %>%
  filter(negpicICC < 1) %>%
  filter(negmusicICC < 1) %>%
  filter(pospicICC < 1) %>%
  filter(posmusicICC < 1) %>%
  filter(allpicICC < 1) %>%
  filter(allmusicICC < 1)
```

##Plotting granularity scores for overall spread and correlations and 
##UPDATED 8-27-24 WITH FISHER R TO Z TRANSFORMS
```{r}
# Reshape data for both histograms
df_long1 <- results %>% gather(key = "Variable", value = "Value", negmusicICC, negpicICC)
df_long2 <- results %>% gather(key = "Variable", value = "Value", posmusicICC, pospicICC)

# Create and print histograms
negICChist <- ggplot(df_long1, aes(x = Value, fill = Variable)) +
  geom_histogram(position = "identity", alpha = 0.5) +
  labs(title = "Negative Emotions - Granularity Scores (Fisher r to z) (Scores > 1 Recoded)", x = "Granularity Score", y = "Count")
ggsave('../results/rating-task/Negative ICCs 8_27_24v2.png', negICChist, width = 14)

posICChist <- ggplot(df_long2, aes(x = Value, fill = Variable)) +
  geom_histogram(position = "identity", alpha = 0.5) +
  labs(title = "Positive Emotions - Granularity Scores (Fisher r to z) (Scores > 1 Recoded)", x = "Granularity Score", y = "Count")
ggsave('../results/rating-task/Positive ICCs 8_27_24v2.png', posICChist, width = 14)

pos_graph <- ggplot(data = results, aes(x = pospicICC, y = posmusicICC)) +
  geom_point() +
  stat_smooth(method = 'lm') +
  xlab('Positive Emotion Granularity (Pictures)') +
  ylab('Positive Emotion Granularity (Music)') +
  ggtitle('Correlation of Positive Emotion Granularity Scores (Fisher r to z) (Scores > 1 Recoded)') +
  theme_classic() +
  theme(axis.title.x = element_text(size=14, face='bold'), axis.title.y = element_text(size=14, face='bold'), axis.text.x = element_text(size=12), axis.text.y = element_text(size=12), plot.title = element_text(size=16, face='bold', hjust = 0.5))

ggsave('../results/rating-task/Pos_Graph 8_27_24v2.png', pos_graph, width = 10)

neg_graph <- ggplot(data = results, aes(x = negpicICC, y = negmusicICC)) +
  geom_point() +
  stat_smooth(method = 'lm') +
  xlab('Negative Emotion Granularity (Pictures)') +
  ylab('Negative Emotion Granularity (Music)') +
  ggtitle('Correlation of Negative Emotion Granularity Scores (Fisher r to z) (Scores > 1 Recoded)') +
  theme_classic() +
  theme(axis.title.x = element_text(size=14, face='bold'), axis.title.y = element_text(size=14, face='bold'), axis.text.x = element_text(size=12), axis.text.y = element_text(size=12), plot.title = element_text(size=16, face='bold', hjust = 0.5))

ggsave('../results/rating-task/Neg_Graph 8_27_24v2.png', neg_graph, width = 10)

```
## GRAPHING COMBINED SCORES
```{r}
df_long3 <- results %>% gather(key = "Variable", value = "Value", allmusicICC, allpicICC)

allICChist <- ggplot(df_long3, aes(x = Value, fill = Variable)) +
  geom_histogram(position = "identity", alpha = 0.5) +
  labs(title = "All Emotions - Granularity Scores (Fisher r to z) (Scores > 1 Recoded)", x = "Granularity Score", y = "Count")
ggsave('../results/rating-task/Combined ICCs (Fisher r to z) (Scores > 1 Recoded) 8_28_24.png', allICChist, width = 14)

all_graph <- ggplot(data = results, aes(x = allpicICC, y = allmusicICC)) +
  geom_point() +
  stat_smooth(method = 'lm') +
  xlab('Positive Emotion Granularity (Pictures)') +
  ylab('Positive Emotion Granularity (Music)') +
  ggtitle('Correlation of Combined Emotion Granularity Scores (Fisher r to z) (Scores > 1 Recoded)') +
  theme_classic() +
  theme(axis.title.x = element_text(size=14, face='bold'), axis.title.y = element_text(size=14, face='bold'), axis.text.x = element_text(size=12), axis.text.y = element_text(size=12), plot.title = element_text(size=16, face='bold', hjust = 0.5))
ggsave('../results/rating-task/Combined Graph (Fisher r to z) (Scores > 1 Recoded) 8_28_24.png', all_graph, width = 10)

```


```{r}
cor.test(results$posmusicICC, results$pospicICC)
cor.test(results$negmusicICC, results$negpicICC)
t.test(results$posmusicICC, results$pospicICC, paired = TRUE)
t.test(results$negmusicICC, results$negpicICC, paired = TRUE)

mean_comparison <- results %>%
  pivot_longer(negmusicICC:pospicICC) %>%
  ggplot(aes(x=name, y=value)) +
  stat_summary(fun.data='mean_cl_normal', geom = 'errorbar', width = 0.2) +
  stat_summary(fun.data='mean_cl_normal', geom = 'pointrange', width = 0.2) +
  theme_bw() +
  xlab('Stimulus and Valence') +
  ylab('Average Emotion Granularity') +
  ggtitle('Average Granularity Scores by Stimulus Type/Valence (Fisher r to z)') +
  theme(axis.title.x = element_text(size=14, face='bold'), axis.title.y = element_text(size=14, face='bold'), axis.text.x = element_text(size=12), axis.text.y = element_text(size=12)) +
  scale_x_discrete(labels = c('Negative Music', 'Negative Picture', 'Positive Music', 'Positive Picture'))

ggsave('../results/rating-task/Mean_Comparisons_8_27_24v1.png', mean_comparison, width = 9)

cor.test(results$allmusicICC, results$allpicICC)

```

##Power analysis - NEW FOR 8/15/24
```{r}
effect_size <- function(x, y) {
  mean_diff <- mean(x - y, na.rm = TRUE)
  sd_diff <- sd(x - y, na.rm = TRUE)
  return(mean_diff / sd_diff)
}

round_up <- function(x, digits) {
  factor <- 10^digits
  return(ceiling(x * factor) / factor)
}

## Power analysis for difference of means of positive granularity scores
# Set desired significance level (alpha) and power
# I just set like super stringent criteria for now since the differences are so significant
alpha <- 0.05
power <- 0.80

# Calculate the effect size
d_pos <- effect_size(results$posmusicICC, results$pospicICC)
mean(results$posmusicICC - results$pospicICC)
sd(results$posmusicICC - results$pospicICC)

# Calculate the necessary sample size
sample_size_pos <- pwr.t.test(d = d_pos, power = power, sig.level = alpha, type = "paired")$n

paste("Effect size for difference in means of positive granularity scores is", round(d_pos, 2), "--> N =", round_up(sample_size_pos, 0), "for 80% power.")

## Repeat for negative granularity scores

d_neg <- effect_size(results$negmusicICC, results$negpicICC)
mean(results$negmusicICC - results$negpicICC)
sd(results$negmusicICC - results$negpicICC)

sample_size_neg <- pwr.t.test(d = d_neg, power = power, sig.level = alpha, type = "paired")$n

paste("Effect size for difference in means of negative granularity scores is", round(d_neg, 2), "--> N =", round_up(sample_size_neg, 0), "for 80% power.")

d_all <- effect_size(results$allmusicICC, results$allpicICC)
mean(results$allmusicICC - results$allpicICC)
sd(results$allmusicICC - results$allpicICC)

sample_size_all <- pwr.t.test(d = d_all, power = power, sig.level = alpha, type = "paired")$n

paste("Effect size for difference in means of combined granularity scores is", round(d_neg, 2), "--> N =", round_up(sample_size_all, 0), "for 80% power.")

```

## Maybe try powering with negative emotion granularity score correlation? - 8/15/24
```{r}
cor_test_neg <- cor.test(results$negmusicICC, results$negpicICC, method = "pearson")

# Extract the correlation coefficient (r)
r <- cor_test_neg$estimate

alpha <- 0.05
power <- 0.8

# Perform power analysis
power_analysis_neg <- pwr.r.test(r = r, sig.level = alpha, power = power)

# Print the power analysis result
print(power_analysis_neg)

cor_test_pos <- cor.test(results$posmusicICC, results$pospicICC, method = "pearson")

# Extract the correlation coefficient (r)
r <- cor_test_pos$estimate

# Perform power analysis
power_analysis_pos <- pwr.r.test(r = r, sig.level = alpha, power = power)

# Print the power analysis result
print(power_analysis_pos)

cor_test_all <- cor.test(results$allmusicICC, results$allpicICC, method = "pearson")

# Extract the correlation coefficient (r)
r <- cor_test_all$estimate

# Perform power analysis
power_analysis_all <- pwr.r.test(r = r, sig.level = alpha, power = power)

# Print the power analysis result
print(power_analysis_all)
```