---
title: "Practice_Gorilla_v2"
output: html_document
date: "2024-07-17"
---

##--------Load packages---------
```{r setup, include=FALSE}
if (!(require("tidyverse"))) install.packages("tidyverse"); require("tidyverse")
if (!(require("psych"))) install.packages("psych"); require("psych")
if (!require("irr")) {install.packages("irr"); require("irr")} 
if (!require("reshape2")) {install.packages("reshape2"); require("reshape2")} 
```

#---------Load in data--------
```{r}
#v8 data
v8 <- read.csv("../data/rating-task/data_exp_169297-v8_task-6dig.csv")
v8 <- v8 %>%
  mutate(Spreadsheet..relaxed_rating = NA) %>%
  mutate(Spreadsheet..upset_rating = NA)

#v9 data
v9 <- read.csv("../data/rating-task/data_exp_169297-v9_task-6dig.csv")
v9 <- v9 %>%
  mutate(Spreadsheet..relaxed_rating = NA) %>%
  mutate(Spreadsheet..upset_rating = NA)

#v10 data
v10 <- read.csv("../data/rating-task/data_exp_169297-v10_task-6dig.csv")
v10 <- v10 %>%
  mutate(Spreadsheet..upset_rating = NA)

v11 <- read.csv("../data/rating-task/data_exp_169297-v11_task-6dig.csv")
v11 <- v11 %>%
  mutate(Spreadsheet..disgusted_rating = NA) %>%
  mutate(Spreadsheet..proud_rating = NA)

#combined data
combined_data <- rbind(v8, v9, v10, v11)

```

```{r}

## Filtering out developmental data
granularity_data <- combined_data %>%
  filter(Response.Type == "response") %>% 
  filter(Participant.Public.ID != "TEAM_DEV_301") %>%
  select("Participant.Public.ID","Response","Object.Name", "Spreadsheet..Image", "Spreadsheet..Audio") %>%
  mutate(Response = as.numeric(Response))

## Separating by picture vs music, removing practice stims
granularity_pic <- granularity_data %>%
  filter(Spreadsheet..Image != "") %>%
  filter(Spreadsheet..Image != "Coffee 1.jpg") %>%
  select(-c("Spreadsheet..Audio"))

granularity_music <- granularity_data %>%
  filter(Spreadsheet..Audio != "") %>%
  filter(Spreadsheet..Audio != "8_pieceA_dreamy_calm_joyous_1.mp3") %>%
  select(-c("Spreadsheet..Image"))
```

##-----Subsetting by valence and stimulus type--------
```{r}
# List of emotions
neg_emotions <- c("Angry", "Disgusted", "Sad", "Scared", "Anxious", "Upset")
pos_emotions <- c("Happy", "Satisfied", "Excited", "Joyful", "Proud", "Relaxed")

# Function to filter and rename
filter_and_rename <- function(data, emotion, media_type, keep_id = FALSE) {
  columns_to_select <- if (keep_id) {
    c("Participant.Public.ID", "Response")
  } else {
    c("Response")
  }
  
  data %>%
    filter(Object.Name == paste(emotion, "Slider")) %>%
    select(-c(paste0("Spreadsheet..", media_type), "Object.Name")) %>%
    select(all_of(columns_to_select)) %>%
    rename(!!tolower(emotion) := "Response")
}

# Apply function to each emotion for music and images
filtered_music_neg <- lapply(seq_along(neg_emotions), function(i) {
  filter_and_rename(granularity_music, neg_emotions[i], "Audio", keep_id = (i == 1))
})

filtered_music_pos <- lapply(seq_along(pos_emotions), function(i) {
  filter_and_rename(granularity_music, pos_emotions[i], "Audio", keep_id = (i == 1))
})

filtered_pic_neg <- lapply(seq_along(neg_emotions), function(i) {
  filter_and_rename(granularity_pic, neg_emotions[i], "Image", keep_id = (i == 1))
})

filtered_pic_pos <- lapply(seq_along(pos_emotions), function(i) {
  filter_and_rename(granularity_pic, pos_emotions[i], "Image", keep_id = (i == 1))
})

# Need to append extra rows for missing "relaxed" ratings 
extend_df <- function(df, num_rows) {
  additional_rows <- data.frame(matrix(NA, nrow = num_rows, ncol = ncol(df)))
  colnames(additional_rows) <- colnames(df)
  extended_df <- bind_rows(df, additional_rows)
  return(extended_df)
}

# # Need to prepend rows for missing "satisfied" ratings
# prepend_rows <- function(df, num_rows) {
#   additional_rows <- data.frame(matrix(NA, nrow = num_rows, ncol = ncol(df)))
#   colnames(additional_rows) <- colnames(df)
#   extended_df <- bind_rows(additional_rows, df)
#   return(extended_df)
# }

# Append 60 rows to the 2nd (satisfied) dataframe, 60 rows to the 6th (relaxed), 140 rows to the 5th (proud) - positive
filtered_music_pos[[2]] <- extend_df(filtered_music_pos[[2]], 60)
filtered_music_pos[[6]] <- extend_df(filtered_music_pos[[6]], 60)
filtered_music_pos[[5]] <- extend_df(filtered_music_pos[[5]], 140)

filtered_pic_pos[[2]] <- extend_df(filtered_pic_pos[[2]], 60)
filtered_pic_pos[[6]] <- extend_df(filtered_pic_pos[[6]], 60)
filtered_pic_pos[[5]] <- extend_df(filtered_pic_pos[[5]], 140)

# Append 140 rows to the 2nd (disgusted) dataframe, 120 to the 6th (upset) - negative
filtered_music_neg[[2]] <- extend_df(filtered_music_neg[[2]], 140)
filtered_music_neg[[6]] <- extend_df(filtered_music_neg[[6]], 120)

filtered_pic_neg[[2]] <- extend_df(filtered_pic_neg[[2]], 140)
filtered_pic_neg[[6]] <- extend_df(filtered_pic_neg[[6]], 120)


# Combine the results
music_negative <- bind_cols(filtered_music_neg) %>%
  na.omit()

music_positive <- bind_cols(filtered_music_pos)

pic_negative <- bind_cols(filtered_pic_neg)

pic_positive <- bind_cols(filtered_pic_pos)

# Display the result
music_negative
music_positive
pic_negative
pic_positive
```

#scoring granularity responses
```{r}
#music neg
music_negative_list <- split(music_negative, music_negative$Participant.Public.ID)

results <- 
  expand.grid(
    ID = names(music_negative_list)
  )

i = seq(seq_along(music_negative_list))

# with irr
for(i in seq_along(music_negative_list)) {
  icc_result <-  (music_negative_list[[i]]) %>%
    select(-c("Participant.Public.ID")) %>%
 icc("twoway", type = "consistency", unit = "average")
   results$negmusicICC[i] = 1 - icc_result$value
}

#pos music
music_positive_list <- split(music_positive, music_positive$Participant.Public.ID)

i = seq(seq_along(music_positive_list))

for(i in seq_along(music_positive_list)) {
  icc_result <-  (music_positive_list[[i]]) %>%
    select(-c("Participant.Public.ID")) %>%
 icc("twoway", type = "consistency", unit = "average")
   results$posmusicICC[i] = 1 - icc_result$value
}

#neg pic
pic_negative_list <- split(pic_negative, pic_negative$Participant.Public.ID)

i = seq(seq_along(pic_negative_list))

for(i in seq_along(pic_negative_list)) {
  icc_result <-  (pic_negative_list[[i]]) %>%
    select(-c("Participant.Public.ID")) %>%
 icc("twoway", type = "consistency", unit = "average")
   results$negpicICC[i] = 1 - icc_result$value
}

#pos pic
pic_positive_list <- split(pic_positive, pic_positive$Participant.Public.ID)

i = seq(seq_along(pic_positive_list))

for(i in seq_along(pic_positive_list)) {
  icc_result <-  (pic_positive_list[[i]]) %>%
    select(-c("Participant.Public.ID")) %>%
 icc("twoway", type = "consistency", unit = "average")
   results$pospicICC[i] = 1 - icc_result$value
}

```


##----Condensed version of above------
```{r}
# Function to compute ICC and store results
compute_icc <- function(data_list, result_column) {
  sapply(seq_along(data_list), function(i) {
    icc_result <- data_list[[i]] %>%
      select(-Participant.Public.ID) %>%
      icc(model = "twoway", type = "consistency", unit = "average")
    1 - icc_result$value
  })
}

# Create a list of data frames split by Participant.Public.ID
music_negative_list <- split(music_negative, music_negative$Participant.Public.ID)
music_positive_list <- split(music_positive, music_positive$Participant.Public.ID)
pic_negative_list <- split(pic_negative, pic_negative$Participant.Public.ID)
pic_positive_list <- split(pic_positive, pic_positive$Participant.Public.ID)

# Initialize results DataFrame
results <- expand.grid(ID = names(music_negative_list))

# Compute ICC values for each subset and add to results
results$negmusicICC <- compute_icc(music_negative_list, "negmusicICC")
results$posmusicICC <- compute_icc(music_positive_list, "posmusicICC")
results$negpicICC <- compute_icc(pic_negative_list, "negpicICC")
results$pospicICC <- compute_icc(pic_positive_list, "pospicICC")

# Display the result
results
```


```{r}
# with psych package
for(i in seq_along(music_negative_list)) {
  icc_result <-  (music_negative_list[[i]]) %>%
    select(-c("Participant.Public.ID")) %>%
 ICC()
  icc_value <- icc_result$results %>%
    filter(type == "ICC3k") %>%
    pull(ICC)
  results$negmusicICC[i] = 1 - icc_value
}
```

##--Correlation and differences test--
```{r}
cor.test(resultse$posmusicICC, results$pospicICC)
cor.test(results$negmusicICC, results$negpicICC)
t.test(results$posmusicICC, results$pospicICC, paired = TRUE)

pos_graph <- ggplot(data = results_, aes(x = pospicICC, y = posmusicICC)) +
  geom_point() +
  stat_smooth(method = 'lm') +
  xlab('Positive Picture Emotion Granularity') +
  ylab('Positive Music Emotion Granularity') +
  theme_classic() +
  theme(axis.title.x = element_text(size=14, face='bold'), axis.title.y = element_text(size=14, face='bold'), axis.text.x = element_text(size=12), axis.text.y = element_text(size=12))

ggsave('../results/rating-task/Pos_Graph.png', pos_graph, width = 9)

neg_graph <- ggplot(data = results, aes(x = negpicICC, y = negmusicICC)) +
  geom_point() +
  stat_smooth(method = 'lm') +
  xlab('Negative Picture Emotion Granularity') +
  ylab('Negative Music Emotion Granularity') +
  theme_classic() +
  theme(axis.title.x = element_text(size=14, face='bold'), axis.title.y = element_text(size=14, face='bold'), axis.text.x = element_text(size=12), axis.text.y = element_text(size=12))

ggsave('../results/rating-task/Neg_Graph.png', neg_graph, width = 9)

mean_comparison <- results %>%
  pivot_longer(negmusicICC:pospicICC) %>%
  ggplot(aes(x=name, y=value)) +
  stat_summary(fun.data='mean_cl_normal', geom = 'errorbar', width = 0.2) +
  stat_summary(fun.data='mean_cl_normal', geom = 'pointrange', width = 0.2) +
  theme_bw() +
  xlab('Stimulus and Valence') +
  ylab('Emotion Granularity') +
  theme(axis.title.x = element_text(size=14, face='bold'), axis.title.y = element_text(size=14, face='bold'), axis.text.x = element_text(size=12), axis.text.y = element_text(size=12)) +
  scale_x_discrete(labels = c('Negative Music', 'Negative Picture', 'Positive Music', 'Positive Picture'))

ggsave('../results/rating-task/Mean_Comparisons.png', mean_comparison, width = 9)
```

##--Plotting means of emotion word ratings--
```{r}
# music neg
music_negative_summary <- music_negative %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

music_negative_means <- ggplot(music_negative_summary, aes(x = variable, y = mean_value)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), width = 0.2) +
  labs(title = "Gorilla Music Negative Emotion Means", x = "Emotion", y = "Mean") +
  theme_bw()

ggsave('../results/rating-task/Music_Negative_Means_8_7_24.png', music_negative_means, width = 9)

# music pos
music_positive_summary <- music_positive %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

music_positive_means <- ggplot(music_positive_summary, aes(x = variable, y = mean_value)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), width = 0.2) +
  labs(title = "Gorilla Music Positive Emotion Means", x = "Emotion", y = "Mean") +
  theme_bw()

ggsave('../results/rating-task/Music_Positive_Means_8_7_24.png', music_positive_means, width = 9)

# pic pos
pic_positive_summary <- pic_positive %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

pic_positive_means <- ggplot(pic_positive_summary, aes(x = variable, y = mean_value)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), width = 0.2) +
  labs(title = "Gorilla Picture Positive Emotion Means", x = "Emotion", y = "Mean") +
  theme_bw()

ggsave('../results/rating-task/Picture_Positive_Means_8_7_24.png', pic_positive_means, width = 9)

# pic neg
pic_negative_summary <- pic_negative %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

pic_negative_means <- ggplot(pic_negative_summary, aes(x = variable, y = mean_value)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), width = 0.2) +
  labs(title = "Gorilla Picture Negative Emotion Means", x = "Emotion", y = "Mean") +
  theme_bw()

ggsave('../results/rating-task/Picture_Negative_Means_8_7_24.png', pic_negative_means, width = 9)
```

##--Graphs printed together to have scale reference--
```{r}
music_negative_summary$type <- "Music"
music_positive_summary$type <- "Music"
pic_negative_summary$type <- "Picture"
pic_positive_summary$type <- "Picture"
neg_summary <- bind_rows(music_negative_summary, pic_negative_summary)
pos_summary <- bind_rows(music_positive_summary, pic_positive_summary)

# Plot for negative emotions
neg_plot <- ggplot(neg_summary, aes(x = variable, y = mean_value, color = type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                width = 0.2) +
  labs(title = "Negative Emotion Means", x = "Emotion", y = "Mean") +
  theme_bw()

# Plot for positive emotions
pos_plot <- ggplot(pos_summary, aes(x = variable, y = mean_value, color = type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                width = 0.2) +
  labs(title = "Positive Emotion Means", x = "Emotion", y = "Mean") +
  theme_bw()

# Save the plots
ggsave('../results/rating-task/Negative_Emotion_Means_8_7_24.png', neg_plot, width = 9)
ggsave('../results/rating-task/Positive_Emotion_Means_8_7_24.png', pos_plot, width = 9)


```

##-Percent of nonzero responses--
```{r}
library(knitr)
library(readr)
library(gridExtra)
library(grid)
library(png)

# Function to calculate the percentage of non-zero responses for each column
calculate_non_zero_percentage <- function(df) {
  df %>%
    select(-Participant.Public.ID) %>%
    summarise(across(everything(), ~ round(sum(!is.na(.) & . != 0) / sum(!is.na(.)) * 100)))
}

# Calculate percentages and create tables
tables <- list(
  list(data = music_negative, caption = "% of Non-Zero Responses for Negative Emotion Words (Music)"),
  list(data = pic_negative, caption = "% of Non-Zero Responses for Negative Emotion Words (Pictures)"),
    list(data = music_positive, caption = "% of Non-Zero Responses for Positive Emotion Words (Music)"),
  list(data = pic_positive, caption = "% of Non-Zero Responses for Positive Emotion Words (Pictures)")
)

# Create grobs for each table and caption
table_grobs <- lapply(tables, function(tbl) {
  percentages <- calculate_non_zero_percentage(tbl$data)
  table_grob <- tableGrob(percentages, theme = ttheme_minimal())
  caption_grob <- textGrob(tbl$caption, gp = gpar(fontsize = 10))
  arrangeGrob(caption_grob, table_grob, ncol = 1)
})

# Arrange all tables vertically
arranged_tables <- do.call(arrangeGrob, c(table_grobs, ncol = 1))

# Save the arranged tables as a PNG file
png("../results/rating-task/emotion_response_percentages_8_7_24.png", width = 400, height = 400)
grid.draw(arranged_tables)
dev.off()
```


##--Separating pics and music by valence (pos/neg) and arousal (high/low)--
```{r}
pos_high_pic <- c("Beach 1.jpg", "Cat 5.jpg", "Fireworks 6.jpg", "Lake 12.jpg", "Rainbow 2.jpg")
pos_high_pic_data <- granularity_pic %>%
  filter(Spreadsheet..Image %in% pos_high_pic)

pos_low_pic <- c("Clean 1.jpg", "Cups 3.jpg", "Heart 3.jpg", "Rocks 1.jpg", "Snow 1.jpg")
pos_low_pic_data <- granularity_pic %>%
  filter(Spreadsheet..Image %in% pos_low_pic)

neg_high_pic <- c("Cockroach 3.jpg", "Dirt 1.jpg", "Ferret 1.jpg", "Fire 10.jpg", "Flood 1.jpg", "Garbage dump 2.jpg")
neg_high_pic_data <- granularity_pic %>%
  filter(Spreadsheet..Image %in% neg_high_pic)

neg_low_pic <- c("Destruction 2.jpg", "Garbage dump 1.jpg", "Prison 2.jpg", "Toilet 4.jpg")
neg_low_pic_data <- granularity_pic %>%
  filter(Spreadsheet..Image %in% neg_low_pic)

pos_high_music <- c("3_pieceB_joyous_anxious_sad_5.mp3", "6_pieceB_anxious_calm_joyous_8.mp3", "7_pieceB_joyous_anxious_sad_5.mp3", "7_pieceB_joyous_anxious_sad_6.mp3")
pos_high_music_data <- granularity_music %>%
  filter(Spreadsheet..Audio %in% pos_high_music)

pos_low_music <- c("5_pieceB_calm_sad_anxious_7.mp3", "6_pieceB_anxious_calm_joyous_5.mp3", "6_pieceB_anxious_calm_joyous_7.mp3", "12_pieceA_joyous_sad_anxious_2.mp3", "12_pieceA_joyous_sad_anxious_3.mp3", "12_pieceA_joyous_sad_anxious_9.mp3")
pos_low_music_data <- granularity_music %>%
  filter(Spreadsheet..Audio %in% pos_low_music)

neg_high_music <- c("3_pieceB_joyous_anxious_sad_1.mp3", "11_pieceA_calm_anxious_sad_4.mp3", "11_pieceA_calm_anxious_sad_5.mp3", "11_pieceA_calm_anxious_sad_6.mp3", "11_pieceA_calm_anxious_sad_8.mp3")
neg_high_music_data <- granularity_music %>%
  filter(Spreadsheet..Audio %in% neg_high_music)

neg_low_music <- c("5_pieceB_calm_sad_anxious_1.mp3", "5_pieceB_calm_sad_anxious_2.mp3", "5_pieceB_calm_sad_anxious_3.mp3", "5_pieceB_calm_sad_anxious_9.mp3", "11_pieceA_calm_anxious_sad_2.mp3")
neg_low_music_data <- granularity_music %>%
  filter(Spreadsheet..Audio %in% neg_low_music)
```

```{r}
# write.csv(pos_low_music_data, "../data/rating-task/pos_low_music_data.csv")

# 6 clips
averages_pos_low_music <- pos_low_music_data %>%
  group_by(Spreadsheet..Audio) %>%
  summarise(Average.Response = mean(Response, na.rm = TRUE))
# for pos low music, lowest is 12_pieceA_joyous_sad_anxious_9.mp3
# second lowest is 12_pieceA_joyous_sad_anxious_3.mp3

# 4 clips
averages_pos_high_music <- pos_high_music_data %>%
  group_by(Spreadsheet..Audio) %>%
  summarise(Average.Response = mean(Response, na.rm = TRUE))
# for pos high music, lowest is 6_pieceB_anxious_calm_joyous_8.mp3

# 5 clips
averages_neg_low_music <- neg_low_music_data %>%
  group_by(Spreadsheet..Audio) %>%
  summarise(Average.Response = mean(Response, na.rm = TRUE))
# for neg low music, lowest is 5_pieceB_calm_sad_anxious_3.mp3

# 5 clips
averages_neg_high_music <- neg_high_music_data %>%
  group_by(Spreadsheet..Audio) %>%
  summarise(Average.Response = mean(Response, na.rm = TRUE))
# for neg high music, lowest is 11_pieceA_calm_anxious_sad_5.mp3

# 5 pics
averages_pos_low_pic <- pos_low_pic_data %>%
  group_by(Spreadsheet..Image) %>%
  summarise(Average.Response = mean(Response, na.rm = TRUE))
# for pos low pic, lowest is Hearts 3.jpg
# second lowest is Cups 3.jpg

# 5 pics
averages_pos_high_pic <- pos_high_pic_data %>%
  group_by(Spreadsheet..Image) %>%
  summarise(Average.Response = mean(Response, na.rm = TRUE))
# for pos high pic, lowest is Fireworks 6.jpg

# 4 pics
averages_neg_low_pic <- neg_low_pic_data %>%
  group_by(Spreadsheet..Image) %>%
  summarise(Average.Response = mean(Response, na.rm = TRUE))
# for neg low pic, lowest is Prison 2.jpg

# 6 pics
averages_neg_high_pic <- neg_high_pic_data %>%
  group_by(Spreadsheet..Image) %>%
  summarise(Average.Response = mean(Response, na.rm = TRUE))
# for neg high pic, lowest is Cockroach 3.jpg
# second lowest is Ferret 1.jpg (but higher than Prison 2.jpg)

all_averages <- bind_rows(
  averages_pos_low_music %>% mutate(Type = "pos_low_music"),
  averages_pos_high_music %>% mutate(Type = "pos_high_music"),
  averages_neg_low_music %>% mutate(Type = "neg_low_music"),
  averages_neg_high_music %>% mutate(Type = "neg_high_music"),
  averages_pos_low_pic %>% mutate(Type = "pos_low_pic"),
  averages_pos_high_pic %>% mutate(Type = "pos_high_pic"),
  averages_neg_low_pic %>% mutate(Type = "neg_low_pic"),
  averages_neg_high_pic %>% mutate(Type = "neg_high_pic")
)

neg_music_averages <- bind_rows(
  averages_neg_low_music %>% mutate(Type = "neg_low_music"),
  averages_neg_high_music %>% mutate(Type = "neg_high_music")
)

pos_music_averages <- bind_rows(
  averages_pos_low_music %>% mutate(Type = "pos_low_music"),
  averages_pos_high_music %>% mutate(Type = "pos_high_music")
)

neg_pic_averages <- bind_rows(
  averages_neg_low_pic %>% mutate(Type = "neg_low_pic"),
  averages_neg_high_pic %>% mutate(Type = "neg_high_pic")
)

pos_pic_averages <- bind_rows(
  averages_pos_low_pic %>% mutate(Type = "pos_low_pic"),
  averages_pos_high_pic %>% mutate(Type = "pos_high_pic")
)

min_values <- all_averages %>%
  group_by(Type) %>%
  filter(Average.Response == min(Average.Response)) %>%
  ungroup()

all_stims_plotted <- ggplot(all_averages, aes(x = Type, y = Average.Response)) +
  geom_point() +
  geom_text(data = min_values, aes(label = ifelse(is.na(Spreadsheet..Audio), Spreadsheet..Image, Spreadsheet..Audio)), vjust = -1, hjust = 0.5, size = 3, color = "red") +
  labs(title = "All Stims Response Averages", x = "Quadrant", y = "Mean Response") +
  theme_bw()

ggsave('../results/rating-task/All_Stims_Means_8_7_24.png', all_stims_plotted, width = 14)
```

##-- NOTHING BELOW HERE HAS BEEN UPDATED FOR THE V11 DATA
##--Reformatting data by valence and arousal--
```{r}
# Function to generate filtered data
generate_filtered_data <- function(data_list, emotions, media_type) {
  lapply(seq_along(emotions), function(i) {
    filter_and_rename(data_list, emotions[i], media_type, keep_id = (i == 1))
  })
}

# Generate filtered data for music and pictures
neg_emo_music_neg_high <- generate_filtered_data(neg_high_music_data, neg_emotions, "Audio")
pos_emo_music_neg_high <- generate_filtered_data(neg_high_music_data, pos_emotions, "Audio")

neg_emo_music_neg_low <- generate_filtered_data(neg_low_music_data, neg_emotions, "Audio")
pos_emo_music_neg_low <- generate_filtered_data(neg_low_music_data, pos_emotions, "Audio")

neg_emo_music_pos_high <- generate_filtered_data(pos_high_music_data, neg_emotions, "Audio")
pos_emo_music_pos_high <- generate_filtered_data(pos_high_music_data, pos_emotions, "Audio")

neg_emo_music_pos_low <- generate_filtered_data(pos_low_music_data, neg_emotions, "Audio")
pos_emo_music_pos_low <- generate_filtered_data(pos_low_music_data, pos_emotions, "Audio")

neg_emo_pic_neg_high <- generate_filtered_data(neg_high_pic_data, neg_emotions, "Image")
pos_emo_pic_neg_high <- generate_filtered_data(neg_high_pic_data, pos_emotions, "Image")

neg_emo_pic_neg_low <- generate_filtered_data(neg_low_pic_data, neg_emotions, "Image")
pos_emo_pic_neg_low <- generate_filtered_data(neg_low_pic_data, pos_emotions, "Image")

neg_emo_pic_pos_high <- generate_filtered_data(pos_high_pic_data, neg_emotions, "Image")
pos_emo_pic_pos_high <- generate_filtered_data(pos_high_pic_data, pos_emotions, "Image")

neg_emo_pic_pos_low <- generate_filtered_data(pos_low_pic_data, neg_emotions, "Image")
pos_emo_pic_pos_low <- generate_filtered_data(pos_low_pic_data, pos_emotions, "Image")

# Adjusting all positive emotion word dataframes accordingly due to the "satisfied" "relaxed" swap
pos_emo_music_neg_high[[2]] <- extend_df(pos_emo_music_neg_high[[2]], 10)
pos_emo_music_neg_high[[6]] <- prepend_rows(pos_emo_music_neg_high[[6]], 15)

pos_emo_music_neg_low[[2]] <- extend_df(pos_emo_music_neg_low[[2]], 10)
pos_emo_music_neg_low[[6]] <- prepend_rows(pos_emo_music_neg_low[[6]], 15)

pos_emo_music_pos_high[[2]] <- extend_df(pos_emo_music_pos_high[[2]], 8)
pos_emo_music_pos_high[[6]] <- prepend_rows(pos_emo_music_pos_high[[6]], 12)

pos_emo_music_pos_low[[2]] <- extend_df(pos_emo_music_pos_low[[2]], 12)
pos_emo_music_pos_low[[6]] <- prepend_rows(pos_emo_music_pos_low[[6]], 18)

pos_emo_pic_neg_high[[2]] <- extend_df(pos_emo_pic_neg_high[[2]], 12)
pos_emo_pic_neg_high[[6]] <- prepend_rows(pos_emo_pic_neg_high[[6]], 18)

pos_emo_pic_neg_low[[2]] <- extend_df(pos_emo_pic_neg_low[[2]], 8)
pos_emo_pic_neg_low[[6]] <- prepend_rows(pos_emo_pic_neg_low[[6]], 12)

pos_emo_pic_pos_high[[2]] <- extend_df(pos_emo_pic_pos_high[[2]], 10)
pos_emo_pic_pos_high[[6]] <- prepend_rows(pos_emo_pic_pos_high[[6]], 15)

pos_emo_pic_pos_low[[2]] <- extend_df(pos_emo_pic_pos_low[[2]], 10)
pos_emo_pic_pos_low[[6]] <- prepend_rows(pos_emo_pic_pos_low[[6]], 15)

# Combine the results
neg_music_neg_high <- bind_cols(neg_emo_music_neg_high)
pos_music_neg_high <- bind_cols(pos_emo_music_neg_high)

neg_music_neg_low <- bind_cols(neg_emo_music_neg_low)
pos_music_neg_low <- bind_cols(pos_emo_music_neg_low)

neg_music_pos_high <- bind_cols(neg_emo_music_pos_high)
pos_music_pos_high <- bind_cols(pos_emo_music_pos_high)

neg_music_pos_low <- bind_cols(neg_emo_music_pos_low)
pos_music_pos_low <- bind_cols(pos_emo_music_pos_low)

neg_pic_neg_high <- bind_cols(neg_emo_pic_neg_high)
pos_pic_neg_high <- bind_cols(pos_emo_pic_neg_high)

neg_pic_neg_low <- bind_cols(neg_emo_pic_neg_low)
pos_pic_neg_low <- bind_cols(pos_emo_pic_neg_low)

neg_pic_pos_high <- bind_cols(neg_emo_pic_pos_high)
pos_pic_pos_high <- bind_cols(pos_emo_pic_pos_high)

neg_pic_pos_low <- bind_cols(neg_emo_pic_pos_low)
pos_pic_pos_low <- bind_cols(pos_emo_pic_pos_low)

```

##--Calculating means for each quadrant--
```{r}
#### Positive Valence, High Arousal ####

## Negative Emotions ##

# Music #
neg_music_pos_high_summary <- neg_music_pos_high %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

# Pic #
neg_pic_pos_high_summary <- neg_pic_pos_high %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

## Positive Emotions ##

# Music #
pos_music_pos_high_summary <- pos_music_pos_high %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

# Pic #
pos_pic_pos_high_summary <- pos_pic_pos_high %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

#### Positive Valence, Low Arousal ####

# Music #
neg_music_pos_low_summary <- neg_music_pos_low %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

# Pic #
neg_pic_pos_low_summary <- neg_pic_pos_low %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

## Positive Emotions ##

# Music #
pos_music_pos_low_summary <- pos_music_pos_low %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

# Pic #
pos_pic_pos_low_summary <- pos_pic_pos_low %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

#### Negative Valence, High Arousal ####

## Negative Emotions ##

# Music #
neg_music_neg_high_summary <- neg_music_neg_high %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

# Pic #
neg_pic_neg_high_summary <- neg_pic_neg_high %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

## Positive Emotions ##

# Music #
pos_music_neg_high_summary <- pos_music_neg_high %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

# Pic #
pos_pic_neg_high_summary <- pos_pic_neg_high %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

#### Negative Valence, Low Arousal ####

## Negative Emotions ##

# Music #
neg_music_neg_low_summary <- neg_music_neg_low %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

# Pic #
neg_pic_neg_low_summary <- neg_pic_neg_low %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

## Positive Emotions ##

# Music #
pos_music_neg_low_summary <- pos_music_neg_low %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )

# Pic #
pos_pic_neg_low_summary <- pos_pic_neg_low %>%
  select(-Participant.Public.ID) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarize(
    mean_value = mean(value, na.rm = TRUE),
    se_value = sd(value, na.rm = TRUE) / sqrt(n())
  )
```

##--Graphs printed together to have scale reference--
```{r}
pos_music_neg_high_summary$type <- "Music"
neg_music_neg_high_summary$type <- "Music"
pos_music_neg_low_summary$type <- "Music"
neg_music_neg_low_summary$type <- "Music"

pos_music_pos_high_summary$type <- "Music"
neg_music_pos_high_summary$type <- "Music"
pos_music_pos_low_summary$type <- "Music"
neg_music_pos_low_summary$type <- "Music"

pos_pic_neg_high_summary$type <- "Picture"
neg_pic_neg_high_summary$type <- "Picture"
pos_pic_neg_low_summary$type <- "Picture"
neg_pic_neg_low_summary$type <- "Picture"

pos_pic_pos_high_summary$type <- "Picture"
neg_pic_pos_high_summary$type <- "Picture"
pos_pic_pos_low_summary$type <- "Picture"
neg_pic_pos_low_summary$type <- "Picture"


## Negative Emotions for Negative Valence, High Arousal
neg_emo_neg_high_summary <- bind_rows(neg_music_neg_high_summary, neg_pic_neg_high_summary)

## Positive Emotions for Negative Valence, High Arousal
pos_emo_neg_high_summary <- bind_rows(pos_music_neg_high_summary, pos_pic_neg_high_summary)

## Negative Emotions for Negative Valence, Low Arousal
neg_emo_neg_low_summary <- bind_rows(neg_music_neg_low_summary, neg_pic_neg_low_summary)

## Positive Emotions for Negative Valence, Low Arousal
pos_emo_neg_low_summary <- bind_rows(pos_music_neg_low_summary, pos_pic_neg_low_summary)

## Negative Emotions for Positive Valence, High Arousal
neg_emo_pos_high_summary <- bind_rows(neg_music_pos_high_summary, neg_pic_pos_high_summary)

## Positive Emotions for Positive Valence, High Arousal
pos_emo_pos_high_summary <- bind_rows(pos_music_pos_high_summary, pos_pic_pos_high_summary)

## Negative Emotions for Positive Valence, Low Arousal
neg_emo_pos_low_summary <- bind_rows(neg_music_pos_low_summary, neg_pic_pos_low_summary)

## Positive Emotions for Positive Valence, Low Arousal
pos_emo_pos_low_summary <- bind_rows(pos_music_pos_low_summary, pos_pic_pos_low_summary)

# Plot Negative Emotions for Negative Valence, High Arousal Stimuli
neg_emo_neg_high_plot <- ggplot(neg_emo_neg_high_summary, aes(x = variable, y = mean_value, color = type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                width = 0.2) +
  labs(title = "Negative Emotion Means for Negative Valence, High Arousal Stimuli", x = "Emotion", y = "Mean") +
  theme_bw()

# Plot Positive Emotions for Negative Valence, High Arousal Stimuli
pos_emo_neg_high_plot <- ggplot(pos_emo_neg_high_summary, aes(x = variable, y = mean_value, color = type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                width = 0.2) +
  labs(title = "Positive Emotion Means for Negative Valence, High Arousal Stimuli", x = "Emotion", y = "Mean") +
  theme_bw()

# Plot Negative Emotions for Negative Valence, Low Arousal Stimuli
neg_emo_neg_low_plot <- ggplot(neg_emo_neg_low_summary, aes(x = variable, y = mean_value, color = type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                width = 0.2) +
  labs(title = "Negative Emotion Means for Negative Valence, Low Arousal Stimuli", x = "Emotion", y = "Mean") +
  theme_bw()

# Plot Positive Emotions for Negative Valence, Low Arousal Stimuli
pos_emo_neg_low_plot <- ggplot(pos_emo_neg_low_summary, aes(x = variable, y = mean_value, color = type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                width = 0.2) +
  labs(title = "Positive Emotion Means for Negative Valence, Low Arousal Stimuli", x = "Emotion", y = "Mean") +
  theme_bw()

# Plot Negative Emotions for Positive Valence, High Arousal Stimuli
neg_emo_pos_high_plot <- ggplot(neg_emo_pos_high_summary, aes(x = variable, y = mean_value, color = type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                width = 0.2) +
  labs(title = "Negative Emotion Means for Positive Valence, High Arousal Stimuli", x = "Emotion", y = "Mean") +
  theme_bw()

# Plot Positive Emotions for Positive Valence, High Arousal Stimuli
pos_emo_pos_high_plot <- ggplot(pos_emo_pos_high_summary, aes(x = variable, y = mean_value, color = type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                width = 0.2) +
  labs(title = "Positive Emotion Means for Positive Valence, High Arousal Stimuli", x = "Emotion", y = "Mean") +
  theme_bw()

# Plot Negative Emotions for Positive Valence, Low Arousal Stimuli
neg_emo_pos_low_plot <- ggplot(neg_emo_pos_low_summary, aes(x = variable, y = mean_value, color = type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                width = 0.2) +
  labs(title = "Negative Emotion Means for Positive Valence, Low Arousal Stimuli", x = "Emotion", y = "Mean") +
  theme_bw()

# Plot Positive Emotions for Positive Valence, Low Arousal Stimuli
pos_emo_pos_low_plot <- ggplot(pos_emo_pos_low_summary, aes(x = variable, y = mean_value, color = type, ymin = 0)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_value - se_value, ymax = mean_value + se_value), 
                width = 0.2) +
  labs(title = "Positive Emotion Means for Positive Valence, Low Arousal Stimuli", x = "Emotion", y = "Mean") +
  theme_bw()

# Save the plots
ggsave('../results/rating-task/Negative_Emotion_Means_NegV_HighA.png', neg_emo_neg_high_plot, width = 9)
ggsave('../results/rating-task/Positive_Emotion_Means_NegV_HighA.png', pos_emo_neg_high_plot, width = 9)
ggsave('../results/rating-task/Negative_Emotion_Means_NegV_LowA.png', neg_emo_neg_low_plot, width = 9)
ggsave('../results/rating-task/Positive_Emotion_Means_NegV_LowA.png', pos_emo_neg_low_plot, width = 9)
ggsave('../results/rating-task/Negative_Emotion_Means_PosV_HighA.png', neg_emo_pos_high_plot, width = 9)
ggsave('../results/rating-task/Positive_Emotion_Means_PosV_HighA.png', pos_emo_pos_high_plot, width = 9)
ggsave('../results/rating-task/Negative_Emotion_Means_PosV_LowA.png', neg_emo_pos_low_plot, width = 9)
ggsave('../results/rating-task/Positive_Emotion_Means_PosV_LowA.png', pos_emo_pos_low_plot, width = 9)

```

```