---
title: "adult_online_surveyscoring"
output:
  html_document: default
  pdf_document: default
date: "2025-12-19"
---

```{r}
library(tidyverse)
library(emmeans)
library(corrplot)
library(lme4)
```

#read in data
```{r}
final <- read.csv(file='../data/study2final_granularityscores.csv')
negative_ratings <- read.csv(file='../data/study2final_negativeratings.csv')
positive_ratings <- read.csv(file='../data/study2final_positiveratings.csv')
```

#replication tests for study1

#outlier detection
```{r}
ggplot(final, aes(y = negmusicICC)) +
  geom_boxplot()

ggplot(final, aes(y = posmusicICC)) +
  geom_boxplot()

# Function to replace IQR outliers with NA
remove_outliers_iqr <- function(df,col_name) {
  x = df[[col_name]]
  Q1 <- quantile(x, 0.25, na.rm = TRUE)
  Q3 <- quantile(x, 0.75, na.rm = TRUE)
  IQR_val <- Q3 - Q1

  lower_bound <- Q1 - 1.5 * IQR_val
  upper_bound <- Q3 + 1.5 * IQR_val

  # Replace outliers with NA
  df[[col_name]][x < lower_bound | x > upper_bound] <- NA
  df=df
}

final <- remove_outliers_iqr(final, "negmusicICC")
final <- remove_outliers_iqr(final, "negpicICC")
final <- remove_outliers_iqr(final, "posmusicICC")
final <- remove_outliers_iqr(final, "pospicICC")
```

#manipulation check - using same randomfx as converged model from study1
```{r}
#test interaction between stimulus type (music/picture), emotion rating valence (pos/negative), and stimulus valence
neg_ratingsperemotion <- negative_ratings %>%
  pivot_longer(gloomy:upset) 

pos_ratingsperemotion <- positive_ratings %>%
  pivot_longer(happy:relaxed)

pos_ratingsperemotion$rating_valence <- "positive"
neg_ratingsperemotion$rating_valence <- "negative"

master_ratingsperemotion <- rbind(pos_ratingsperemotion, neg_ratingsperemotion)

#assigning stimulus valence
# Positive and Negative picture and music lists
pos_pic <- c("Beach 1.jpg", "Fireworks 6.jpg", "Lake 12.jpg", "Rainbow 2.jpg", "Clean 1.jpg", "Heart 3.jpg", "Rocks 1.jpg", "Snow 1.jpg")
neg_pic <- c("Dirt 1.jpg", "Ferret 1.jpg", "Fire 10.jpg", "Flood 1.jpg", "Destruction 2.jpg", "Garbage dump 1.jpg", "Prison 2.jpg", "Toilet 4.jpg")

pos_music <- c("2_1.mp3", "4_1.mp3", "4_2.mp3", "6_5.mp3", "8_2.mp3", "10_1.mp3", "10_2.mp3", "12_2.mp3")
neg_music <- c("3_1.mp3", "5_14.mp3", "6_10.mp3", "7_10.mp3", "7_13.mp3", "11_2.mp3", "11_10.mp3", "11_11.mp3")

# Apply the filter function
# Create a function to filter data by positive or negative images/music
filter_by_type <- function(data, type_list, column_name) {
  data %>%
    filter(!!sym(column_name) %in% type_list)
}

pos_pic_data <- filter_by_type(master_ratingsperemotion, pos_pic, "stim")
pos_pic_data$stimulus_valence <- "positive"
neg_pic_data <- filter_by_type(master_ratingsperemotion, neg_pic, "stim")
neg_pic_data$stimulus_valence <- "negative"

pos_music_data <- filter_by_type(master_ratingsperemotion, pos_music, "stim")
pos_music_data$stimulus_valence <- "positive"
neg_music_data <- filter_by_type(master_ratingsperemotion, neg_music, "stim")
neg_music_data$stimulus_valence <- "negative"

master_ratingsperemotion <- rbind(pos_pic_data,neg_pic_data,pos_music_data,neg_music_data)

#m1 <- lmer(data=master_ratingsperemotion, (value) ~ condition*rating_valence*stimulus_valence +  (rating_valence|Participant.Public.ID),control=lmerControl(optimizer="bobyqa")) #removed stim intercept to assist in model convergence and main random effect of stimulus_valence (explained least amt of variance), 8/13/26 -- and the main effect of condition and interaction between rating valence and condition

m1 <- lmer(data=master_ratingsperemotion, (value) ~ condition*rating_valence*stimulus_valence + (rating_valence|Participant.Public.ID),control=lmerControl(optimizer="bobyqa"))
car::Anova(m1,type="II" )
summary(m1)

#simple test of means (i.e., seeing pos rated pos, neg rated neg)
test(emmeans(m1, ~ condition*rating_valence*stimulus_valence, lmerTest.limit = 64000, lmer.df = "satterthwaite"))

emmeans::test(emmeans(m1, pairwise ~ condition*rating_valence*stimulus_valence,lmerTest.limit = 64000,lmer.df = "satterthwaite"))
```

#heat map
```{r}
averages_pos <- positive_ratings %>%
  pivot_longer(happy:relaxed, names_to = "Emotion", values_to = "Response") %>%
  group_by(stim, condition, Emotion) %>%
  summarise(
     `Average\nRating` = mean(Response, na.rm = TRUE)
    )

averages_neg <- negative_ratings %>%
  pivot_longer(gloomy:upset, names_to = "Emotion", values_to = "Response") %>%
  group_by(stim, condition,Emotion) %>%
  summarise(
    `Average\nRating` = mean(Response, na.rm = TRUE)
    )

# Positive and Negative picture and music lists
pos_pic <- c("Beach 1.jpg", "Fireworks 6.jpg", "Lake 12.jpg", "Rainbow 2.jpg", "Clean 1.jpg", "Heart 3.jpg", "Rocks 1.jpg", "Snow 1.jpg")
neg_pic <- c("Dirt 1.jpg", "Ferret 1.jpg", "Fire 10.jpg", "Flood 1.jpg", "Destruction 2.jpg", "Garbage dump 1.jpg", "Prison 2.jpg", "Toilet 4.jpg")

pos_music <- c("2_1.mp3", "4_1.mp3", "4_2.mp3", "6_5.mp3", "8_2.mp3", "10_1.mp3", "10_2.mp3", "12_2.mp3")
neg_music <- c("3_1.mp3", "5_14.mp3", "6_10.mp3", "7_10.mp3", "7_13.mp3", "11_2.mp3", "11_10.mp3", "11_11.mp3")

# Apply the filter function
# Create a function to filter data by positive or negative images/music
filter_by_type <- function(data, type_list, column_name) {
  data %>%
    filter(!!sym(column_name) %in% type_list)
}
averages_master <- rbind(averages_pos,averages_neg)
pos_pic_data <- filter_by_type(averages_master, pos_pic, "stim")
neg_pic_data <- filter_by_type(averages_master, neg_pic, "stim")

pos_music_data <- filter_by_type(averages_master, pos_music, "stim")
neg_music_data <- filter_by_type(averages_master, neg_music, "stim")

neg_averages <- rbind(neg_pic_data,neg_music_data)

neg_averages$Emotion <- factor(neg_averages$Emotion, levels = c("sad", "scared", "gloomy", "anxious", "upset", "happy", "relaxed", "satisfied", "excited", "joyful"))

neg_averages <- neg_averages %>%
  mutate(condition = recode(condition, music = "Negatively-Valenced Music", pic = "Negatively-Valenced Images")) 

ggplot(neg_averages,aes(x = Emotion, y = stim, fill = `Average\nRating`)) +
    geom_tile() +
    #ggtitle(paste("Average Responses by Emotion and Stimulus for", group_name)) +
    xlab("Emotion") +
    ylab("Stimulus") +
    scale_fill_gradient(low = "blue", high = "red") +  # Adjust color scheme as needed
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, color = "black"), axis.text.y = element_text(color = "black"), plot.background = element_rect(fill = "white", color = NA),  # Set plot background to white
        panel.background = element_rect(fill = "white", color = NA),legend.title = element_text(size = 9), 
               legend.text = element_text(size = 8)) +
  facet_wrap(~condition, scales = "free") +
  geom_vline(xintercept=5.5, color="black", linetype="solid", size=1)

pos_averages <- rbind(pos_pic_data,pos_music_data)

pos_averages$Emotion <- factor(pos_averages$Emotion, levels = c("sad", "scared", "gloomy", "anxious", "upset", "happy", "relaxed", "satisfied", "excited", "joyful"))

pos_averages <- pos_averages %>%
  mutate(condition = recode(condition, music = "Positively-Valenced Music", pic = "Positiveley-Valenced Images"))

ggplot(pos_averages, aes(x = Emotion, y = stim, fill = `Average\nRating`)) +
    geom_tile() +
    #ggtitle(paste("Average Responses by Emotion and Stimulus for", group_name)) +
    xlab("Emotion") +
    ylab("Stimulus") +
    scale_fill_gradient(low = "blue", high = "red") +  # Adjust color scheme as needed
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, color = "black"), axis.text.y = element_text(color = "black"), plot.background = element_rect(fill = "white", color = NA),  # Set plot background to white
        panel.background = element_rect(fill = "white", color = NA),legend.title = element_text(size = 9), 
               legend.text = element_text(size = 8)) +
  facet_wrap(~condition, scales = "free") +
  geom_vline(xintercept=5.5, color="black", linetype="solid", size=1)

averages_total <- rbind(pos_averages, neg_averages)
averages_total$stim <- gsub(".jpg", "", averages_total$stim)
averages_total$stim <- gsub(".mp3", "", averages_total$stim)

averages_total_plot <-
ggplot(averages_total, aes(x = Emotion, y = stim, fill = `Average\nRating`)) +
    geom_tile() +
    #ggtitle(paste("Average Responses by Emotion and Stimulus for", group_name)) +
    xlab("Emotion") +
    ylab("Stimulus") +
    scale_fill_gradient(low = "blue", high = "red") +  # Adjust color scheme as needed
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, color = "black", size = 30), 
          axis.text.y = element_text(color = "black", size=30),
          strip.text = element_text(color = "black", size=30),
          axis.title = element_text(color = "black", size=36),
          plot.background = element_rect(fill = "white", color = NA),  # Set plot background to white
        panel.background = element_rect(fill = "white", color = NA),
        legend.title = element_text(size = 28), 
            legend.text = element_text(size = 30)
        ) +
  facet_wrap(~condition, scales = "free") +
  geom_vline(xintercept=5.5, color="black", linetype="solid", size=3)

ggsave('../heatmap_averagestudy2.png',averages_total_plot, dpi=1000,width=18, height=10.5)
```

#correlations
```{r}
#granularity across pics + music
##positive
cor.test(final$posmusicICC, final$pospicICC)

##negative
cor.test(final$negmusicICC, final$negpicICC)

##combined
cor.test(final$allmusicICC, final$allpicICC)
```

#t-test
```{r}
#granularity across pics + music
##positive
t.test(final$posmusicICC, final$pospicICC, paired=TRUE)

##negative
t.test(final$negmusicICC, final$negpicICC, paired=TRUE)

##combined
t.test(final$allmusicICC, final$allpicICC, paired=TRUE)
```

#average ratings for plot
```{r}
#gloomy sad scared anxious upset
negative_ratings$average <- (negative_ratings$gloomy + negative_ratings$sad + negative_ratings$scared + negative_ratings$anxious + negative_ratings$gloomy)/5

neg_averages <-
  negative_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(mean = mean(average))

neg_averages$valence <- "Negative"

#relaxed, excited, satisfied, happy, joyful
positive_ratings$average <- (positive_ratings$relaxed + positive_ratings$excited + positive_ratings$satisfied + positive_ratings$happy + positive_ratings$joyful)/5

pos_averages <-
  positive_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(mean = mean(average))

pos_averages$valence <- "Positive"

averages <- rbind(neg_averages, pos_averages)
```

#recreate plots from thesis sub
```{r}
pos_granularity_plot <- 
ggplot(data=final, aes(x=posmusicICC, y=pospicICC)) +
  theme_classic()+
  theme(legend.position = "none")+
  geom_point(alpha=0.7) +
  geom_smooth(method="lm") +
  xlab("Positive Emotional\nGranularity Score - Music") +
  ylab("Positive Emotional\nGranularity Score - Images") +
  theme(
    axis.title.x = element_text(family="Arial", size=20),
    axis.title.y = element_text(family="Arial",size=20),
    axis.text.x = element_text(family="Arial", size=14),
    axis.text.y = element_text(family="Arial",size=14)) +
    theme(
    axis.title.x = element_text(family="Arial", size=30),
    axis.title.y = element_text(family="Arial",size=30),
    axis.text.x = element_text(family="Arial", size=26),
    axis.text.y = element_text(family="Arial",size=26))

ggsave('../figures/study_posgrancor.png',dpi=1000, pos_granularity_plot, height=8)

neg_granularity_plot <-
ggplot(data=final, aes(x=negmusicICC, y=negpicICC)) +
  theme_classic()+
  theme(legend.position = "none")+
  geom_point(alpha=0.7) +
  geom_smooth(method="lm") +
  xlab("Negative Emotional\nGranularity Score - Music") +
  ylab("Negative Emotional\nGranularity Score - Images")+
  theme(
    axis.title.x = element_text(family="Arial", size=30),
    axis.title.y = element_text(family="Arial",size=30),
    axis.text.x = element_text(family="Arial", size=26),
    axis.text.y = element_text(family="Arial",size=26))

ggsave('../figures/study2_neggrancor.png',dpi=1000, neg_granularity_plot, height=8)


#differences in ICCs
granularity_scores_long <-
  final %>%
  pivot_longer(negmusicICC:allpicICC) 
  
granularity_scores_long$valence <- ifelse(grepl("^neg",granularity_scores_long$name), "Negative", "Positive")
granularity_scores_long$valence <- ifelse(grepl("^all",granularity_scores_long$name), "Combined", granularity_scores_long$valence)
granularity_scores_long$condition <- ifelse(grepl("pic",granularity_scores_long$name), "Images", "Music")

mag_difference <-
granularity_scores_long %>%
  subset(valence!="Combined") %>%
  ggplot(aes(x=condition, y=value)) +
  stat_summary(fun.data = 'mean_cl_normal', geom = 'errorbar', size=1.25, width = 0.1, alpha=0.7,position = position_nudge(x = .3, y = 0), color="red") +
  stat_summary(fun.data = 'mean_cl_normal', geom = 'pointrange',size=1.25, alpha=0.7,position = position_nudge(x = .3, y = 0), color="red")+
  theme_classic()+
  theme(legend.position = "none") +
  facet_wrap(~valence,scales = "free_x") +
  geom_jitter(alpha=0.7, width=0.075,size=3) +
  #geom_violinhalf(position = position_nudge(x = .2, y = 0))
  xlab("Condition") +
  ylab("Granularity Score") +
  theme(
    axis.title.x = element_text(family="Arial", size=50),
    axis.title.y = element_text(family="Arial",size=50),
    axis.text.x = element_text(family="Arial", size=44),
    axis.text.y = element_text(family="Arial",size=44),
    strip.text = element_text(family="Arial",size=46))

ggsave('../figures/study2_magdifference.png',dpi=1000, mag_difference, width=14, height=12)


#magnitude differences in raw ratings (not ICC)
ggplot(data=averages, aes(x=valence, y=mean, color=condition)) +
     stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0.05, alpha=0.7,position=position_dodge(width=0.2)) +
  stat_summary(fun.data = 'mean_se', geom = 'pointrange', alpha=0.7,position=position_dodge(width=0.2))+
  theme_classic()+
  theme(legend.position = "none") +
  xlab("Emotion Valence") +
  ylab("Rating") +
  scale_color_manual(values=c("#0072B2", "#D55E00" )) +
  scale_fill_manual(values=c("#0072B2","#D55E00"))
```

#investigating differences in granularity -- is there greater arousal-based differentiation?
```{r}
##Pos emotions
#relaxed, excited, satisfied, happy, joyful

#relaxed - excited
relaxed_excited_cor <-
  positive_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(relaxed, excited))

relaxed_excited_cor_pics <- relaxed_excited_cor %>%
  subset(condition == "pic")

relaxed_excited_cor_music <- relaxed_excited_cor %>%
  subset(condition == "music")

#relaxed - satisfied
relaxed_satisfied_cor <-
  positive_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(relaxed, satisfied))

relaxed_satisfied_cor_pics <- relaxed_satisfied_cor %>%
  subset(condition == "pic")

relaxed_satisfied_cor_music <- relaxed_satisfied_cor %>%
  subset(condition == "music")

#relaxed - happy
relaxed_happy_cor <-
  positive_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(relaxed, happy))

relaxed_happy_cor_pics <- relaxed_happy_cor %>%
  subset(condition == "pic")

relaxed_happy_cor_music <- relaxed_happy_cor %>%
  subset(condition == "music")

#relaxed - joyful
relaxed_joyful_cor <-
  positive_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(relaxed, joyful))

relaxed_joyful_cor_pics <- relaxed_joyful_cor %>%
  subset(condition == "pic")

relaxed_joyful_cor_music <- relaxed_joyful_cor %>%
  subset(condition == "music")

#excited - satisfied
excited_satisfied_cor <-
  positive_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(excited, satisfied))

excited_satisfied_cor_pics <- excited_satisfied_cor %>%
  subset(condition == "pic")

excited_satisfied_cor_music <- excited_satisfied_cor %>%
  subset(condition == "music")

#excited - happy
excited_happy_cor <-
  positive_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(excited, happy))

excited_happy_cor_pics <- excited_happy_cor %>%
  subset(condition == "pic")

excited_happy_cor_music <- excited_happy_cor %>%
  subset(condition == "music")

#excited - joyful
excited_joyful_cor <-
  positive_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(excited, joyful))

excited_joyful_cor_pics <- excited_joyful_cor %>%
  subset(condition == "pic")

excited_joyful_cor_music <- excited_joyful_cor %>%
  subset(condition == "music")

#satisfied - happy
satisfied_happy_cor <-
  positive_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(satisfied, happy))

satisfied_happy_cor_pics <- satisfied_happy_cor %>%
  subset(condition == "pic")

satisfied_happy_cor_music <- satisfied_happy_cor %>%
  subset(condition == "music")

#satisfied - joyful
satisfied_joyful_cor <-
  positive_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(satisfied, joyful))

satisfied_joyful_cor_pics <- satisfied_joyful_cor %>%
  subset(condition == "pic")

satisfied_joyful_cor_music <- satisfied_joyful_cor %>%
  subset(condition == "music")

#joyful - happy
joyful_happy_cor <-
  positive_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(joyful, happy))

joyful_happy_cor_pics <- joyful_happy_cor %>%
  subset(condition == "pic")

joyful_happy_cor_music <- joyful_happy_cor %>%
  subset(condition == "music")

#neg emotions
#gloomy sad scared anxious upset
#gloomy - sad
gloomy_sad_cor <-
  negative_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(gloomy, sad))

gloomy_sad_cor_pics <- gloomy_sad_cor %>%
  subset(condition == "pic")

gloomy_sad_cor_music <- gloomy_sad_cor %>%
  subset(condition == "music")

#gloomy - scared
gloomy_scared_cor <-
  negative_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(gloomy, scared))

gloomy_scared_cor_pics <- gloomy_scared_cor %>%
  subset(condition == "pic")

gloomy_scared_cor_music <- gloomy_scared_cor %>%
  subset(condition == "music")

#gloomy - anxious
gloomy_anxious_cor <-
  negative_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(gloomy, anxious))

gloomy_anxious_cor_pics <- gloomy_anxious_cor %>%
  subset(condition == "pic")

gloomy_anxious_cor_music <- gloomy_anxious_cor %>%
  subset(condition == "music")

#gloomy - upset
gloomy_upset_cor <-
  negative_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(gloomy, upset))

gloomy_upset_cor_pics <- gloomy_upset_cor %>%
  subset(condition == "pic")

gloomy_upset_cor_music <- gloomy_upset_cor %>%
  subset(condition == "music")

#sad - scared
sad_scared_cor <-
  negative_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(sad, scared))

sad_scared_cor_pics <- sad_scared_cor %>%
  subset(condition == "pic")

sad_scared_cor_music <- sad_scared_cor %>%
  subset(condition == "music")

#sad - anxious
sad_anxious_cor <-
  negative_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(sad, anxious))

sad_anxious_cor_pics <- sad_anxious_cor %>%
  subset(condition == "pic")

sad_anxious_cor_music <- sad_anxious_cor %>%
  subset(condition == "music")

#sad - upset
sad_upset_cor <-
  negative_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(sad, upset))

sad_upset_cor_pics <- sad_upset_cor %>%
  subset(condition == "pic")

sad_upset_cor_music <- sad_upset_cor %>%
  subset(condition == "music")

#scared - anxious
scared_anxious_cor <-
  negative_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(scared, anxious))

scared_anxious_cor_pics <- scared_anxious_cor %>%
  subset(condition == "pic")

scared_anxious_cor_music <- scared_anxious_cor %>%
  subset(condition == "music")

#scared - upset
scared_upset_cor <-
  negative_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(scared, upset))

scared_upset_cor_pics <- scared_upset_cor %>%
  subset(condition == "pic")

scared_upset_cor_music <- scared_upset_cor %>%
  subset(condition == "music")

#upset - anxious
upset_anxious_cor <-
  negative_ratings %>%
  group_by(Participant.Public.ID, condition) %>%
  dplyr::summarize(cor = cor(upset, anxious))

upset_anxious_cor_pics <- upset_anxious_cor %>%
  subset(condition == "pic")

upset_anxious_cor_music <- upset_anxious_cor %>%
  subset(condition == "music")
```

```{r}
##Pos emotions
#relaxed (low), excited (high), satisfied (low), happy (high), joyful (high)
relaxed_excited_cor$arousal_dif <- "different"
relaxed_satisfied_cor$arousal_dif <- "same"
relaxed_happy_cor$arousal_dif <- "different"
relaxed_joyful_cor$arousal_dif <- "different"
excited_satisfied_cor$arousal_dif <- "different"
excited_happy_cor$arousal_dif <- "same"
excited_joyful_cor$arousal_dif <- "same"
satisfied_happy_cor$arousal_dif <- "different"
satisfied_joyful_cor$arousal_dif <- "different"
joyful_happy_cor$arousal_dif <- "same"

master <- rbind(relaxed_excited_cor, relaxed_satisfied_cor, relaxed_happy_cor, 
                relaxed_joyful_cor,excited_satisfied_cor,excited_happy_cor,
                excited_joyful_cor,satisfied_happy_cor,satisfied_joyful_cor,
                joyful_happy_cor)
master$condition <- as.factor(master$condition)
contrasts(master$condition) <- c(-0.5,0.5)
master$arousal_dif <- as.factor(master$arousal_dif)
contrasts(master$arousal_dif) <- c(-0.5,0.5)

test <- lmer(data=master, scale(cor) ~ condition*arousal_dif + (condition*arousal_dif|Participant.Public.ID))
summary(test)

##Neg emotions
gloomy_sad_cor$arousal_dif <- "same"
gloomy_scared_cor$arousal_dif <- "different"
gloomy_anxious_cor$arousal_dif <- "different"
gloomy_upset_cor$arousal_dif <- "different"
sad_anxious_cor$arousal_dif <- "different"
sad_upset_cor$arousal_dif <- "different"
scared_anxious_cor$arousal_dif <- "same"
scared_upset_cor$arousal_dif <- "same"
upset_anxious_cor$arousal_dif <- "same"
sad_scared_cor$arousal_dif <- "different"

master_neg <- rbind(gloomy_sad_cor, gloomy_scared_cor, gloomy_anxious_cor, 
                gloomy_upset_cor,sad_anxious_cor,sad_upset_cor,
                scared_upset_cor,scared_anxious_cor,scared_anxious_cor,
                sad_scared_cor)
master_neg$condition <- as.factor(master_neg$condition)
contrasts(master_neg$condition) <- c(-0.5,0.5)
master_neg$arousal_dif <- as.factor(master_neg$arousal_dif)
contrasts(master_neg$arousal_dif) <- c(-0.5,0.5)

test <- lmer(data=master_neg, scale(cor) ~ condition*arousal_dif + (condition:arousal_dif + condition|Participant.Public.ID)) #removed main effect of arousal diff from random fx for convergence
summary(test)

master$valence <- "Positive"
master_neg$valence <- "Negative"

master_posneg <- rbind(master,master_neg)
```

#plot
```{r}
average_corr <-
master_posneg %>%
  group_by(condition, valence, Participant.Public.ID,arousal_dif) %>%
    summarise(
     `cor` = mean(cor, na.rm = TRUE)
    )  %>%
  mutate(arousal_dif = recode(arousal_dif, "different" = "Different", "same" = "Similar"))

arousal_differentiation <-
average_corr %>%
  mutate(arousal_dif = recode(arousal_dif, "different" = "Different", "same" = "Similar")) %>%
  ggplot(aes(x=arousal_dif, y=cor, color=condition)) +
   stat_summary(fun.data = 'mean_se', geom = 'errorbar',alpha=0.7, width = 0.03,size=0.75,position = position_nudge(x = .3, y = 0)) +
  stat_summary(fun.data = 'mean_se', geom = 'pointrange', alpha=0.7,size=0.4,position = position_nudge(x = .3, y = 0))+
  theme_classic() +
  theme(legend.position = "none") +
 facet_wrap(~valence)+
  xlab("Arousal Level") +
  ylab("Correlation Among Emotion Ratings")  +    
  theme(
    axis.title.x = element_text(family="Arial", size=50),
    axis.title.y = element_text(family="Arial",size=50),
    axis.text.x = element_text(family="Arial", size=44),
    axis.text.y = element_text(family="Arial",size=44),
    strip.text = element_text(family="Arial",size=44))+
  scale_color_manual(values=c("#0072B2", "#D55E00" )) +
  scale_fill_manual(values=c("#0072B2","#D55E00")) +
  geom_jitter(alpha=0.5, width=0.1,size=2)


ggsave('../figures/study2_arousal_differentiation.png',dpi=1000, arousal_differentiation, width=14, height=12)
```

#associations
```{r}
survey_measures <- final %>%
  select(
    CD.RISC_total,
    STAI_total,
    STAI_S_total,
    BDI_total,
    SCAARED_total,
    PMERQ_conf_unpl_sit,
    PMERQ_av_unpl_sit,
    PMERQ_foc_ew,
    PMERQ_cog_dis,
    PMERQ_cons_bf,
    PMERQ_red_ip,
    PMERQ_emo_share,
    PMERQ_exp_sup,
    PMERQ_res_conf,
    PMERQ_av_conf,
    DERS_non_ac,
    DERS_dif_gd,
    DERS_imp_con,
    DERS_lack_ea,
    DERS_lim_ers,
    DERS_lack_ec,
    negmusicICC,
    posmusicICC,
    negpicICC,
    pospicICC,
    #commented back in 7/31/26
  #  negICC,
  #  posICC
  )

numeric_columns <- survey_measures[, sapply(survey_measures, is.numeric)]

# Calculate the correlation matrix
correlation_matrix <- cor(numeric_columns, use = "complete.obs")

# Compute p-values
p_values1 <- cor.mtest(numeric_columns)
p_values <- p_values1$p

# Specify the folder where you want to save the file
output_folder <- "../results/"

# Combine the folder path with the file name
output_file <- file.path(output_folder, "online_adul_corr.png")

# Open a PNG device with the specified file path
png(output_file, width = 800, height = 800)

# Generate the corrplot
corrplot(correlation_matrix, method = "circle", type = "upper", 
         p.mat = p_values, sig.level = 0.05, insig = "blank",
         tl.col = "black", tl.srt = 45, addCoef.col = NULL,
         col = colorRampPalette(c("blue", "white", "red"))(200))

# Close the PNG device
dev.off()

# Specify the folder where you want to save the file
output_folder <- "../results/structural/"

# Combine the folder path with the file name
output_file <- file.path(output_folder, "Structural Correlations Right Hemisphere 9-30-26.png")

# Open a PNG device with the specified file path
png(output_file, width = 800, height = 800)

# Generate the corrplot
corrplot(correlation_matrix, method = "circle", type = "upper", 
         p.mat = p_values, sig.level = 0.05, insig = "blank",
         tl.col = "black", tl.srt = 45, addCoef.col = NULL,
         col = colorRampPalette(c("blue", "white", "red"))(200))

title(main = "Structural Correlations Right Hemisphere Study 2", col.main = "black", font.main = 4)

# Close the PNG device
dev.off()

cor.test(final$negpicICC, final$STAI_total)

sapply(numeric_columns, class)
```

#all correlation plots
```{r}
##ALL POS CORR PLOTS
icc_vars <- c("posICC", "pospicICC", "posmusicICC")
survey_vars <- c("BDI_total", "STAI_S_total", "STAI_total", "CD.RISC_total", "SCAARED_total", "DERS_non_ac", "DERS_dif_gd", "DERS_imp_con", "DERS_lack_ea", "DERS_lim_ers", "DERS_lack_ec", "PMERQ_conf_unpl_sit", "PMERQ_av_unpl_sit", "PMERQ_foc_ew", "PMERQ_cog_dis", "PMERQ_cons_bf", "PMERQ_red_ip", "PMERQ_emo_share", "PMERQ_exp_sup", "PMERQ_res_conf", "PMERQ_av_conf")

results <- data.frame(
  icc = character(),
  survey = character(),
  r = numeric(),
  r_squared = numeric(),
  p_value = numeric(),
  n = integer(),
  stringsAsFactors = FALSE
)

for (icc in icc_vars) {
  for (survey in survey_vars) {
    
    complete_data <- final[!is.na(final[[icc]]) & !is.na(final[[survey]]), ]
    n_obs <- nrow(complete_data)
    
    r <- cor.test(complete_data[[icc]], complete_data[[survey]])
    r_val <- round(as.numeric(r$estimate), 3)
    r_squared <- round(as.numeric(r$estimate)^2, 3)
    p_val <- r$p.value
    
    # Print to console
    cat("\n---", icc, "vs", survey, "---\n")
    cat("r =", r_val, "\n")
    cat("R\u00b2 =", r_squared, "\n")
    cat("p =", round(p_val, 4), "\n")
    cat("n =", n_obs, "\n")
    
    results <- rbind(results, data.frame(
      icc = icc,
      survey = survey,
      r = r_val,
      r_squared = r_squared,
      p_value = round(p_val, 4),
      n = n_obs
    ))
    
    p_label <- if (p_val < 0.001) "< .001" else paste0("= ", round(p_val, 3))
    
    p <- ggplot(complete_data, aes(x = .data[[icc]], y = .data[[survey]])) +
      geom_point() +
      geom_smooth(method = "lm", se = TRUE, color = "blue") +
      labs(
        x = icc,
        y = survey,
        title = paste(icc, "vs", survey),
        subtitle = paste0("R\u00b2 = ", r_squared, "  |  p ", p_label, "  |  n = ", n_obs)
      ) +
      theme_minimal()
    
    ggsave(file.path("plots", paste0("plot_", icc, "_", survey, ".png")), 
           plot = p, width = 6, height = 5, dpi = 300)
    
    print(p)
  }
}

cat("\n=== Summary Table (sorted by strength of association) ===\n")
results <- results[order(-abs(results$r)), ]
rownames(results) <- NULL
print(results)

##ALL NEG CORR PLOTS

library(ggplot2)

icc_vars <- c("negICC", "negpicICC", "negmusicICC")
survey_vars <- c("BDI_total", "STAI_S_total", "STAI_total", "CD.RISC_total", "SCAARED_total", "DERS_non_ac", "DERS_dif_gd", "DERS_imp_con", "DERS_lack_ea", "DERS_lim_ers", "DERS_lack_ec", "PMERQ_conf_unpl_sit", "PMERQ_av_unpl_sit", "PMERQ_foc_ew", "PMERQ_cog_dis", "PMERQ_cons_bf", "PMERQ_red_ip", "PMERQ_emo_share", "PMERQ_exp_sup", "PMERQ_res_conf", "PMERQ_av_conf")

results <- data.frame(
  icc = character(),
  survey = character(),
  r = numeric(),
  r_squared = numeric(),
  p_value = numeric(),
  n = integer(),
  stringsAsFactors = FALSE
)

for (icc in icc_vars) {
  for (survey in survey_vars) {
    
    complete_data <- final[!is.na(final[[icc]]) & !is.na(final[[survey]]), ]
    n_obs <- nrow(complete_data)
    
    r <- cor.test(complete_data[[icc]], complete_data[[survey]])
    r_val <- round(as.numeric(r$estimate), 3)
    r_squared <- round(as.numeric(r$estimate)^2, 3)
    p_val <- r$p.value
    
    # Print to console
    cat("\n---", icc, "vs", survey, "---\n")
    cat("r =", r_val, "\n")
    cat("R\u00b2 =", r_squared, "\n")
    cat("p =", round(p_val, 4), "\n")
    cat("n =", n_obs, "\n")
    
    results <- rbind(results, data.frame(
      icc = icc,
      survey = survey,
      r = r_val,
      r_squared = r_squared,
      p_value = round(p_val, 4),
      n = n_obs
    ))
    
    p_label <- if (p_val < 0.001) "< .001" else paste0("= ", round(p_val, 3))
    
    p <- ggplot(complete_data, aes(x = .data[[icc]], y = .data[[survey]])) +
      geom_point() +
      geom_smooth(method = "lm", se = TRUE, color = "blue") +
      labs(
        x = icc,
        y = survey,
        title = paste(icc, "vs", survey),
        subtitle = paste0("R\u00b2 = ", r_squared, "  |  p ", p_label, "  |  n = ", n_obs)
      ) +
      theme_minimal()
    
    ggsave(file.path("plots", paste0("plot_", icc, "_", survey, ".png")), 
           plot = p, width = 6, height = 5, dpi = 300)
    
    print(p)
  }
}

cat("\n=== Summary Table (sorted by strength of association) ===\n")
results <- results[order(-abs(results$r)), ]
rownames(results) <- NULL
print(results)


#PLOT FOR SLIDE 28 replication 8/5/26
library(ggplot2)

x_var <- "posmusicICC"
y_var <- "pospicICC"

# Remove missing data for this pair
plot_data <- final[!is.na(final[[x_var]]) & !is.na(final[[y_var]]), ]

# Calculate correlation
r <- cor.test(plot_data[[x_var]], plot_data[[y_var]])
r_val <- round(as.numeric(r$estimate), 2)

# Build plot
p <- ggplot(plot_data, aes(x = .data[[x_var]], y = .data[[y_var]])) +
  geom_point(color = "black", size = 2, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = "steelblue", fill = "lightblue") +
  annotate(
    "text",
    x = max(plot_data[[x_var]], na.rm = TRUE),
    y = min(plot_data[[y_var]], na.rm = TRUE),
    label = paste0("r = ", r_val),
    hjust = 1, vjust = 0,
    size = 5
  ) +
  labs(
    x = "Positive Emotion Granularity Score - Music",
    y = "Positive Emotion Granularity Score - Pictures"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    panel.grid.minor = element_blank(),
    axis.title = element_text(face = "bold")
  )

print(p)

#NEG VERSION of above
x_var <- "negmusicICC"
y_var <- "negpicICC"

# Remove missing data for this pair
plot_data <- final[!is.na(final[[x_var]]) & !is.na(final[[y_var]]), ]

# Calculate correlation
r <- cor.test(plot_data[[x_var]], plot_data[[y_var]])
r_val <- round(as.numeric(r$estimate), 2)

# Build plot
p <- ggplot(plot_data, aes(x = .data[[x_var]], y = .data[[y_var]])) +
  geom_point(color = "black", size = 2, alpha = 0.7) +
  geom_smooth(method = "lm", se = TRUE, color = "steelblue", fill = "lightblue") +
  annotate(
    "text",
    x = max(plot_data[[x_var]], na.rm = TRUE),
    y = min(plot_data[[y_var]], na.rm = TRUE),
    label = paste0("r = ", r_val),
    hjust = 1, vjust = 0,
    size = 5
  ) +
  labs(
    x = "Negative Emotion Granularity Score - Music",
    y = "Negative Emotion Granularity Score - Pictures"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    panel.grid.minor = element_blank(),
    axis.title = element_text(face = "bold")
  )

print(p)

```
#HEATMAP of ICCs vs. Surveys
```{r}
library(ggplot2)
library(reshape2)

icc_vars <- c("negICC", "negpicICC", "negmusicICC", "posICC", "pospicICC", "posmusicICC")
survey_vars <- c("BDI_total", "STAI_S_total", "STAI_total", "CD.RISC_total", "SCAARED_total")

# Build a correlation matrix (rows = ICC vars, cols = survey vars)
cor_matrix <- matrix(NA, nrow = length(icc_vars), ncol = length(survey_vars),
                      dimnames = list(icc_vars, survey_vars))
p_matrix <- cor_matrix  # store p-values too, for optional significance marking

for (icc in icc_vars) {
  for (survey in survey_vars) {
    complete_data <- final[!is.na(final[[icc]]) & !is.na(final[[survey]]), ]
    test <- cor.test(complete_data[[icc]], complete_data[[survey]])
    cor_matrix[icc, survey] <- test$estimate
    p_matrix[icc, survey] <- test$p.value
  }
}

# Reshape into long format for ggplot
cor_long <- melt(cor_matrix, varnames = c("icc", "survey"), value.name = "r")
p_long <- melt(p_matrix, varnames = c("icc", "survey"), value.name = "p")
heat_data <- merge(cor_long, p_long, by = c("icc", "survey"))

# Add significance stars
heat_data$sig <- ifelse(heat_data$p < 0.001, "***",
                  ifelse(heat_data$p < 0.01, "**",
                  ifelse(heat_data$p < 0.05, "*", "")))

# Build heatmap
p <- ggplot(heat_data, aes(x = survey, y = icc, fill = r)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(round(r, 2), sig)), size = 4) +
  scale_fill_gradient2(
    low = "steelblue", mid = "white", high = "firebrick",
    midpoint = 0, limits = c(-1, 1), name = "r"
  ) +
  labs(
    x = "Survey Measure",
    y = "ICC Variable",
    title = "Correlation Heatmap: ICC Variables vs Survey Measures",
    caption = "* p < .05   ** p < .01   *** p < .001"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid = element_blank()
  )

print(p)

ggsave("ICCSurvey_correlation_heatmap.png", plot = p, width = 8, height = 6, dpi = 300)

```



