---
title: "v23_Survey_Scoring"
output: html_document
date: "2024-10-08"
---

#replace "df" in script w/ dataframe name of survey.csv
```{r}
library(tidyverse)
install.packages("corrplot")
library(corrplot)
source("reverseCode.R")

data <- read.csv("../data/qualtrics/emo-granularity_October 8, 2024_09.26.csv")
df <- data %>%
  filter(Finished == 1) %>%
  filter(SURVEY_CODE != '')
```

#STAI
```{r}
STAI <- df %>%
  dplyr::select("STAI1_1":"STAI20_1")

STAI <- as.data.frame(lapply(STAI[,], as.integer))

cols_reverse <- c("STAI1_1","STAI3_1","STAI6_1","STAI7_1","STAI10_1","STAI13_1","STAI14_1","STAI16_1","STAI19_1")
STAI[cols_reverse] <- lapply(STAI[cols_reverse], reverseCode, min=1, max=4)

df$STAI_total <- apply(STAI,1,sum)
hist(df$STAI_total)
```

#CD-RISC
```{r}
CD.RISC <- df %>%
  dplyr::select("CD.RISC1_1":"CD.RISC10_1")

CD.RISC <- as.data.frame(lapply(CD.RISC[,], as.integer))

df$CD.RISC_total <- apply(CD.RISC,1,sum)
hist(df$CD.RISC_total)
```

#GoldMSI Scoring
```{r}
Gold <- df %>%
  dplyr::select("Q1.1_1":"Q1.38")
  
 # dplyr::select("X1..I.spend.a.lot.of.my.free.time.doing.music.related.activities....Completely.Disagree.Completely.Agree":"X38..I.listen.attentively.to.music.for.___.per.day.")

#delete atttention checking question
Gold$Qcheck <- NULL

Gold <- as.data.frame(lapply(Gold[,], as.integer))

# GoldMSI columns to reverse code and sub-score (for these questions, the correct answer (ie the more positive answer) is a higher number. Negative questions are reverse coded.) 

cols_reverse <- c("Q1.21_1" ,
"Q1.11_1" ,
"Q1.13_1" ,
"Q1.23_1" ,
"Q1.14_1" ,
"Q1.27_1" ,
"Q1.17_1" ,
"Q1.25_1" ,
"Q1.9_1")

cols_activeengagement <- c("Q1.1_1" ,
"Q1.3_1" ,
"Q1.8_1" ,
"Q1.15_1" ,
"Q1.21_1" ,
"Q1.24_1" ,
"Q1.28_1" ,
"Q1.34" ,
"Q1.38")

cols_perceptualabilities <- c("Q1.5_1" ,
"Q1.6_1" ,
"Q1.11_1" ,
"Q1.12_1" ,
"Q1.13_1" ,
"Q1.18_1" ,
"Q1.22_1" ,
"Q1.23_1" ,
"Q1.26_1")

cols_musicaltraining <- c("Q1.14_1" , "Q1.27_1",
"Q1.32" ,
"Q1.33" , ## think about how this is scored? doesn't seem like a lot of people answered
"Q1.35" ,
"Q1.36" ,
"Q1.37")


cols_singingabilities <- c("Q1.4_1" ,
"Q1.7_1" ,
"Q1.10_1" ,
"Q1.17_1" ,
"Q1.25_1" ,
"Q1.29_1" ,
"Q1.30_1")

cols_emotion <- c("Q1.2_1" ,
"Q1.9_1" ,
"Q1.16_1" ,
"Q1.19_1" ,
"Q1.20_1" ,
"Q1.31_1")

cols_musicalsophistication <- c("Q1.1_1" ,
           "Q1.3_1" ,
"Q1.4_1" ,
"Q1.7_1" ,
"Q1.10_1" ,
"Q1.12_1" ,
"Q1.14_1" ,
"Q1.15_1" ,
"Q1.17_1" ,
"Q1.19_1" ,
"Q1.23_1" ,
"Q1.24_1" ,
"Q1.25_1" ,
"Q1.27_1" ,
"Q1.29_1" ,
"Q1.32" ,
"Q1.33")

# Reverse code

Gold[cols_reverse] <- lapply(Gold[cols_reverse], reverseCode, min=1, max=7)

# Add sub-scores and total to main df

df$Gold_total <- apply(Gold,1, sum)/38 # total GoldMSI score
df$Gold_activeengagement <- apply(Gold[cols_activeengagement], 1,sum)/9
df$Gold_perceptualabilities <- apply(Gold[cols_perceptualabilities],1, sum)/9
df$Gold_musicaltraining <-apply(Gold[cols_musicaltraining],1, sum)/7
df$Gold_singingabilities <- apply(Gold[cols_singingabilities],1, sum)/7
df$Gold_emotion <- apply(Gold[cols_emotion],1, sum)/6
df$Gold_musicalsophistication <- apply(Gold[cols_musicalsophistication],1, sum)/18

hist(df$Gold_total)
```

#eBMRQ
```{r}
bmrq <- df %>%
  dplyr::select("Q2_1":"Q21_1", "Q23_1":"Q26_1")

bmrq <- as.data.frame(lapply(bmrq[,], as.integer))

# BMRQ columns to reverse code and sub-score
cols_reverse <- c("Q3_1",
                  "Q6_1")

cols_emotion <- c("Q4_1",
  "Q9_1",
  "Q13_1",
  "Q19_1")

cols_sensorimotor <-c("Q6_1",
  "Q11_1",
  "Q16_1",
  "Q21_1")
                      
cols_moodreg <- c("Q5_1",
  "Q10_1",
  "Q15_1",
  "Q20_1")

cols_musicseek <- c("Q3_1",
  "Q8_1",
  "Q12_1",
  "Q18_1")

cols_socialreward <-c("Q2_1",
  "Q7_1",
  "Q14_1",
  "Q17_1")

cols_absorption <- c("Q23_1", "Q24_1", "Q25_1", "Q26_1")

# Reverse code
bmrq[cols_reverse] <- lapply(bmrq[cols_reverse], reverseCode)

# Add sub-scores and total to main df
df$eBMRQ_total <- apply(bmrq,1, sum) 
df$BMRQ_emotion <- apply(bmrq[cols_emotion], 1,sum)
df$BMRQ_sensorimotor <- apply(bmrq[cols_sensorimotor],1, sum)
df$BMRQ_moodreg <-apply(bmrq[cols_moodreg],1, sum)
df$BMRQ_musicseek <- apply(bmrq[cols_musicseek],1, sum)
df$BMRQ_socialreward <- apply(bmrq[cols_socialreward],1, sum)
df$BMRQ_absorption<- apply(bmrq[cols_absorption],1, sum)

hist(df$eBMRQ_total)
```

#BDI --> items asking about changes in appetite (BDI_17) and sleep (BDI_15) need to be scored differently (see Attachment_AU in named attachments folder - there are two answers for both 1, 2, and 3 scores; also the responses should range from 0 to 3 )
```{r}
BDI <- df %>%
  dplyr::select("BDI_1":"BDI_20")

BDI$BDI_15[BDI$BDI_15 == 3] <- 2
BDI$BDI_15[BDI$BDI_15 == 4 | BDI$BDI_15 == 5] <- 3
BDI$BDI_15[BDI$BDI_15 == 6 | BDI$BDI_15 == 7] <- 4

BDI$BDI_17[BDI$BDI_17 == 3] <- 2
BDI$BDI_17[BDI$BDI_17 == 4 | BDI$BDI_17 == 5] <- 3
BDI$BDI_17[BDI$BDI_17 == 6 | BDI$BDI_17 == 7] <- 4

BDI[BDI == 1] <- 0
BDI[BDI == 2] <- 1
BDI[BDI == 3] <- 2
BDI[BDI == 4] <- 3

BDI <- as.data.frame(lapply(BDI[,], as.integer))

df$BDI_total <- apply(BDI,1,sum)

hist(df$BDI_total)
```

#M@H
```{r}
MH <- df %>%
  dplyr::select("M.H_child1_1":"M.H_child20_1")

MH <- MH[complete.cases(MH),]
MH <- as.data.frame(lapply(MH[,], as.integer))

cols_reverse <- c("M.H_child6_1","M.H_child7_1","M.H_child11_1","M.H_child12_1","M.H_child18_1","M.H_child19_1","M.H_child20_1")
MH[cols_reverse] <- lapply(MH[cols_reverse], reverseCode, min=1, max=7)

df$MH_total <- apply(MH,1, sum) # total M@H scores
hist(df$MH_total)

# # started putting these together but I'm not sure what goes where
# cols_caregiverbeliefs <- c("M.H_child1_1", "M.H_child2_1", "M.H_child3_1", "M.H_child4_1")
# 
# cols_caregiversinging <- c("M.H_child9_1")
# 
# cols_childhoodattitude <- c("M.H_child8_1")
# 
# cols_socialcontexts <- c("")
# 
# cols_musicmaking <- c("M.H_child5_1", "M.H_child6_1", "M.H_child7_1")
# 
# df$MH_caregiverbeliefs <- apply(MH[cols_caregiverbeliefs], 1,sum)
# df$MH_caregiversinging <- apply(MH[cols_caregiversinging],1, sum)
# df$MH_childhoodattitude <-apply(MH[cols_childhoodattitude],1, sum)
# df$MH_socialcontexts <- apply(MH[cols_socialcontexts],1, sum)
# df$MH_musicmaking <- apply(MH[cols_musicmaking],1, sum)
```

#RDEES
```{r}
rdees <- df %>%
  dplyr::select("RDEES_1_1":"RDEES_14_1")

cols_reverse <- c("RDEES_1_1","RDEES_5_1","RDEES_9_1", "RDEES_11_1")

rdees <- as.data.frame(lapply(rdees[,], as.integer))

rdees[cols_reverse] <- lapply(rdees[cols_reverse], reverseCode, min=1, max=5)

cols_range <- c("RDEES_1_1","RDEES_3_1","RDEES_5_1","RDEES_7_1", "RDEES_9_1", "RDEES_11_1", "RDEES_13_1")
cols_differentation <- c("RDEES_2_1","RDEES_4_1","RDEES_6_1","RDEES_8_1", "RDEES_10_1", "RDEES_12_1", "RDEES_14_1")

df$rdees_range <- apply(rdees[cols_range], 1,sum)
df$rdees_differentiation <- apply(rdees[cols_differentation],1, sum)
df$rdees_total <- df$rdees_differentiation + df$rdees_range

hist(df$rdees_total)
```

## REMOVE THE SECOND OPTION IF THERE ARE DUPLICATES
```{r}
# Check for duplicates in the SURVEY_CODE column and keep only the first occurrence
df_unique <- df[!duplicated(df$SURVEY_CODE), ]

# If you want to see the duplicate entries that were removed
duplicates <- df[duplicated(df$SURVEY_CODE), ]

# Display the result
print(df_unique)
print(duplicates)
```


## SELECT RELEVANT COLUMNS
```{r}
scores <- df_unique %>%
  dplyr::select("SURVEY_CODE", "STAI_total":"rdees_total")
```

```{r}
# Find SURVEY_CODE in scores that do not match any ID in results
non_matching_in_scores <- scores[!scores$SURVEY_CODE %in% results$ID, ]

# Find ID in results that do not match any SURVEY_CODE in scores
non_matching_in_results <- results[!results$ID %in% scores$SURVEY_CODE, ]

# Display the non-matching entries
print("SURVEY_CODEs in scores that do not match any ID in results:")
print(non_matching_in_scores)

print("IDs in results that do not match any SURVEY_CODE in scores:")
print(non_matching_in_results)

```

## MERGE WITH V23_ANALYSIS
```{r}
merged_df <- merge(scores, results, by.x = "SURVEY_CODE", by.y = "ID", all = FALSE)
merged_df_recoded <- merge(scores, results_recode, by.x = "SURVEY_CODE", by.y = "ID", all = FALSE)
```

#correlations
```{r}
# Select only the numeric columns for the correlation matrix
numeric_columns <- merged_df[, sapply(merged_df, is.numeric)]
numeric_columns_recoded <- merged_df_recoded[, sapply(merged_df_recoded, is.numeric)]

# Calculate the correlation matrix
correlation_matrix <- cor(numeric_columns, use = "complete.obs")
correlation_matrix_recoded <- cor(numeric_columns_recoded, use = "complete.obs")

# Function to compute significance levels
cor.mtest <- function(mat, conf.level = 0.95) {
  mat <- as.matrix(mat)
  n <- ncol(mat)
  p.mat <- matrix(NA, n, n)
  diag(p.mat) <- 0
  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      tmp <- cor.test(mat[, i], mat[, j], conf.level = conf.level)
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
    }
  }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}

# Compute p-values
p_values <- cor.mtest(numeric_columns)
p_values_recoded <- cor.mtest(numeric_columns_recoded)

# Specify the folder where you want to save the file
output_folder <- "../results/qualtrics/"

# Combine the folder path with the file name
output_file <- file.path(output_folder, "Significant Correlations Plot (without Recoding ICC) 10-7-24.png")

# Open a PNG device with the specified file path
png(output_file, width = 800, height = 800)

# Generate the corrplot
corrplot(correlation_matrix, method = "circle", type = "upper", 
         p.mat = p_values, sig.level = 0.05, insig = "blank",
         tl.col = "black", tl.srt = 45, addCoef.col = NULL,
         col = colorRampPalette(c("blue", "white", "red"))(200))

title(main = "Significant Correlations (without Recoding Granularity Scores)", col.main = "black", font.main = 4)

# Close the PNG device
dev.off()

# Specify the folder where you want to save the file
output_folder <- "../results/qualtrics/"

# Combine the folder path with the file name
output_file <- file.path(output_folder, "Significant Correlations Plot (with Recoding ICC) 10-7-24.png")

# Open a PNG device with the specified file path
png(output_file, width = 800, height = 800)

# Generate the corrplot
corrplot(correlation_matrix_recoded, method = "circle", type = "upper", 
         p.mat = p_values, sig.level = 0.05, insig = "blank",
         tl.col = "black", tl.srt = 45, addCoef.col = NULL,
         col = colorRampPalette(c("blue", "white", "red"))(200))

title(main = "Significant Correlations (WITH Recoding Granularity Scores)", col.main = "black", font.main = 4)

# Close the PNG device
dev.off()
```

## ISOLATING PHONE NUMBERS for IDing aMEDT
```{r}
phones <- df %>%
  select(c("PUBLICID", "SURVEY_CODE"))

clean_numbers <- function(phone) {
  gsub("[^0-9]", "", phone)
}

missing_phones <- data.frame(SURVEY_CODE = c("30022","30064","30070","30349","30475","30880","31231","31576","31699","32275","32392","32572","32587","32791","32884"),
                             PUBLICID = c("9147193363","4692333768","6469831605","9492282663","9708256433","7818179742","8623384867","7819994302","6178936664","6099371048","9788573567","6503882928","8184141619","7742767724","4432798350"))

# Update PUBLIC_ID in df based on SURVEY_CODE match

phones <- phones %>%
  left_join(missing_phones, by = "SURVEY_CODE") %>%
  mutate(PUBLICID = ifelse(!is.na(PUBLICID.y), PUBLICID.y, PUBLICID.x)) %>%
  select(SURVEY_CODE, PUBLICID) # Clean up extra columns


cleaned_phones <- phones %>%
  mutate(PUBLICID = clean_numbers(PUBLICID)) %>%
  filter(nchar(PUBLICID) == 10 | nchar(PUBLICID) == 5)

aMEDT <- read.csv("../data/EDT/aMEDT Results - Sheet1.csv") %>%
  select(c("session.p_id", "EDT.ability"))

merged_aMEDT <- merge(aMEDT, cleaned_phones, by.x = "session.p_id", by.y = "PUBLICID", all = FALSE)

merged_with_aMEDT <- merge(merged_aMEDT, merged_df, by.x = "SURVEY_CODE", by.y = "SURVEY_CODE", all = FALSE) %>%
  select(-("session.p_id"))
merged_recoded_with_aMEDT <- merge(merged_aMEDT, merged_df_recoded, by.x = "SURVEY_CODE", by.y = "SURVEY_CODE", all = FALSE) %>%
  select(-("session.p_id"))
```

## find missing IDs
```{r}
results[!results$ID %in% merged_df$SURVEY_CODE, ]
#30907 and 30916 didn't do the Qualtrics

scores[!scores$SURVEY_CODE %in% results$ID, ]
merged_aMEDT[!merged_aMEDT$SURVEY_CODE %in% merged_df$SURVEY_CODE, ]
#32578 was removed from granularity scoring (see v23_Analysis)

merged_df[!merged_df$SURVEY_CODE %in% merged_aMEDT$SURVEY_CODE, ]
#missing 30349, 30475, 30880, 31231, 31576, 32791, 32884
```

# Function to compute significance levels
```{r}
cor.mtest <- function(mat, conf.level = 0.95) {
  mat <- as.matrix(mat)
  n <- ncol(mat)
  p.mat <- matrix(NA, n, n)
  diag(p.mat) <- 0
  for (i in 1:(n - 1)) {
    for (j in (i + 1):n) {
      tmp <- cor.test(mat[, i], mat[, j], conf.level = conf.level)
      p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
    }
  }
  colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
  p.mat
}
```

## correlations w/ aMEDT 10/21/24
```{r}
# Select only the numeric columns for the correlation matrix
numeric_columns <- merged_df[, sapply(merged_df, is.numeric)]
numeric_columns_recoded <- merged_df_recoded[, sapply(merged_df_recoded, is.numeric)]

# Calculate the correlation matrix
correlation_matrix <- cor(numeric_columns, use = "complete.obs")
correlation_matrix_recoded <- cor(numeric_columns_recoded, use = "complete.obs")

# Compute p-values
p_values <- cor.mtest(numeric_columns)
p_values_recoded <- cor.mtest(numeric_columns_recoded)

# Specify the folder where you want to save the file
output_folder <- "../results/qualtrics/"

# Combine the folder path with the file name
output_file <- file.path(output_folder, "Significant Correlations Plot (without Recoding ICC) 10-25-24.png")

# Open a PNG device with the specified file path
png(output_file, width = 800, height = 800)

# Generate the corrplot
corrplot(correlation_matrix, method = "circle", type = "upper", 
         p.mat = p_values, sig.level = 0.05, insig = "blank",
         tl.col = "black", tl.srt = 45, addCoef.col = NULL,
         col = colorRampPalette(c("blue", "white", "red"))(200))

title(main = "Significant Correlations (without Recoding Granularity Scores) 10-25-24", col.main = "black", font.main = 4)

# Close the PNG device
dev.off()

# Specify the folder where you want to save the file
output_folder <- "../results/qualtrics/"

# Combine the folder path with the file name
output_file <- file.path(output_folder, "Significant Correlations Plot (with Recoding ICC) 10-25-24.png")

# Open a PNG device with the specified file path
png(output_file, width = 800, height = 800)

# Generate the corrplot
corrplot(correlation_matrix_recoded, method = "circle", type = "upper", 
         p.mat = p_values, sig.level = 0.05, insig = "blank",
         tl.col = "black", tl.srt = 45, addCoef.col = NULL,
         col = colorRampPalette(c("blue", "white", "red"))(200))

title(main = "Significant Correlations (WITH Recoding Granularity Scores) 10-25-24", col.main = "black", font.main = 4)

# Close the PNG device
dev.off()
```

## EDT correlation with granularity scores
```{r}
# Function to create correlation scatter plots with linear model fit
create_scatter_plot <- function(data, x_var, y_var, x_label, y_label, title, output_file) {
  # Calculate correlation coefficient and p-value
  correlation <- cor.test(data[[x_var]], data[[y_var]], method = "pearson")
  corr_coeff <- round(correlation$estimate, 2)
  p_value <- sub("^0.", ".", round(correlation$p.value, 3))
  
  # Create scatter plot
  scatter_plot <- ggplot(data, aes(x = !!ensym(x_var), y = !!ensym(y_var))) +
    geom_point() +
    stat_smooth(method = 'lm', formula = y ~ x, color = "blue") +
    xlab(x_label) +
    ylab(y_label) +
    ggtitle(title) +
    theme_classic() +
    theme(axis.title.x = element_text(size = 14, face = 'bold'),
          axis.title.y = element_text(size = 14, face = 'bold'),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12),
          plot.title = element_text(size = 16, face = 'bold', hjust = 0.5)) +
    # Add correlation coefficient and p-value as annotation
    annotate("text", x = Inf, y = Inf, label = paste("r =", corr_coeff, "\np =", p_value), 
             hjust = 1.1, vjust = 1.5, size = 5, color = "red", fontface = "bold")
  
  # Save plot to file
  ggsave(output_file, scatter_plot, width = 11)
}

create_scatter_plot(merged_with_aMEDT, "EDT.ability", "negmusicICC", 
                    "aMEDT Score", 
                    "Negative Emotion Granularity (Music)", 
                    "Correlation of Negative Emotion Granularity Scores (Music) and aMEDT Score", 
                    "../results/EDT/Neg_Graph_10_25_24.png")

create_scatter_plot(merged_with_aMEDT, "EDT.ability", "posmusicICC", 
                    "aMEDT Score", 
                    "Positive Emotion Granularity (Music)", 
                    "Correlation of Positive Emotion Granularity Scores (Music) and aMEDT Score", 
                    "../results/EDT/Pos_Graph_10_25_24.png")

create_scatter_plot(merged_with_aMEDT, "EDT.ability", "allmusicICC", 
                    "aMEDT Score", 
                    "Combined Emotion Granularity (Music)", 
                    "Correlation of Combined Emotion Granularity Scores (Music) and aMEDT Score", 
                    "../results/EDT/Combined_Graph_10_25_24.png")

# Plotting correlation scatter plots - Recoded
create_scatter_plot(merged_recoded_with_aMEDT, "EDT.ability", "negmusicICC", 
                    "Negative Emotion Granularity (Pictures)", 
                    "Negative Emotion Granularity (Music)", 
                    "Correlation of Negative Emotion Granularity Scores (Music) (Scores > 1 Recoded) and aMEDT Score", 
                    "../results/EDT/Neg_Graph_Recoded_10_25_24.png")

create_scatter_plot(merged_recoded_with_aMEDT, "EDT.ability", "posmusicICC", 
                    "Positive Emotion Granularity (Pictures)", 
                    "Positive Emotion Granularity (Music)", 
                    "Correlation of Positive Emotion Granularity Scores (Music) (Scores > 1 Recoded) and aMEDT Score", 
                    "../results/EDT/Pos_Graph_Recoded_10_25_24.png")

create_scatter_plot(merged_recoded_with_aMEDT, "EDT.ability", "allmusicICC", 
                    "Combined Emotion Granularity (Pictures)", 
                    "Combined Emotion Granularity (Music)", 
                    "Correlation of Combined Emotion Granularity Scores (Music) (Scores > 1 Recoded) and aMEDT Score", 
                    "../results/EDT/Combined_Graph_Recoded_10_25_24.png")

```